### 2022-02-07 paper1-cleaning.Rmd
git init

---
title: "gtrends_cleaning"
author: "Kelsey Gonzalez"
date: "2/7/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, here, vroom, gtrendsR,
               lubridate, zoo)

```

# Functions
```{r}
find_mondays <- function(year) {
  mondays <- seq(ymd(glue("{year}-01-01")),ymd(glue("{year}-12-31")),by="1 day")
  mondays <- mondays[wday(mondays,label = TRUE) == "Mon" & mondays < today() - 7]
  return(mondays)
}
find_initial_trends <- function(keyword, period_list){
  period_list <- as.character(period_list)

  trends <- tibble(location = character(),
                   hits = numeric(),
                   keyword = character(),
                   date = character())

  for (period in period_list){ 
    ppl7<- as.character(ymd(period) + 7)

    trends <- gtrends(
      keyword = keyword,
      geo = "US",
      time = paste(period, ppl7),
      gprop = "web",
      category = 0,
      hl = "en-US")$interest_by_dma %>%
      tibble() %>%
      mutate(date = period,
             hits = as.numeric(hits)) %>% 
      select(-c(geo, gprop)) %>%
      bind_rows(trends)
  }

  return(trends)
}
find_scale_point <- function(keyword, year){
  if (year(today()) == year) {
    span <- glue("{year}-01-01 {as.character(today() - 7)}")
    } else {
      span <- glue("{year}-01-01 {year}-12-31")
    }

  if (nchar(span) != 21) stop('incorrect span')

  print(glue("keyword = {keyword}"))
  print(glue("span = {span}"))

  rescale <- gtrends(
    keyword = keyword,
    geo = "US-CA-803",
    time = span,
    gprop = "web",
    category = 0,
    hl = "en-US", 
    onlyInterest = TRUE, 
    low_search_volume = FALSE)$interest_over_time %>% 
    tibble()  %>% 
    mutate(date = ymd(date(date))+1,
           hits = ifelse(hits < 1, NA, hits)) %>%
    fill(hits)%>% 
    select(-c(gprop, keyword, geo, time, category)) %>% 
    rename(hits_rescale = hits)

  if (rescale %>% drop_na() %>% nrow() == 0) stop('no rows of data')
  return(rescale)
}
rescale_trends <- function(trends, rescale){
  rescale_ratio <- rescale %>%
    mutate(location = 'Los Angeles CA',
           hits_rescale = replace_na(hits_rescale, 0),
           hits_rescale = ifelse(hits_rescale == 0, 0.0001, hits_rescale)) %>% 
    left_join(trends %>% 
                 mutate(date = ymd(date)), by = c('date', 'location'))  %>% 
    mutate(rescale_ratio = hits_rescale/hits)  %>% 
    select(date, rescale_ratio)

  trends <- trends %>% 
    mutate(date = ymd(date)) %>% 
    group_by(location) %>% 
    fill(hits) %>%
    ungroup() %>% 
    left_join(rescale_ratio, by = "date") %>% 
    mutate(hits_transformed_a = hits * rescale_ratio)
  return(trends)
}
find_year_trends <- function(keyword, year){
  trends <- find_initial_trends(keyword, find_mondays(year))
  rescaled<- find_scale_point(keyword, year)
  rescaled_trends <- rescale_trends(trends, rescaled)

  rescaled_trends <- rescaled_trends %>% 
    mutate(location = str_to_upper(location),
           location = str_replace_all(location,"-", " - "),
           location = str_replace_all(location,",", ""),
           location = str_replace_all(location,"\\s(\\w{2})\\b", " \\(\\1\\)")) %>% 
    select(DMA_google = location, !!keyword := hits_transformed_a, date)

  return(rescaled_trends)
}

find_cross_sectional_trends <- function(keyword, date_begin, span_type = 'month'){
  if (span_type == 'week'){
    ppl <- as.character(ymd(date_begin) + 7)
  }
  if (span_type == 'two-week'){
    ppl <- as.character(ymd(date_begin) + 14)
  }
  if (span_type == 'month'){
    ppl <- as.character(ymd(date_begin) + 31)
  }
  if (span_type == 'year'){
    ppl <- as.character(ymd(date_begin) + 365)
  }

  print(glue("keyword = {keyword}"))
  print(glue("span = {date_begin} - {ppl}"))

  trends <- gtrends(
    keyword = keyword,
    geo = "US",
    time = paste(date_begin, ppl),
    gprop = "web",
    category = 0,
    hl = "en-US")$interest_by_dma %>%
    tibble() %>%
    mutate(date = date_begin,
           hits = as.numeric(hits)) %>% 
    select(-c(geo, gprop))

  return(trends)

}
```

# attitudinal
• Vaccine Hesitancy
		○ https://data.cdc.gov/Vaccinations/Vaccine-Hesitancy-for-COVID-19-County-and-local-es/q9mh-h2tw/data

cross-sectional
dates - March 3, 2021 – March 15, 2021
```{r}
find_cross_sectional_trends('trend', '2021-03-03', 'two-week')
```

• Mask Usage
		○ New York Times Survey
		○ https://github.com/nytimes/covid-19-data/tree/master/mask-use

cross-sectional
July 2 and July 14, 2020
```{r}
find_cross_sectional_trends('trend', '2020-07-02', 'two-week')
```

# health
• Covid Rates
		○ https://github.com/nytimes/covid-19-data/tree/master/rolling-averages
longitudinal
dates -

find_year_trends <- function(keyword, year)

• Suicide
		○ https://wonder.cdc.gov/mcd.html 
		○ Multiple Cause of Death Data 2019 (see notes for which variables count)
dates -

# political
• Presidential results
		○ https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/VOQCHQ
		○ MIT Election Data and Science Lab, 2018, 
		○ "County Presidential Election Returns 2000-2020",
		○ https://doi.org/10.7910/DVN/VOQCHQ, 
		○ Harvard Dataverse, V9

### 2022-02-07 paper1.Rmd
git init

---
title: "Article 1:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
author: "Kelsey Gonzalez"
date: "`r format(Sys.time(), '%d %B, %Y')`"
editor_options:
  chunk_output_type: console
output:
  bookdown::word_document2: 
    toc: true
    reference_docx: StylesTemplate.docx
  bookdown::pdf_document2:
    latex_engine: xelatex
    number_sections: true
header-includes:
   - \usepackage{siunitx}
   - \usepackage{setspace}
   - \usepackage{dcolumn}
   - \usepackage{caption}
   - \usepackage{longtable}
   - \usepackage{booktabs}
   - \doublespacing
   - \usepackage{placeins}
csl: american-sociological-association.csl
bibliography: "My Library.bib"
indent: true
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, 
                      message = FALSE,
                      warning = FALSE,
                      # cache = TRUE,
                      fig.width = 7,
                      fig.asp = 0.8,
                      out.width = "80%",
                      fig.align="center"
                      # dev.args = list(png = list(type = "cairo"))
                      )

if (!require("pacman")) install.packages("pacman")
pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
               modelsummary, showtext, thematic, kableExtra, scales)

my_palette = c('#56b4e9','#999999','#E69F00','#009E73','#CC79A7','#0072B2','#D55E00','#E69F00')
my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')

## Automatically use showtext to render text
font_add_google("Lora", "lora")
showtext_auto()

theme_diss <- function(base_size = 14) {
  theme_minimal(base_size = base_size) %+replace%
    theme(
      # Figure assembly
      plot.title = element_text(family="lora",
                                size = rel(1), 
                                margin = margin(0,0,5,0), 
                                hjust = 0),
      plot.title.position = "plot",
      plot.subtitle = element_text(family="lora",
                                   size = rel(0.85)),
      plot.caption = element_text(family="lora",
                                  size = rel(0.70),
                                  hjust = 1),
      # Graphical Zones
      panel.grid.minor = element_blank(),
      panel.border = element_blank(),
      # Axes
      axis.title = element_text(family="lora", 
                                size = rel(0.85)),
      axis.text = element_text(family="lora", 
                               size = rel(0.70)),
      axis.line = element_line(color = "black", 
                               arrow = arrow(length = unit(0.3, "lines"), 
                                             type = "closed")),
      # Legend
      legend.title = element_text(family="lora",
                                  size = rel(0.85)),
      legend.text = element_text(family="lora", 
                                 size = rel(0.70)),
      legend.key = element_rect(fill = "transparent", 
                                colour = NA),
      legend.key.size = unit(1.5, "lines"),
      legend.background = element_rect(fill = "transparent", 
                                       colour = NA),
      # Facetting 
      strip.background = element_rect(fill = "#17252D",
                                      color = "#17252D"),
      strip.text = element_text(family="lora",
                                size = rel(0.85), 
                                color = "white", 
                                margin = margin(5,0,5,0))
    )
}

theme_set(theme_diss())

conf_int_prop <- function(var){
  p <- mean(!!var, na.rm = T)
  q <- 1 - p
  n <- nrow(rain)
  min <- p - 1.96*sqrt((p*q)/n)
  max <- p + 1.96*sqrt((p*q)/n) 
  paste0(label_percent()(min), ", ", label_percent()(max))
}
print_perc <- function(var){
  label_percent()(mean(var, na.rm = T))
}

```

# Abstract

**Keywords**:

# Intro 
New big data sources have led to vast possibilities for social science research
because they are bigger, cheaper, and already available  (King 2011; Lazer et
al. 2009; Salganik 2017). Before overenthusiastically embracing these sources
into our workflows, social scientists must clearly establish parameters under
which these data sources could be operationalized (Bail 2014; Lazer et al.
2014). As prior research outlined, the “quantity of data does not mean that one
can ignore foundational issues of measurement and construct validity and
reliability and dependencies among data” (Lazer et al. 2014:1203). Building on
this prior research outlining these various issues with big data (boyd and
Crawford 2012; Lazer 2015), this paper tests the construct validity of Google
Search Trends as an indicator of three different cases, namely cultural
attitudes, disease prevalence and voting behavior. These three cases will be
tested using cultural indicators from the NORC General Social Survey, United
States county-level suicide rates from National Center for Health Statistics, US
cases rates of Covid-19 from The New York Times, historical US Presidential
Election results, and the American National Election Survey. Data will be
analyzed against corresponding operationalized Google Trends longitudinal data
using Pearson’s r for pairwise correlations, testing for the strength of
relationships between the Google Trend indicator and the respective comparison
indicator. This paper will contribute to the creation of methodological norms
and standards of how to use Google Trends as a big data source for societal
research and serve as a critical inquiry into the adoption of big data without a
critical eye for the ecological validity of the sources.

With the expansion of big data, some research has shown extremely innovative
methods that lead to groundbreaking results that are shown to be reliable. As an
example, Blumenstock et al. (2015) use county-level cell-phone records to
construct the distribution of poverty and wealth in Rwanda, a country where
national surveys and censes are rare and costly. However, Blumenstock et al.
(2015) go to great lengths to demonstrate that their operationalization of the
cell phone data creates a reliable and valid construct; few social science
papers utilizing big data dig into the construct validity of their metrics to
this extent and even fewer publications focus on methodological guidelines of
how to use sources of big data (Asseo et al. 2020; Stiles and Grogan-Myers
2018). However, research has shown the small adjustments to an algorithm or
metric may void any research insight we are able to pull from such data (Lazer
et al. 2014). Because of this, I propose a methodological validation study of
the Google Search Trends source of big data to investigate how it is advisable
to utilize this data in social scientific research.

I will use three categorizations of ways I propose Google Trends could be
operationalized for social scientific usage. First, I’ll test Google Trends as
an operationalization of cultural attitudes with the General Social Survey.
After Bail (2014)’s call for cultural sociologists to utilize the ever expanding
world of big data, Google trends as a data source began appearing in
sociological and social science research.  From research on mass shootings and
firearms (Brownstein, Nahari, and Reis 2020; Semenza and Bernau 2020), protest
and anti-Muslim sentiment (Bail, Merhout, and Ding 2018; Barrie 2020; Gross and
Mann 2017), to analyzing country-level changes in social perception (Reyes,
Majluf, and Ibáñez 2018), Google search trends are a new and innovative
indicator of cultural interest. Extending into social networks and culture,
Bail, Brown and Wimmer (2019) even used Google trends to measure how culture
spreads around the globe.

Google Search Trends have also been used continuously in estimations of disease
prevalence and population health in journals like the Journal of Medical
Internet Research. While much of this research has focused on the Covid-19
pandemic (Jimenez et al. 2020a, 2020b; Lim et al. 2020:20; Mavragani and Gkillas
2020; Nguyen et al. 2020; Todorova, Tsankova, and Ermenlieva 2021), other
research has investigated Google Trends as an indicator of wellbeing (Brodeur et
al. 2021; Carpi et al. 2020; Du et al. 2020), suicidality (Burnett, Eapen, and
Lin 2020), vaccination uptake (Dalum Hansen, Lioma, and Mølbak 2016), obesity
(Sarigul and Rui 2014), and even insomnia (Zitting et al. 2020), to cover a few
examples. For a partial review of other utilizations, see Nuti et al. (2014).
According to Jaidka et al (2021), the majority of studies profess a correlation
of > .70, “demonstrating the vast potential of Google Search as a proxy for
monitoring population health” (p. 3) based on assumptions that individuals
search because of self-diagnosis and to identify possible courses of treatment
(De Choudhury, Morris, and White 2014).

Various sources have also used Google Trends as a way to forecast political
elections and political attitudes (Wolf 2018). For instance, Swearingen and
Ripberger (2014) investigate how U.S. Senate Elections relate to attention
measured by search traffic. Prado-Román et al. (2020) compare how Google Search
trends are able to predict presidential election results in both the United
States and Canada. Finally, the OECD Development Centre is investigating how
Google data can help elucidate governments’ approval in Latin America (Montoya
et al. 2020)

Research Question - How can we operationalize Google Search Trends as a valid
indicator for uses in social science research?

# Research Methodology
To investigate the construct and criterion validity of the use of Google Trends
in these three areas, I will gather geo-located data from a sources related to
each case and use Pearson’s r for pairwise correlations, testing for the
strength of relationship between the Google Trend indicator and the respective
comparison indicator. Pairwise correlations allow for testing of nested data,
allowing for multiple search terms to be compared across locations
simultaneously as well as comparing change over time. I will test both raw
questions with raw trends as well as using dimensionality reduction through
factor analysis and principal components analysis (PCA). In addition, I’d like
to explore how this data would cluster locations together using tools like
blockmodeling and other clustering techniques.

To investigate the correlation between Google search trends, I will use
questions from the NORC General Social Survey. I will need to obtain an $800
grant to purchase geolocated data from NORC for this project. I plan to submit a
small grant application to SBS to receive these funds. I will use various NORC
GSS cultural value questions and aggregate the relevant zip code up to Nielsen’s
metropolitan market area (MMA), the level Google trends are aggregated to, using
population weighting.

For disease prevalence, I will use United States county-level suicide rates from
National Center for Health Statistics, US cases rates of Covid-19 from The New
York Times, and obesity rates to compare search trends to observable data.

Finally, I’ll test Google Trends as an operationalization of political attitudes
by looking at actual voting outcomes in historical US Presidential Election
results and the American National Election Survey and Google Trends about
candidates.

```{r}
tibble::tribble(
                                ~Validated.source, ~Google.trend.equivalent,
                                            "GSS",                       NA,
  "Suicide,\\nCovid-19 rates\\nVaccine hesitancy",                       NA,
           "Presidential Voting outcomes,\\nANES",                       NA
  )

```

## Measures
### attitudinal
• Vaccine Hesitancy
		○ https://data.cdc.gov/Vaccinations/Vaccine-Hesitancy-for-COVID-19-County-and-local-es/q9mh-h2tw/data

• Mask Usage
		○ New York Times Survey

### health
• Covid Rates
		○ https://github.com/nytimes/covid-19-data/tree/master/rolling-averages

• Suicide
		○ https://wonder.cdc.gov/mcd.html 
		○ Multiple Cause of Death Data 2019 (see notes for which variables count)

### political
• Presidential results
		○ https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/VOQCHQ
		○ MIT Election Data and Science Lab, 2018, 
		○ "County Presidential Election Returns 2000-2020",
		○ https://doi.org/10.7910/DVN/VOQCHQ, 
		○ Harvard Dataverse, V9

### Independent Variables
## Analysis
# Results
## Cultural
## Medical
## Political
# Discussion
While I expect these tests to show high correlation between observed indicators
and Google search trends, there will be three important questions that surface.
First, just because something is correlated, does that mean it can replace the
collection of other types of data? Second, how correlated does a trend need to
be for social scientists to justifiably rely on it to indicate some outcome? And
finally, how can we construct analyses like this to be robust to changes in the
terms used across time and location?

The purpose of this paper is more methodological than theoretical, and I see
this paper having an impact on the social sciences and computational social
science as researchers pursue more projects using this source of big data.
Google Trends are relatively underutilized in the field compared to in the
health sciences and business. Once I assess how this data can be used, I would
like to be able to join Bail (2014) in encouraging social scientists to pursue
more research with big data while taking into account the potential pitfalls
with any source of big data (McFarland and McFarland 2015).

# Conclusion

\newpage

# References {-}

<div id="refs"></div>

\newpage

# Appendix

### 2022-02-07 googletrends.R

@@ -1,0 +1,133 @@
+pacman::p_load(tidyverse, gtrendsR, lubridate, here, glue, zoo)
+
+find_mondays <- function(year) {
+  mondays <- seq(ymd(glue("{year}-01-01")),ymd(glue("{year}-12-31")),by="1 day")
+  mondays <- mondays[wday(mondays,label = TRUE) == "Mon" & mondays < today() - 7]
+  return(mondays)
+}
+find_initial_trends <- function(keyword, period_list){
+  period_list <- as.character(period_list)
+  
+  trends <- tibble(location = character(),hits = numeric(),keyword = character(),date = character())
+  
+  for (period in period_list){ 
+    ppl7<- as.character(ymd(period) + 7)
+    trends <- gtrends(
+      keyword = keyword,
+      geo = "US",
+      time = paste(period, ppl7),
+      gprop = "web",
+      category = 0,
+      hl = "en-US")$interest_by_dma %>%
+      tibble() %>%
+      mutate(date = period,
+             hits = as.numeric(hits)) %>% 
+      select(-c(geo, gprop)) %>%
+      bind_rows(trends)
+  }
+  
+  return(trends)
+}
+find_scale_point <- function(keyword, year){
+  if (year(today()) == year) {
+    span <- glue("{year}-01-01 {as.character(today() - 7)}")
+    } else {
+      span <- glue("{year}-01-01 {year}-12-31")
+    }
+  
+  if (nchar(span) != 21) stop('incorrect span')
+  
+  print(glue("keyword = {keyword}"))
+  print(glue("span = {span}"))
+  
+  rescale <- gtrends(
+    keyword = keyword,
+    geo = "US-CA-803",
+    time = span,
+    gprop = "web",
+    category = 0,
+    hl = "en-US", 
+    onlyInterest = TRUE, 
+    low_search_volume = FALSE)$interest_over_time %>% 
+    tibble()  %>% 
+    mutate(date = ymd(date(date))+1,
+           hits = ifelse(hits < 1, NA, hits)) %>%
+    fill(hits)%>% 
+    select(-c(gprop, keyword, geo, time, category)) %>% 
+    rename(hits_rescale = hits)
+  
+  if (rescale %>% drop_na() %>% nrow() == 0) stop('no rows of data')
+  return(rescale)
+}
+rescale_trends <- function(trends, rescale){
[…]

### 2022-02-16 paper1-cleaning.Rmd
fix dma key code

@@
 output: html_document
+editor_options: 
+  chunk_output_type: console
 ---
@@
 
-find_cross_sectional_trends <- function(keyword, date_begin, span_type = 'month'){
-  if (span_type == 'week'){
-    ppl <- as.character(ymd(date_begin) + 7)
-  }
-  if (span_type == 'two-week'){
-    ppl <- as.character(ymd(date_begin) + 14)
-  }
-  if (span_type == 'month'){
-    ppl <- as.character(ymd(date_begin) + 31)
-  }
-  if (span_type == 'year'){
-    ppl <- as.character(ymd(date_begin) + 365)
-  }
+```
+
+```{r find_cross_sectional_trends}
+find_cross_sectional_trends <- function(keyword, date_begin, span_length = 1){
+  ppl <- as.character(ymd(date_begin) + span_length)
 
@@
            hits = as.numeric(hits)) %>% 
-    select(-c(geo, gprop))
+    select(-c(geo, gprop)) %>% 
+    mutate(location = str_to_upper(location),
+           location = str_replace_all(location,"-", " - "),
+           location = str_replace_all(location,",", ""),
+           location = str_replace_all(location,"\\s(\\w{2})\\b", " \\(\\1\\)"))
 
@@
 }
+```
+
+# dma keys
+```{r}
+# bringing in DMA fox new search from
+# https://dataverse.harvard.edu/file.xhtml?persistentId=doi:10.7910/DVN/IVXEHT/A56RIW&version=7.4
+dma <- read_csv(here("data", "county_dma.csv")) %>%
+    mutate(FIPS_state = str_pad(STATEFP, 2, pad = "0"),
+         FIPS_county = str_pad(CNTYFP, 3, pad = "0"),
+         FIPS = paste0(FIPS_state, FIPS_county)) %>%
+  select(FIPS, DMA, STATE, COUNTY)
+
+# I made this file for the various inconsistencies between the two
+dma_key <- read_csv(here("data","google_dma_key.csv"))
+
+dma <- dma %>%
+  full_join(dma_key)
 ```
@@
 ```{r}
-find_cross_sectional_trends('trend', '2021-03-03', 'two-week')
+find_cross_sectional_trends('trend', '2021-03-03', 12)
 ```
@@
 ```{r}
-find_cross_sectional_trends('trend', '2020-07-02', 'two-week')
+find_cross_sectional_trends('trend', '2020-07-02', 12)
 ```
@@
 # health
-• Covid Rates
+## Covid Rates
 		○ https://github.com/nytimes/covid-19-data/tree/master/rolling-averages
@@
 
-find_year_trends <- function(keyword, year)
+```{r}
+covid_rates <- vroom('https://raw.githubusercontent.com/nytimes/covid-19-data/master/rolling-averages/us-counties-2020.csv') %>% bind_rows(vroom('https://raw.githubusercontent.com/nytimes/covid-19-data/master/rolling-averages/us-counties-2021.csv')) %>%
+  mutate(wday = lubridate::wday(date, label=TRUE),
+         fips = str_sub(geoid, start = -5)) %>% 
+  filter(wday == "Mon") %>% 
+  select(fips, date, county, state, covid_rate = cases_avg_per_100k)
 
-• Suicide
+covid_gtrend <- find_year_trends('Covid-19', 2020) %>% 
+  rowbind(find_year_trends('Covid-19', 2021))
+
+find_year_trends('Cant smell', '2020-01-01', 365)
+find_year_trends('Covid-19', '2021-01-01', 365)
+```
+
+## Suicide
 		○ https://wonder.cdc.gov/mcd.html 
 		○ Multiple Cause of Death Data 2019 (see notes for which variables count)
-dates -
+dates - 2019 cross sectional inclusive
+
+<!-- TODO need new wonder file, this one only has 1k counties??  -->
+
+```{r suicide}
+suicide_measures <- read_delim(here('data','suicide',
+                                    'Multiple Cause of Death, 2018-2019, Single Race.txt')) %>% 
+  janitor::clean_names() %>% 
+  filter(is.na(notes)) %>% 
+  select(fips = county_code, county, deaths, population, crude_rate)
+
+suicide_gtrends <- find_cross_sectional_trends(c('suicide', 'depression', 'suicide hotline'), 
+                                               '2019-01-01', 365) %>%   
+  pivot_wider(names_from = keyword, values_from = hits)  %>% 
+  select(-date) %>% 
+  mutate(location = str_to_lower(location))
+
+suicide <- suicide_measures %>% 
+  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
+  full_join(suicide_gtrends, by = c('DMA_google' = 'location'))
+
+  select(dma = DMA_google,
+         fips = county_fips, 
+         clinton_p, `Hilary Clinton`, trump_p, `Donald Trump`)
+```
 
@@
 • Presidential results
-		○ https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/VOQCHQ
-		○ MIT Election Data and Science Lab, 2018, 
-		○ "County Presidential Election Returns 2000-2020",
-		○ https://doi.org/10.7910/DVN/VOQCHQ, 
-		○ Harvard Dataverse, V9
+https://github.com/tonmcg/US_County_Level_Election_Results_08-20
+```{r pres_results}
+pres_2016_results <- read_csv('https://raw.githubusercontent.com/tonmcg/US_County_Level_Election_Results_08-20/master/2016_US_County_Level_Presidential_Results.csv') %>% 
+  select(county_name, county_fips = combined_fips, 
+         totalvotes = total_votes, clinton = votes_dem, trump = votes_gop) %>% 
+    mutate(county_fips = str_pad(county_fips, 5, pad = 0),
+           clinton_p = clinton / totalvotes,
+         trump_p = trump / totalvotes)
+
+pres_2020_results <- read_csv('https://raw.githubusercontent.com/tonmcg/US_County_Level_Election_Results_08-20/master/2020_US_County_Level_Presidential_Results.csv') %>% 
+  select(state = state_name, county_name, county_fips, 
+         totalvotes = total_votes, biden = votes_dem, trump = votes_gop) %>% 
+    mutate(biden_p = biden / totalvotes,
+         trump_p = trump / totalvotes)
+```
+```{r pres_gtrend}
+pres_2020_gtrend <- find_cross_sectional_trends(c('Joe Biden', 'Donald Trump'), '2020-01-01', 307) %>% 
+  pivot_wider(names_from = keyword, values_from = hits)  %>% 
+  select(-date)
+
+pres_2016_gtrend <- find_cross_sectional_trends(c('Hilary Clinton', 'Donald Trump'), '2016-01-01', 307) %>% 
+  pivot_wider(names_from = keyword, values_from = hits)  %>% 
+  select(-date)
+```
+```{r}
+pres_2016 <- pres_2016_results %>% 
+  inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>%
+  left_join(pres_2016_gtrend, by = c('DMA_google' = 'location')) %>%
+  select(dma = DMA_google,
+         fips = county_fips, 
+         clinton_p, `Hilary Clinton`, trump_p, `Donald Trump`)
+
+pres_2016 %>% ggplot(aes(x = trump_p, y = `Donald Trump`)) + geom_jitter() + geom_smooth()
+pres_2016 %>% ggplot(aes(x = clinton_p, y = `Hilary Clinton`)) + geom_jitter()
+
+pres_2020 <- pres_2020_results %>% 
+  inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>% 
+  left_join(pres_2020_gtrend, by = c('DMA_google' = 'location')) %>% 
+  select(dma = DMA_google,
+         fips = county_fips, 
+         biden_p, `Joe Biden`, trump_p, `Donald Trump`)
+
+pres_2020 %>% ggplot(aes(x = biden_p, y = Joe Biden`)) + geom_jitter() + geom_smooth()
+pres_2020 %>% ggplot(aes(x = trump_p, y = `Donald Trump`)) + geom_jitter() + geom_smooth()
+
+rm(list = c("pres_2016_results", "pres_2016_gtrend",
+            "pres_2020_results", "pres_2020_gtrend"))

### 2022-02-18 paper1-cleaning.Rmd
Done with wrangling more or less

@@
 # Functions
-```{r}
+```{r find_year_trends}
 find_mondays <- function(year) {
+  print('finding mondays')
   mondays <- seq(ymd(glue("{year}-01-01")),ymd(glue("{year}-12-31")),by="1 day")
@@
 find_initial_trends <- function(keyword, period_list){
+  print(glue("find trends for '{keyword}'"))
+
   period_list <- as.character(period_list)
@@
 find_scale_point <- function(keyword, year){
+  print('finding relevant scale point, using US-CA-803')
   if (year(today()) == year) {
@@
 rescale_trends <- function(trends, rescale){
+  print('rescaling trends')
   rescale_ratio <- rescale %>%
@@
 # attitudinal
-• Vaccine Hesitancy
+
+## Vaccine Hesitancy
 		○ https://data.cdc.gov/Vaccinations/Vaccine-Hesitancy-for-COVID-19-County-and-local-es/q9mh-h2tw/data
+		○ https://data.cdc.gov/Vaccinations/Vaccine-Hesitancy-for-COVID-19-County-and-local-es/q9mh-h2tw
 
@@
 dates - March 3, 2021 – March 15, 2021
-```{r}
-find_cross_sectional_trends('trend', '2021-03-03', 12)
+```{r vacc_hes}
+vacc_hes_data <- vroom(here('data', 'vaccine-hesitancy', 'Vaccine_Hesitancy_for_COVID-19__County_and_local_estimates.csv')) %>% 
+  janitor::clean_names() %>% 
+  mutate(fips = str_pad(fips_code, 5, pad = '0')) %>% 
+  select(fips, county_name, vacc_hesitant = estimated_hesitant_or_unsure)
+
+vacc_hes_gtrends <- find_cross_sectional_trends(c('covid conspiracy',
+                                                  'COVID-19 vaccine',
+                                                  'Coronavirus',
+                                                  'Covid-19'
+                                                  # URLdecode('%2Fg%2F11j8_9sv06'),
+                                                  # URLdecode('%2Fg%2F11j2cc_qll')
+                                                  ), 
+                            '2021-03-03', 12) %>%   
+  pivot_wider(names_from = keyword, values_from = hits)  %>% 
+  select(-date) %>% 
+  janitor::clean_names()
+
+vacc_hes <- vacc_hes_data %>% 
+  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
+  full_join(vacc_hes_gtrends, by = c('DMA_google' = 'location'))
+
+vacc_hes %>% 
+  pivot_longer(cols = covid_conspiracy:covid_19) %>% 
+  ggplot(aes(y = vacc_hesitant, x = value, color = name)) +
+  geom_point(alpha = 0.2) +
+  geom_smooth(method = "lm") +
+  facet_wrap(~ name)
+
+write_rds(vacc_hes, here('data', 'cleaned_data', 'vacc_hes.rds'))
 ```
 
-• Mask Usage
+## Mask Usage
 		○ New York Times Survey
@@
 July 2 and July 14, 2020
-```{r}
-find_cross_sectional_trends('trend', '2020-07-02', 12)
+```{r Mask}
+
+mask_data <- read_csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/mask-use/mask-use-by-county.csv') %>% 
+  rowwise() %>% 
+  mutate(mask_rare = NEVER + RARELY) %>% 
+  select(fips = COUNTYFP, mask_rare)
+
+mask_gtrends <- find_cross_sectional_trends(c('Face mask',
+                                              'Mask',
+                                              # 'Civil and political rights',
+                                              'Cloth face mask'
+                                              ),
+                                            '2020-07-02', 12)%>%   
+  pivot_wider(names_from = keyword, values_from = hits)  %>% 
+  select(-date) %>% 
+  janitor::clean_names()
+
+mask <- mask_data %>% 
+  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
+  full_join(mask_gtrends, by = c('DMA_google' = 'location'))
+
+mask %>% 
+  pivot_longer(cols = face_mask:civil_and_political_rights) %>% 
+  ggplot(aes(y = mask_rare, x = value, color = name)) +
+  geom_point(alpha = 0.2) +
+  geom_smooth(method = "lm") +
+  facet_wrap(~ name)
+
+write_rds(mask, here('data', 'cleaned_data', 'mask.rds'))
+
 ```
@@
 
-```{r}
+```{r covid}
 covid_rates <- vroom('https://raw.githubusercontent.com/nytimes/covid-19-data/master/rolling-averages/us-counties-2020.csv') %>% bind_rows(vroom('https://raw.githubusercontent.com/nytimes/covid-19-data/master/rolling-averages/us-counties-2021.csv')) %>%
@@
          fips = str_sub(geoid, start = -5)) %>% 
-  filter(wday == "Mon") %>% 
+  filter(wday == "Mon",
+         county != 'Unknown',
+         !(state %in% c('Puerto Rico', 'Virgin Islands', 'Northern Mariana Islands'))) %>% 
   select(fips, date, county, state, covid_rate = cases_avg_per_100k)
 
-covid_gtrend <- find_year_trends('Covid-19', 2020) %>% 
-  rowbind(find_year_trends('Covid-19', 2021))
+covid_gtrend_2020 <- find_year_trends('Covid-19', 2020) 
+covid_gtrend_2021 <- find_year_trends('Covid-19', 2021) 
+covid_gtrend  <- covid_gtrend_2020 %>% bind_rows(covid_gtrend_2021)
 
-find_year_trends('Cant smell', '2020-01-01', 365)
-find_year_trends('Covid-19', '2021-01-01', 365)
+taste_gtrend_2020 <- find_year_trends('Taste Loss', 2020) 
+taste_gtrend_2021 <- find_year_trends('Taste Loss', 2021) 
+taste_gtrend  <- taste_gtrend_2020 %>% bind_rows(taste_gtrend_2021)
+
+smell_gtrend_2020 <- find_year_trends('Smell Loss', 2020) 
+smell_gtrend_2021 <- find_year_trends('Smell Loss', 2021) 
+smell_gtrend  <- smell_gtrend_2020 %>% bind_rows(smell_gtrend_2021)
+
+covid <- covid_rates %>% 
+  inner_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
+  left_join(covid_gtrend, by = c('DMA_google', 'date')) %>% 
+  left_join(taste_gtrend, by = c('DMA_google', 'date')) %>% 
+  left_join(smell_gtrend, by = c('DMA_google', 'date')) %>% 
+  janitor::clean_names()
+
+covid %>% 
+  filter(fips %in% c("08003", '55057', '51059', '39085', 
+           # '36119',
+           '34021', '12071', '04017')) %>% 
+  pivot_longer(cols = c(covid_rate, covid_19, taste_loss, smell_loss)) %>% 
+  ggplot(aes(x = date, y = value, group = name, color = name)) +
+  geom_line() + 
+  geom_point() +
+  facet_wrap(~ glue('{county}, {state}'), scale = 'free_y') + 
+  theme_minimal()
+
+write_rds(covid, here('data', 'cleaned_data', 'covid.rds'))
+
 ```
@@
 
-<!-- TODO need new wonder file, this one only has 1k counties??  -->
-
 ```{r suicide}
-suicide_measures <- read_delim(here('data','suicide',
-                                    'Multiple Cause of Death, 2018-2019, Single Race.txt')) %>% 
+suicide_measures_both <- read_delim(here('data','suicide',
+                                    'Multiple Cause of Death, 1999-2020.txt')) %>% 
   janitor::clean_names() %>% 
   filter(is.na(notes)) %>% 
-  select(fips = county_code, county, deaths, population, crude_rate)
+  select(fips = county_code, county, year = year_code, deaths_both = deaths, population)
 
-suicide_gtrends <- find_cross_sectional_trends(c('suicide', 'depression', 'suicide hotline'), 
-                                               '2019-01-01', 365) %>%   
+suicide_measures_mcd <- read_delim(here('data','suicide',
+                                    'Multiple Cause of Death, 1999-2020 only multiple cause.txt')) %>% 
+  janitor::clean_names() %>% 
+  filter(is.na(notes)) %>% 
+  select(fips = county_code, county, year = year_code, deaths_mcd = deaths)
+
+breaks <-  c(10,20,40,60,100,200,400,700,1300)
+suicide_measures <- suicide_measures_both %>% 
+  left_join(suicide_measures_mcd, by = c('fips', 'county', 'year')) %>% 
+  mutate(deaths_mcd = na_if(deaths_mcd,'Missing'),
+         deaths_both = na_if(deaths_both,'Missing'),
+         deaths_mcd_supp = ifelse(deaths_mcd == 'Suppressed', '(0:9]', NA), 
+         deaths_both_supp = ifelse(deaths_both == 'Suppressed', '(0:9]', NA), 
+         deaths_mcd = na_if(deaths_mcd,'Suppressed'),
+         deaths_both = na_if(deaths_both,'Suppressed'),
+         deaths_mcd_cut = as.character(cut(as.numeric(deaths_mcd), breaks = breaks)),
+         deaths_both_cut = as.character(cut(as.numeric(deaths_both), breaks = breaks)),
+         deaths_mcd_cut = ifelse(!is.na(deaths_mcd_supp),
+                                 deaths_mcd_supp,
+                                 deaths_mcd_cut), 
+         deaths_both_cut = ifelse(!is.na(deaths_both_supp),
+                                  deaths_both_supp,
+                                  deaths_both_cut)) %>% 
+        select(fips, county, year, deaths_both_cut) %>% 
+  mutate(deaths = factor(deaths_both_cut, ordered = T),
+         deaths = fct_relevel(deaths, c("(0:9]",
+                                        "(10,20]",
+                                        "(20,40]", 
+                                        "(40,60]",
+                                        "(60,100]",    
+                                        "(100,200]",
+                                        "(200,400]",
+                                        "(400,700]",   
+                                        "(700,1.3e+03]")))
+suicide_measures %>% 
+  count(year, deaths) %>%
+  ggplot(aes(x = deaths, y = n)) +
+  geom_bar(stat = 'identity') +
+  facet_wrap(~year)
+
+append_years <- function(year_begin, year_end){
+  years <- seq(year_begin,year_end,1)
+  results <- tibble('location' = character(),
+    'suicide' = numeric(), 
+    'depression' = numeric(),
+    'suicide hotline' = numeric(),
+    'year' = numeric()
+    )
+  for (i in years){
+    print(glue("finding trends for {i}..."))
+    results <- find_cross_sectional_trends(c('suicide', 'depression', 'suicide hotline'),
+                                glue("{i}-01-01"), 365) %>%
       pivot_wider(names_from = keyword, values_from = hits)  %>%
       select(-date) %>%
-  mutate(location = str_to_lower(location))
+      mutate(year = i) %>% 
+      bind_rows(results)
+  }
+  results
+}
+
+suicide_gtrends <- append_years(2010, 2020)
 
@@
   left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
-  full_join(suicide_gtrends, by = c('DMA_google' = 'location'))
+  full_join(suicide_gtrends, by = c('DMA_google' = 'location', 'year' = 'year'))  %>% 
+  janitor::clean_names()
 
-  select(dma = DMA_google,
-         fips = county_fips, 
-         clinton_p, `Hilary Clinton`, trump_p, `Donald Trump`)
+write_rds(suicide, here('data', 'cleaned_data', 'suicide.rds'))
+
+suicide %>% 
+  filter(fips %in% c("08003", '55057', '51059', '39085', 
+           # '36119',
+           '34021', '12071', '04017')) %>% 
+  mutate(`actual deaths` = as.numeric(deaths) * 10) %>% 
+  pivot_longer(cols = c('suicide', 'depression', 'suicide_hotline', 'actual deaths')) %>% 
+  ggplot(aes(x = year, y = value, group = name, color = name)) +
+  geom_line() + 
+  geom_point() +
+  facet_wrap(~ glue('{county}'), scale = 'free_y') + 
+  theme_minimal()
+
 ```
@@
 https://github.com/tonmcg/US_County_Level_Election_Results_08-20
-```{r pres_results}
+```{r pres}
 pres_2016_results <- read_csv('https://raw.githubusercontent.com/tonmcg/US_County_Level_Election_Results_08-20/master/2016_US_County_Level_Presidential_Results.csv') %>% 
@@
          trump_p = trump / totalvotes)
-```
-```{r pres_gtrend}
+
 pres_2020_gtrend <- find_cross_sectional_trends(c('Joe Biden', 'Donald Trump'), '2020-01-01', 307) %>% 
@@
   select(-date)
-```
-```{r}
+
 pres_2016 <- pres_2016_results %>% 
@@
             "pres_2020_results", "pres_2020_gtrend"))
+
+write_rds(pres_2016, here('data', 'cleaned_data', 'pres_2016.rds'))
+write_rds(pres_2020, here('data', 'cleaned_data', 'pres_2020.rds'))

### 2022-02-18 paper1.Rmd
Done with wrangling more or less

@@
 ---
-title: "Article 1:	Information-Seeking Behaviors for Information on Covid-19 Vaccinations"
+title: "Article 1:	Construct Validity and Correspondence of Google Trends"
 author: "Kelsey Gonzalez"
@@
 output:
+  bookdown::pdf_document2:
+    latex_engine: xelatex
+    number_sections: true
   bookdown::word_document2: 
@@
     reference_docx: StylesTemplate.docx
-  bookdown::pdf_document2:
-    latex_engine: xelatex
-    number_sections: true
 header-includes:
@@
 csl: american-sociological-association.csl
-bibliography: "My Library.bib"
+bibliography: "thesis.bib"
 indent: true
@@
 
+Possible titles 
+Digital Trace Data as Social Indicators: Indicators of Attention Rather Than Support
+
 **Keywords**:
@@
 New big data sources have led to vast possibilities for social science research
-because they are bigger, cheaper, and already available  (King 2011; Lazer et
-al. 2009; Salganik 2017). Before overenthusiastically embracing these sources
+because they are bigger, cheaper, and already available
+[@kingEnsuringDataRichFuture2011; @lazerComputationalSocialScience2009;
+@salganikBitBitSocial2017]. Before overenthusiastically embracing these sources
 into our workflows, social scientists must clearly establish parameters under
-which these data sources could be operationalized (Bail 2014; Lazer et al.
-2014). As prior research outlined, the “quantity of data does not mean that one
-can ignore foundational issues of measurement and construct validity and
-reliability and dependencies among data” (Lazer et al. 2014:1203). Building on
-this prior research outlining these various issues with big data (boyd and
-Crawford 2012; Lazer 2015), this paper tests the construct validity of Google
-Search Trends as an indicator of three different cases, namely cultural
-attitudes, disease prevalence and voting behavior. These three cases will be
-tested using cultural indicators from the NORC General Social Survey, United
-States county-level suicide rates from National Center for Health Statistics, US
-cases rates of Covid-19 from The New York Times, historical US Presidential
-Election results, and the American National Election Survey. Data will be
-analyzed against corresponding operationalized Google Trends longitudinal data
-using Pearson’s r for pairwise correlations, testing for the strength of
-relationships between the Google Trend indicator and the respective comparison
-indicator. This paper will contribute to the creation of methodological norms
-and standards of how to use Google Trends as a big data source for societal
-research and serve as a critical inquiry into the adoption of big data without a
-critical eye for the ecological validity of the sources.
+which these data sources could be operationalized
+[@bailCulturalEnvironmentMeasuring2014; @lazerParableGoogleFlu2014]. As prior
+research outlined, the “quantity of data does not mean that one can ignore
+foundational issues of measurement and construct validity and reliability and
+dependencies among data” [@lazerParableGoogleFlu2014, p. 1203]. Building on this
+prior research outlining these various issues with big data
+[@boydCriticalQuestionsBig2012; @lazerIssuesConstructValidity2015], this paper
+tests the construct validity of Google Search Trends as an indicator of three
+different cases, namely cultural attitudes, disease prevalence and voting
+behavior. These three cases will be tested using cultural indicators from the
+NORC General Social Survey, United States county-level suicide rates from
+National Center for Health Statistics, US cases rates of Covid-19 from The New
+York Times, historical US Presidential Election results, and the American
+National Election Survey. Data will be analyzed against corresponding
+operationalized Google Trends longitudinal data using Pearson’s r for pairwise
+correlations, testing for the strength of relationships between the Google Trend
+indicator and the respective comparison indicator. This paper will contribute to
+the creation of methodological norms and standards of how to use Google Trends
+as a big data source for societal research and serve as a critical inquiry into
+the adoption of big data without a critical eye for the ecological validity of
+the sources.
 
@@
 methods that lead to groundbreaking results that are shown to be reliable. As an
-example, Blumenstock et al. (2015) use county-level cell-phone records to
-construct the distribution of poverty and wealth in Rwanda, a country where
-national surveys and censes are rare and costly. However, Blumenstock et al.
-(2015) go to great lengths to demonstrate that their operationalization of the
-cell phone data creates a reliable and valid construct; few social science
-papers utilizing big data dig into the construct validity of their metrics to
-this extent and even fewer publications focus on methodological guidelines of
-how to use sources of big data (Asseo et al. 2020; Stiles and Grogan-Myers
-2018). However, research has shown the small adjustments to an algorithm or
-metric may void any research insight we are able to pull from such data (Lazer
-et al. 2014). Because of this, I propose a methodological validation study of
-the Google Search Trends source of big data to investigate how it is advisable
-to utilize this data in social scientific research.
+example, @blumenstockPredictingPovertyWealth2015 use
+county-level cell-phone records to construct the distribution of poverty and
+wealth in Rwanda, a country where national surveys and censes are rare and
+costly. However, @blumenstockPredictingPovertyWealth2015
+go to great lengths to demonstrate that their operationalization of the cell
+phone data creates a reliable and valid construct; few social science papers
+utilizing big data dig into the construct validity of their metrics to this
+extent and even fewer publications focus on methodological guidelines of how to
+use sources of big data [@asseoTrackingCOVID19Using2020;
+@stilesAssessingCriterionValidity2018]. However, research has shown the small
+adjustments to an algorithm or metric may void any research insight we are able
+to pull from such data [@lazerParableGoogleFlu2014]. Because of this, I propose
+a methodological validation study of the Google Search Trends source of big data
+to investigate how it is advisable to utilize this data in social scientific
+research.
 
@@
 an operationalization of cultural attitudes with the General Social Survey.
-After Bail (2014)’s call for cultural sociologists to utilize the ever expanding
-world of big data, Google trends as a data source began appearing in
-sociological and social science research.  From research on mass shootings and
-firearms (Brownstein, Nahari, and Reis 2020; Semenza and Bernau 2020), protest
-and anti-Muslim sentiment (Bail, Merhout, and Ding 2018; Barrie 2020; Gross and
-Mann 2017), to analyzing country-level changes in social perception (Reyes,
-Majluf, and Ibáñez 2018), Google search trends are a new and innovative
+After @bailCulturalEnvironmentMeasuring2014’s call for cultural
+sociologists to utilize the ever-expanding world of big data, Google trends as a
+data source began appearing in sociological and social science research.  From
+research on mass shootings and firearms [@brownsteinInternetSearchPatterns2020;
+@semenzaInformationseekingWakeTragedy2020], protest and anti-Muslim sentiment
+[@bailUsingInternetSearch2018; @barrieSearchingRacismGeorge2020;
+@grossThereFergusonEffect2017], to analyzing country-level changes in social
+perception [@reyes_etal18], Google search trends are a new and innovative
 indicator of cultural interest. Extending into social networks and culture,
-Bail, Brown and Wimmer (2019) even used Google trends to measure how culture
-spreads around the globe.
+@bailPrestigeProximityPrejudice2019 even used Google
+trends to measure how culture spreads around the globe.
 
@@
 Internet Research. While much of this research has focused on the Covid-19
-pandemic (Jimenez et al. 2020a, 2020b; Lim et al. 2020:20; Mavragani and Gkillas
-2020; Nguyen et al. 2020; Todorova, Tsankova, and Ermenlieva 2021), other
-research has investigated Google Trends as an indicator of wellbeing (Brodeur et
-al. 2021; Carpi et al. 2020; Du et al. 2020), suicidality (Burnett, Eapen, and
-Lin 2020), vaccination uptake (Dalum Hansen, Lioma, and Mølbak 2016), obesity
-(Sarigul and Rui 2014), and even insomnia (Zitting et al. 2020), to cover a few
-examples. For a partial review of other utilizations, see Nuti et al. (2014).
-According to Jaidka et al (2021), the majority of studies profess a correlation
-of > .70, “demonstrating the vast potential of Google Search as a proxy for
-monitoring population health” (p. 3) based on assumptions that individuals
-search because of self-diagnosis and to identify possible courses of treatment
-(De Choudhury, Morris, and White 2014).
+pandemic [@jimenez_etal20; @jimenezCOVID19SymptomGoogle2020;
+@limEstimatingInformationSeekingBehaviour2020;
+@mavraganiCOVID19PredictabilityUnited2020; @nguyenGoogleTrendsAnalysis2020;
+@todorovaInternetBasedData2021] , other research has investigated Google Trends
+as an indicator of wellbeing [@brodeurCOVID19LockdownsWellbeing2021;
+@carpiTwitterSubjectiveWellBeing2020; @duCOVID19IncreasesOnline2020],
+suicidality [@burnettTimeTrendsPublic2020], vaccination uptake
+[@dalumhansenEnsembleLearnedVaccination2016], obesity
+[@sarigulNowcastingObesityUsing2014], and even insomnia
+[@zittingGoogleTrendsReveal2020], to cover a few examples. For a partial
+review of other utilizations, see @nutiUseGoogleTrends2014. According to
+@jaidkaInformationseekingVsSharing2021, the majority of studies profess a
+correlation of > .70, “demonstrating the vast potential of Google Search as a
+proxy for monitoring population health” (p. 3) based on assumptions that
+individuals search because of self-diagnosis and to identify possible courses
+of treatment [@dechoudhurySeekingSharingHealth2014].
+
+<!-- Following reports say that Google searches can predict covid  -->
+<!-- 14. Brunori, P. & Resce, G. Searching for the peak Google Trends and the Covid-19 outbreak in Italy. SERIES working papers N. 04/2020 -->
+<!-- Lampos, V. et al. Tracking COVID-19 using online search. Preprint at https://arxiv.org/abs/2003.08086 (2020). -->
+<!-- 16. Walker, A., Hopkins, C. & Surda, P. The use of google trends to investigate the loss of smell related searches during COVID‐19 -->
+<!-- outbreak. Int. Forum Allergy Rh. 10, 839–847 (2020). -->
+<!-- 17. Stephens-Davidowitz, S. Google Searches Can Help Us Find Emerging Covid-19 Outbreaks. The New York Times https://www. -->
+<!-- nytimes.com/2020/04/05/opinion/coronavirus-google-searches.html (2020). -->
+<!-- 18.
+Frank, T.
+Goldman says fewer ‘loss of smell’ Google queries suggest better COVID outlook.
+Consumer News and Business Channel.
+CNBC https://www.cnbc.com/2020/04/15/goldman-says-fewer-loss-of-smell-google-searches-is-a-positive-sign-for-pande -->
+<!-- mic.html (2020) -->
 
 Various sources have also used Google Trends as a way to forecast political
-elections and political attitudes (Wolf 2018). For instance, Swearingen and
-Ripberger (2014) investigate how U.S. Senate Elections relate to attention
-measured by search traffic. Prado-Román et al. (2020) compare how Google Search
-trends are able to predict presidential election results in both the United
-States and Canada. Finally, the OECD Development Centre is investigating how
-Google data can help elucidate governments’ approval in Latin America (Montoya
-et al. 2020)
+elections and political attitudes [@wolfTrendingRightDirection2018]. For
+instance, @swearingenGoogleInsightsSenate2014 investigate how U.S. Senate
+Elections relate to attention measured by search traffic.
+@prado-romanGoogleTrendsPredictor2020 compare how Google Search trends are able
+to predict presidential election results in both the United States and Canada.
+Finally, the OECD Development Centre is investigating how Google data can help
+elucidate governments’ approval in Latin America [@montoyaUsingGoogleData2020].
 
@@
 indicator for uses in social science research?
+
+https://journals.sagepub.com/doi/10.1177/0894439316631043
+			§ What constructs might google trends capture and not capture well? 
+Capture attention but not attitudes
+
+Also Asseo - "we assumed that media coverage may potentially decouple the search
+popularity from the number of cases, since searches would result not only from
+self-symptoms, but also from interest elicited by media coverage."
 
@@
 health sciences and business. Once I assess how this data can be used, I would
-like to be able to join Bail (2014) in encouraging social scientists to pursue
+like to be able to join @bailCulturalEnvironmentMeasuring2014 in encouraging social scientists to pursue
 more research with big data while taking into account the potential pitfalls
-with any source of big data (McFarland and McFarland 2015).
+with any source of big data [@mcfarlandBigDataDanger2015].
 

### 2022-02-19 paper1-cleaning.Rmd
write initial data and methods

@@
                                                   ), 
-                            '2021-03-03', 12) %>%   
+                            '2021-05-26', 12) %>%   
   pivot_wider(names_from = keyword, values_from = hits)  %>% 
@@
                                               'Mask',
-                                              # 'Civil and political rights',
                                               'Cloth face mask'
@@
 
+corona_gtrend_2020 <- find_year_trends('Coronavirus', 2020) 
+corona_gtrend_2021 <- find_year_trends('Coronavirus', 2021) 
+corona_gtrend  <- corona_gtrend_2020 %>% bind_rows(corona_gtrend_2021)
+
 taste_gtrend_2020 <- find_year_trends('Taste Loss', 2020) 
@@
 
+covid <- covid %>% 
+  left_join(corona_gtrend, by = c('DMA_google', 'date')) %>% 
+  group_by(fips) %>%
+  mutate(covid_rate  = na.approx(covid_rate, na.rm = FALSE),
+         covid_19    = na.approx(covid_19, na.rm = FALSE),
+         coronavirus = na.approx(coronavirus, na.rm = FALSE),
+         taste_loss  = na.approx(taste_loss, na.rm = FALSE),
+         smell_loss  = na.approx(smell_loss, na.rm = FALSE))
+
 write_rds(covid, here('data', 'cleaned_data', 'covid.rds'))
@@
 ```{r suicide}
-suicide_measures_both <- read_delim(here('data','suicide',
-                                    'Multiple Cause of Death, 1999-2020.txt')) %>% 
+# suicide_measures_both <- read_delim(here('data','suicide',
+#                                     'Multiple Cause of Death, 1999-2020.txt')) %>% 
+#   janitor::clean_names() %>% 
+#   filter(is.na(notes)) %>% 
+#   select(fips = county_code, county, year = year_code, deaths_both = deaths, population)
+# 
+# suicide_measures_mcd <- read_delim(here('data','suicide',
+#                                     'Multiple Cause of Death, 1999-2020 only multiple cause.txt')) %>% 
+#   janitor::clean_names() %>% 
+#   filter(is.na(notes)) %>% 
+#   select(fips = county_code, county, year = year_code, deaths_mcd = deaths)
+# 
+# breaks <-  c(10,20,40,60,100,200,400,700,1300)
+# suicide_measures <- suicide_measures_both %>% 
+#   left_join(suicide_measures_mcd, by = c('fips', 'county', 'year')) %>% 
+#   mutate(deaths_mcd = na_if(deaths_mcd,'Missing'),
+#          deaths_both = na_if(deaths_both,'Missing'),
+#          deaths_mcd_supp = ifelse(deaths_mcd == 'Suppressed', '(0:9]', NA), 
+#          deaths_both_supp = ifelse(deaths_both == 'Suppressed', '(0:9]', NA), 
+#          deaths_mcd = na_if(deaths_mcd,'Suppressed'),
+#          deaths_both = na_if(deaths_both,'Suppressed'),
+#          deaths_mcd_cut = as.character(cut(as.numeric(deaths_mcd), breaks = breaks)),
+#          deaths_both_cut = as.character(cut(as.numeric(deaths_both), breaks = breaks)),
+#          deaths_mcd_cut = ifelse(!is.na(deaths_mcd_supp),
+#                                  deaths_mcd_supp,
+#                                  deaths_mcd_cut), 
+#          deaths_both_cut = ifelse(!is.na(deaths_both_supp),
+#                                   deaths_both_supp,
+#                                   deaths_both_cut)) %>% 
+#         select(fips, county, year, deaths_both_cut) %>% 
+#   mutate(deaths = factor(deaths_both_cut, ordered = T),
+#          deaths = fct_relevel(deaths, c("(0:9]",
+#                                         "(10,20]",
+#                                         "(20,40]", 
+#                                         "(40,60]",
+#                                         "(60,100]",    
+#                                         "(100,200]",
+#                                         "(200,400]",
+#                                         "(400,700]",   
+#                                         "(700,1.3e+03]")))
+# suicide_measures %>% 
+#   count(year, deaths) %>%
+#   ggplot(aes(x = deaths, y = n)) +
+#   geom_bar(stat = 'identity') +
+#   facet_wrap(~year)
+
+suicide_measures <- read_delim(here('data','suicide',
+                                    'Multiple Cause of Death, 1999-2020 only multiple cause.txt'),
+                               show_col_types = FALSE) %>% 
   janitor::clean_names() %>% 
   filter(is.na(notes)) %>% 
-  select(fips = county_code, county, year = year_code, deaths_both = deaths, population)
-
-suicide_measures_mcd <- read_delim(here('data','suicide',
-                                    'Multiple Cause of Death, 1999-2020 only multiple cause.txt')) %>% 
-  janitor::clean_names() %>% 
-  filter(is.na(notes)) %>% 
-  select(fips = county_code, county, year = year_code, deaths_mcd = deaths)
-
-breaks <-  c(10,20,40,60,100,200,400,700,1300)
-suicide_measures <- suicide_measures_both %>% 
-  left_join(suicide_measures_mcd, by = c('fips', 'county', 'year')) %>% 
-  mutate(deaths_mcd = na_if(deaths_mcd,'Missing'),
-         deaths_both = na_if(deaths_both,'Missing'),
-         deaths_mcd_supp = ifelse(deaths_mcd == 'Suppressed', '(0:9]', NA), 
-         deaths_both_supp = ifelse(deaths_both == 'Suppressed', '(0:9]', NA), 
-         deaths_mcd = na_if(deaths_mcd,'Suppressed'),
-         deaths_both = na_if(deaths_both,'Suppressed'),
-         deaths_mcd_cut = as.character(cut(as.numeric(deaths_mcd), breaks = breaks)),
-         deaths_both_cut = as.character(cut(as.numeric(deaths_both), breaks = breaks)),
-         deaths_mcd_cut = ifelse(!is.na(deaths_mcd_supp),
-                                 deaths_mcd_supp,
-                                 deaths_mcd_cut), 
-         deaths_both_cut = ifelse(!is.na(deaths_both_supp),
-                                  deaths_both_supp,
-                                  deaths_both_cut)) %>% 
-        select(fips, county, year, deaths_both_cut) %>% 
-  mutate(deaths = factor(deaths_both_cut, ordered = T),
-         deaths = fct_relevel(deaths, c("(0:9]",
-                                        "(10,20]",
-                                        "(20,40]", 
-                                        "(40,60]",
-                                        "(60,100]",    
-                                        "(100,200]",
-                                        "(200,400]",
-                                        "(400,700]",   
-                                        "(700,1.3e+03]")))
-suicide_measures %>% 
-  count(year, deaths) %>%
-  ggplot(aes(x = deaths, y = n)) +
-  geom_bar(stat = 'identity') +
-  facet_wrap(~year)
+  select(fips = county_code, county, year = year_code, deaths, population) %>% 
+  mutate(across(c(deaths, population), ~na_if(.x,'Missing')),
+         deaths = ifelse(deaths == 'Suppressed', '9', deaths), 
+         population = na_if(population,'Suppressed'),
+         across(c(deaths, population), as.numeric),
+         death_rate = (deaths/ population) * 1000)
 
@@
 
+suicide <- suicide %>% 
+  group_by(fips) %>%
+  mutate(deaths           = na.approx(deaths, na.rm = FALSE),
+         population       = na.approx(population, na.rm = FALSE),
+         suicide          = na.approx(suicide, na.rm = FALSE),
+         depression       = na.approx(depression, na.rm = FALSE),
+         suicide_hotline  = na.approx(suicide_hotline, na.rm = FALSE))
+
 write_rds(suicide, here('data', 'cleaned_data', 'suicide.rds'))
@@
            '34021', '12071', '04017')) %>% 
-  mutate(`actual deaths` = as.numeric(deaths) * 10) %>% 
-  pivot_longer(cols = c('suicide', 'depression', 'suicide_hotline', 'actual deaths')) %>% 
+  mutate(death_rate = death_rate * 100) %>% 
+  pivot_longer(cols = c('suicide', 'depression', 'suicide_hotline', 'death_rate')) %>% 
   ggplot(aes(x = year, y = value, group = name, color = name)) +

### 2022-02-19 paper1.Rmd
write initial data and methods

@@
   chunk_output_type: console
+  markdown: 
+    wrap: 72
 output:
@@
 pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
-               modelsummary, showtext, thematic, kableExtra, scales)
+               modelsummary, showtext, thematic, kableExtra, scales,
+               rmcorr)
 
@@
 
-conf_int_prop <- function(var){
-  p <- mean(!!var, na.rm = T)
-  q <- 1 - p
-  n <- nrow(rain)
-  min <- p - 1.96*sqrt((p*q)/n)
-  max <- p + 1.96*sqrt((p*q)/n) 
-  paste0(label_percent()(min), ", ", label_percent()(max))
-}
-print_perc <- function(var){
-  label_percent()(mean(var, na.rm = T))
-}
-
+```
+```{r data}
+vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
+mask <- read_rds(here('data', 'cleaned_data', 'mask.rds'))
+covid <- read_rds(here('data', 'cleaned_data', 'covid.rds'))
+suicide <- read_rds(here('data', 'cleaned_data', 'suicide.rds'))
+pres_2016 <- read_rds(here('data', 'cleaned_data', 'pres_2016.rds'))
+pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))
 ```
@@
 
-Possible titles 
-Digital Trace Data as Social Indicators: Indicators of Attention Rather Than Support
+Possible titles Digital Trace Data as Social Indicators: Indicators of
+Attention Rather Than Support
 
@@
 # Intro
-New big data sources have led to vast possibilities for social science research
-because they are bigger, cheaper, and already available
+
+New big data sources have led to vast possibilities for social science
+research because they are bigger, cheaper, and already available
 [@kingEnsuringDataRichFuture2011; @lazerComputationalSocialScience2009;
-@salganikBitBitSocial2017]. Before overenthusiastically embracing these sources
-into our workflows, social scientists must clearly establish parameters under
-which these data sources could be operationalized
-[@bailCulturalEnvironmentMeasuring2014; @lazerParableGoogleFlu2014]. As prior
-research outlined, the “quantity of data does not mean that one can ignore
-foundational issues of measurement and construct validity and reliability and
-dependencies among data” [@lazerParableGoogleFlu2014, p. 1203]. Building on this
-prior research outlining these various issues with big data
-[@boydCriticalQuestionsBig2012; @lazerIssuesConstructValidity2015], this paper
-tests the construct validity of Google Search Trends as an indicator of three
-different cases, namely cultural attitudes, disease prevalence and voting
-behavior. These three cases will be tested using cultural indicators from the
-NORC General Social Survey, United States county-level suicide rates from
-National Center for Health Statistics, US cases rates of Covid-19 from The New
-York Times, historical US Presidential Election results, and the American
-National Election Survey. Data will be analyzed against corresponding
-operationalized Google Trends longitudinal data using Pearson’s r for pairwise
-correlations, testing for the strength of relationships between the Google Trend
-indicator and the respective comparison indicator. This paper will contribute to
-the creation of methodological norms and standards of how to use Google Trends
-as a big data source for societal research and serve as a critical inquiry into
-the adoption of big data without a critical eye for the ecological validity of
-the sources.
+@salganikBitBitSocial2017]. Before overenthusiastically embracing these
+sources into our workflows, social scientists must clearly establish
+parameters under which these data sources could be operationalized
+[@bailCulturalEnvironmentMeasuring2014; @lazerParableGoogleFlu2014]. As
+prior research outlined, the "quantity of data does not mean that one
+can ignore foundational issues of measurement and construct validity and
+reliability and dependencies among data" \[@lazerParableGoogleFlu2014,
+p. 1203\]. Building on this prior research outlining these various
+issues with big data [@boydCriticalQuestionsBig2012;
+@lazerIssuesConstructValidity2015], this paper tests the construct
+validity of Google Search Trends as an indicator of three different
+cases, namely cultural attitudes, disease prevalence and voting
+behavior. These three cases will be tested using cultural indicators
+from the NORC General Social Survey, United States county-level suicide
+rates from National Center for Health Statistics, US cases rates of
+Covid-19 from The New York Times, historical US Presidential Election
+results, and the American National Election Survey. Data will be
+analyzed against corresponding operationalized Google Trends
+longitudinal data using Pearson's r for pairwise correlations, testing
+for the strength of relationships between the Google Trend indicator and
+the respective comparison indicator. This paper will contribute to the
+creation of methodological norms and standards of how to use Google
+Trends as a big data source for societal research and serve as a
+critical inquiry into the adoption of big data without a critical eye
+for the ecological validity of the sources.
 
-With the expansion of big data, some research has shown extremely innovative
-methods that lead to groundbreaking results that are shown to be reliable. As an
-example, @blumenstockPredictingPovertyWealth2015 use
-county-level cell-phone records to construct the distribution of poverty and
-wealth in Rwanda, a country where national surveys and censes are rare and
-costly. However, @blumenstockPredictingPovertyWealth2015
-go to great lengths to demonstrate that their operationalization of the cell
-phone data creates a reliable and valid construct; few social science papers
-utilizing big data dig into the construct validity of their metrics to this
-extent and even fewer publications focus on methodological guidelines of how to
-use sources of big data [@asseoTrackingCOVID19Using2020;
-@stilesAssessingCriterionValidity2018]. However, research has shown the small
-adjustments to an algorithm or metric may void any research insight we are able
-to pull from such data [@lazerParableGoogleFlu2014]. Because of this, I propose
-a methodological validation study of the Google Search Trends source of big data
-to investigate how it is advisable to utilize this data in social scientific
-research.
+With the expansion of big data, some research has shown extremely
+innovative methods that lead to groundbreaking results that are shown to
+be reliable. As an example, @blumenstockPredictingPovertyWealth2015 use
+county-level cell-phone records to construct the distribution of poverty
+and wealth in Rwanda, a country where national surveys and censes are
+rare and costly. However, @blumenstockPredictingPovertyWealth2015 go to
+great lengths to demonstrate that their operationalization of the cell
+phone data creates a reliable and valid construct; few social science
+papers utilizing big data dig into the construct validity of their
+metrics to this extent and even fewer publications focus on
+methodological guidelines of how to use sources of big data
+[@asseoTrackingCOVID19Using2020; @stilesAssessingCriterionValidity2018].
+However, research has shown the small adjustments to an algorithm or
+metric may void any research insight we are able to pull from such data
+[@lazerParableGoogleFlu2014]. Because of this, I propose a
+methodological validation study of the Google Search Trends source of
+big data to investigate how it is advisable to utilize this data in
+social scientific research.
 
-I will use three categorizations of ways I propose Google Trends could be
-operationalized for social scientific usage. First, I’ll test Google Trends as
-an operationalization of cultural attitudes with the General Social Survey.
-After @bailCulturalEnvironmentMeasuring2014’s call for cultural
-sociologists to utilize the ever-expanding world of big data, Google trends as a
-data source began appearing in sociological and social science research.  From
-research on mass shootings and firearms [@brownsteinInternetSearchPatterns2020;
-@semenzaInformationseekingWakeTragedy2020], protest and anti-Muslim sentiment
-[@bailUsingInternetSearch2018; @barrieSearchingRacismGeorge2020;
-@grossThereFergusonEffect2017], to analyzing country-level changes in social
-perception [@reyes_etal18], Google search trends are a new and innovative
-indicator of cultural interest. Extending into social networks and culture,
-@bailPrestigeProximityPrejudice2019 even used Google
-trends to measure how culture spreads around the globe.
+I will use three categorizations of ways I propose Google Trends could
+be operationalized for social scientific usage. First, I'll test Google
+Trends as an operationalization of cultural attitudes with the General
+Social Survey. After @bailCulturalEnvironmentMeasuring2014's call for
+cultural sociologists to utilize the ever-expanding world of big data,
+Google trends as a data source began appearing in sociological and
+social science research. From research on mass shootings and firearms
+[@brownsteinInternetSearchPatterns2020;
+@semenzaInformationseekingWakeTragedy2020], protest and anti-Muslim
+sentiment [@bailUsingInternetSearch2018;
+@barrieSearchingRacismGeorge2020; @grossThereFergusonEffect2017], to
+analyzing country-level changes in social perception [@reyes_etal18],
+Google search trends are a new and innovative indicator of cultural
+interest. Extending into social networks and culture,
+@bailPrestigeProximityPrejudice2019 even used Google trends to measure
+how culture spreads around the globe.
 
-Google Search Trends have also been used continuously in estimations of disease
-prevalence and population health in journals like the Journal of Medical
-Internet Research. While much of this research has focused on the Covid-19
-pandemic [@jimenez_etal20; @jimenezCOVID19SymptomGoogle2020;
+Google Search Trends have also been used continuously in estimations of
+disease prevalence and population health in journals like the Journal of
+Medical Internet Research. While much of this research has focused on
+the Covid-19 pandemic [@jimenez_etal20;
+@jimenezCOVID19SymptomGoogle2020;
 @limEstimatingInformationSeekingBehaviour2020;
-@mavraganiCOVID19PredictabilityUnited2020; @nguyenGoogleTrendsAnalysis2020;
-@todorovaInternetBasedData2021] , other research has investigated Google Trends
-as an indicator of wellbeing [@brodeurCOVID19LockdownsWellbeing2021;
+@mavraganiCOVID19PredictabilityUnited2020;
+@nguyenGoogleTrendsAnalysis2020; @todorovaInternetBasedData2021] , other
+research has investigated Google Trends as an indicator of wellbeing
+[@brodeurCOVID19LockdownsWellbeing2021;
 @carpiTwitterSubjectiveWellBeing2020; @duCOVID19IncreasesOnline2020],
@@
 review of other utilizations, see @nutiUseGoogleTrends2014. According to
-@jaidkaInformationseekingVsSharing2021, the majority of studies profess a
-correlation of > .70, “demonstrating the vast potential of Google Search as a
-proxy for monitoring population health” (p. 3) based on assumptions that
-individuals search because of self-diagnosis and to identify possible courses
-of treatment [@dechoudhurySeekingSharingHealth2014].
+@jaidkaInformationseekingVsSharing2021, the majority of studies profess
+a correlation of \> .70, "demonstrating the vast potential of Google
+Search as a proxy for monitoring population health" (p. 3) based on
+assumptions that individuals search because of self-diagnosis and to
+identify possible courses of treatment
+[@dechoudhurySeekingSharingHealth2014].
 
 <!-- Following reports say that Google searches can predict covid  -->
+
 <!-- 14. Brunori, P. & Resce, G. Searching for the peak Google Trends and the Covid-19 outbreak in Italy. SERIES working papers N. 04/2020 -->
+
 <!-- Lampos, V. et al. Tracking COVID-19 using online search. Preprint at https://arxiv.org/abs/2003.08086 (2020). -->
+
 <!-- 16. Walker, A., Hopkins, C. & Surda, P. The use of google trends to investigate the loss of smell related searches during COVID‐19 -->
+
 <!-- outbreak. Int. Forum Allergy Rh. 10, 839–847 (2020). -->
+
 <!-- 17. Stephens-Davidowitz, S. Google Searches Can Help Us Find Emerging Covid-19 Outbreaks. The New York Times https://www. -->
+
 <!-- nytimes.com/2020/04/05/opinion/coronavirus-google-searches.html (2020). -->
+
 <!-- 18.
@@
 CNBC https://www.cnbc.com/2020/04/15/goldman-says-fewer-loss-of-smell-google-searches-is-a-positive-sign-for-pande -->
+
 <!-- mic.html (2020) -->
 
-Various sources have also used Google Trends as a way to forecast political
-elections and political attitudes [@wolfTrendingRightDirection2018]. For
-instance, @swearingenGoogleInsightsSenate2014 investigate how U.S. Senate
+Various sources have also used Google Trends as a way to forecast
+political elections and political attitudes
+[@wolfTrendingRightDirection2018]. For instance,
+@swearingenGoogleInsightsSenate2014 investigate how U.S. Senate
 Elections relate to attention measured by search traffic.
-@prado-romanGoogleTrendsPredictor2020 compare how Google Search trends are able
-to predict presidential election results in both the United States and Canada.
-Finally, the OECD Development Centre is investigating how Google data can help
-elucidate governments’ approval in Latin America [@montoyaUsingGoogleData2020].
+@prado-romanGoogleTrendsPredictor2020 compare how Google Search trends
+are able to predict presidential election results in both the United
+States and Canada. Finally, the OECD Development Centre is investigating
+how Google data can help elucidate governments' approval in Latin
+America [@montoyaUsingGoogleData2020].
 
-Research Question - How can we operationalize Google Search Trends as a valid
-indicator for uses in social science research?
+Research Question - How can we operationalize Google Search Trends as a
+valid indicator for uses in social science research?
 
-https://journals.sagepub.com/doi/10.1177/0894439316631043
-			§ What constructs might google trends capture and not capture well? 
-Capture attention but not attitudes
+<https://journals.sagepub.com/doi/10.1177/0894439316631043> § What
+constructs might google trends capture and not capture well? Capture
+attention but not attitudes
 
-Also Asseo - "we assumed that media coverage may potentially decouple the search
-popularity from the number of cases, since searches would result not only from
-self-symptoms, but also from interest elicited by media coverage."
+Also Asseo - "we assumed that media coverage may potentially decouple
+the search popularity from the number of cases, since searches would
+result not only from self-symptoms, but also from interest elicited by
+media coverage."
 
@@
 To investigate the construct and criterion validity of the use of Google Trends
-in these three areas, I will gather geo-located data from a sources related to
-each case and use Pearson’s r for pairwise correlations, testing for the
-strength of relationship between the Google Trend indicator and the respective
-comparison indicator. Pairwise correlations allow for testing of nested data,
-allowing for multiple search terms to be compared across locations
-simultaneously as well as comparing change over time. I will test both raw
-questions with raw trends as well as using dimensionality reduction through
-factor analysis and principal components analysis (PCA). In addition, I’d like
-to explore how this data would cluster locations together using tools like
-blockmodeling and other clustering techniques.
+in these three areas, I gathered geo-located social science data across multiple
+sources to address the three areas of inquiry for this paper.  Table
+\@ref(tab:data-sources-table) outlines which data sources are used for this
+project and which trends are matched to each source.
 
-To investigate the correlation between Google search trends, I will use
-questions from the NORC General Social Survey. I will need to obtain an $800
-grant to purchase geolocated data from NORC for this project. I plan to submit a
-small grant application to SBS to receive these funds. I will use various NORC
-GSS cultural value questions and aggregate the relevant zip code up to Nielsen’s
-metropolitan market area (MMA), the level Google trends are aggregated to, using
-population weighting.
+```{r data-sources-table}
+#| results='asis',
+#| tab.cap = 'airquality dataset caption here'
 
-For disease prevalence, I will use United States county-level suicide rates from
-National Center for Health Statistics, US cases rates of Covid-19 from The New
-York Times, and obesity rates to compare search trends to observable data.
+data_sources <- tibble::tribble(
+~Validated.Data.Source, ~Type, ~Dates, ~Google.Trends.Used,
+"General Social Survey", "Cross-Sectional", "2010 - 2020", NA,
 
-Finally, I’ll test Google Trends as an operationalization of political attitudes
-by looking at actual voting outcomes in historical US Presidential Election
-results and the American National Election Survey and Google Trends about
-candidates.
+"Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "covid conspiracy', 'COVID-19 vaccine', 'Coronavirus', 'Covid-19'",
 
-```{r}
-tibble::tribble(
-                                ~Validated.source, ~Google.trend.equivalent,
-                                            "GSS",                       NA,
-  "Suicide,\\nCovid-19 rates\\nVaccine hesitancy",                       NA,
-           "Presidential Voting outcomes,\\nANES",                       NA
+"Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "'Face Mask', 'Mask', 'Cloth Face Mask'",
+
+ "Covid Rates", "Longitudinal", "Every Monday, 2020 - 2021", "'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss'",
+
+"County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "'Suicide', 'Depression',' Suicide Hotline'",
+
+"American National Election Survey", "Cross-Sectional", "2020", NA,
+
+"Presidential Election Results", "Cross Sectional", "2016 & 2020", "'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
  )
+
+data_sources %>% 
+  kbl() %>%
+  # group rows
+  pack_rows("Behaviors and Attitudes", 1,3, background = '#bad7db', bold = T) %>% 
+  pack_rows("Health", 4,5, background = '#bad7db', bold = T) %>% 
+  pack_rows('Political', 6,7, background = '#bad7db', bold = T) %>% 
+  # header style
+  row_spec(0, background = my_palette[8], color = 'white', bold = T) %>% 
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
 
@@
 ## Measures
+### Google Trends
+This paper focuses on a validation of Google search trends [@googletrends].
+Google trends portray the search frequency for specific search terms across
+designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
+counties to 210 media markets based on similar population clusters [@dma_key].
+Raw data is on a scale from 0 to 100, with 100 being the maximum search
+popularity out of all DMAs. Google Search Trend are now only available
+cross-sectionally (a single time period across a geography) or as time-series (a
+single geo-location across time). To remedy this and build a longitudinal
+dataset of each search topic for the longitudinal datasets, I follow the method
+proposed in @park_etal (p. 5). This method involves building a dataset of
+unscaled cross-sectional values, selecting a DMA to use to establish the
+rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
+values for the one DMA. To find the rescaling ratio for each week in the
+time-series, you divide the time-series value for each week by the
+cross-sectional value for each week, resulting in a rescaling vector to be used
+for all weeks in the dataset across geographies. To rescale each longitudinal
+value, multiply the respective week's rescaling ratio by the cross-sectional
+value. Rescaled longitudinal data was compared against time-series data for
+multiple test counties and was equivalent. For a more in-depth explanation of
+this procedure, see @park_etal (p. 5). Missing datapoints in longitudinal
+datasets were filled in with interpolated values using `zoo::na.approx()`
+[@zoo].
+
 ### attitudinal
-• Vaccine Hesitancy
-		○ https://data.cdc.gov/Vaccinations/Vaccine-Hesitancy-for-COVID-19-County-and-local-es/q9mh-h2tw/data
 
-• Mask Usage
-		○ New York Times Survey
+<!-- [@gss_data] (let's see if I get access first) -->
+
+One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
+[@vaches_data]. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
+(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
+Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
+vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
+of `r nrow(vacc_hes)` observations, one for each U.S. County.
+
+Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
+Dynata for the New York Times from July 2 through 14, 2020 [@mask_data]. 250,000
+survey respondents were asked, "How often do you wear a mask in public when you
+expect to be within six feet of another person?". The NYT weighted each response
+to create a county level measure of what percent of the county never, rarely,
+sometimes, frequetly, and always wore a mask when in public. This dataset
+consists of `r nrow(mask)` observations, one for each U.S. County.
 
 ### health
-• Covid Rates
-		○ https://github.com/nytimes/covid-19-data/tree/master/rolling-averages
 
-• Suicide
-		○ https://wonder.cdc.gov/mcd.html 
-		○ Multiple Cause of Death Data 2019 (see notes for which variables count)
+I first use U.S. Covid-19 rates to validate health and disease related topics. I
+retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
+data based on reports from state and local health agencies. It is widely
+acknowledged that there are biases in this data due to inconsistencies and
+availability in testing as well as different community propensity to test
+[@gu22; @cdc20a] However, it is the best measure we have of actual case rates.
+Case Rate is measured as number of cases per 100,000 population. Observations
+vary from a minimum of 0 to a maximum of `r max(covid$covid_rate))` for each 
+Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
+There are `r nrow(covid)` cases across `r nrow(count(covid, fips))` 
+counties and `r nrow(count(covid, date))` dates. Missing data were interpolated 
+using `zoo::na.approx()` [@zoo].
+
+I also use county-level suicide rates from the US Centers for Disease Control
+and Prevention [-@suic_data]. Data is grouped by year from 2010-2020. Raw death
+rates are scaled by population size for each year. There are `r nrow(suicide)` 
+total cases, resulting from `r nrow(count(suicide, year))` observations of 
+`r nrow(count(suicide, fips))` counties. Missing data were interpolated 
+using `zoo::na.approx()` [@zoo].
 
 ### political
-• Presidential results
-		○ https://dataverse.harvard.edu/dataset.xhtml?persistentId=doi:10.7910/DVN/VOQCHQ
-		○ MIT Election Data and Science Lab, 2018, 
-		○ "County Presidential Election Returns 2000-2020",
-		○ https://doi.org/10.7910/DVN/VOQCHQ, 
-		○ Harvard Dataverse, V9
+Finally, I test Google Trends as an operationalization of political
+attitudes by first looking at actual voting outcomes in historical US
+Presidential Election results. This data comes from @pres_data, who scraped the
+results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
+presidential outcomes were avaiable for `r nrow(pres_2016)` counties in 2016 and
+`r nrow(pres_2020)` counties in 2020.
 
-### Independent Variables
+In addition, I use data on political opinions from the the American National
+Election Survey 2020 Time-Series Study [@anes_data]. This data is paired with
+restricted data provided by ICPSR, the Inter-university Consortium for Political
+and Social Research, that contains the geo-ids of the `r 5,441` survey respondents.
+The study interviewed respondents in a pre-election survey that was conducted
+between August 18, 2020 and the day of the US Presidential election day,
+November 3, 2020.
+
 ## Analysis
+For cross-sectional numeric data, I use the Pearson correlation formula (formula
+\@ref(eq:pearsoncorr)) to calculate the strength of the relationship between
+each Google Trend and the respective datasource.
+
+\begin{equation}
+ r =
+  \frac{ \sum_{i=1}^{n}(x_i-\bar{x})(y_i-\bar{y}) }{
+        \sqrt{\sum_{i=1}^{n}(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^{n}(y_i-\bar{y})^2}} (\#eq:pearsoncorr)
+\end{equation}
+
+To address longitudinal correlations, I employ Repeated Measures Correlation
+[@bland1995] using the `rmcorr` package in R [@bakdash2017]. Repeated Measures
+Correlation is useful for determining the within-individual association for
+paired measures across time and individuals.
+
+I test both the raw trends, as well a combination of trends created
+through factor analysis as a method of dimensionality reduction.
+
+As an additional test of correlation, I employ multiple linear
+regression to identify the strength of relationships across locales: I
+include city-data like county population size, internet usage rates, and
+Z to attempt to disentangle why some individual cases may be better predicted by
+Google Trends while others may not.
+
+visualizations made with [@wickham11; @wickham_etal]
+
 # Results
+
 ## Cultural
+
 ## Medical
+
+```{r}
+covid_corr <- rmcorr::rmcorr(fips, measure1 = covid_rate, measure2 = covid_19, dataset = covid)
+
+covid_reg <- lm(covid_rate ~ covid_19 + smell_loss + taste_loss, data = covid)
+
+```
+
+```{r}
+suicide_corr <- rmcorr::rmcorr(fips, measure1 = death_rate, measure2 = suicide, dataset = suicide)
+
+suicide_reg <- lm(death_rate ~ suicide + depression + suicide_hotline, data = suicide)
+summary(suicide_reg)
+
+library(nlme)
+
+suicide <- suicide %>% 
+  drop_na()
+suicide_lme <- lme(fixed = death_rate ~ suicide + depression + suicide_hotline,
+             random = ~ 1 | fips,
+             data = suicide)
+summary(suicide_lme)
+```
+
 ## Political
+
 # Discussion
-While I expect these tests to show high correlation between observed indicators
-and Google search trends, there will be three important questions that surface.
-First, just because something is correlated, does that mean it can replace the
-collection of other types of data? Second, how correlated does a trend need to
-be for social scientists to justifiably rely on it to indicate some outcome? And
-finally, how can we construct analyses like this to be robust to changes in the
-terms used across time and location?
 
-The purpose of this paper is more methodological than theoretical, and I see
-this paper having an impact on the social sciences and computational social
-science as researchers pursue more projects using this source of big data.
-Google Trends are relatively underutilized in the field compared to in the
-health sciences and business. Once I assess how this data can be used, I would
-like to be able to join @bailCulturalEnvironmentMeasuring2014 in encouraging social scientists to pursue
-more research with big data while taking into account the potential pitfalls
-with any source of big data [@mcfarlandBigDataDanger2015].
+While I expect these tests to show high correlation between observed
+indicators and Google search trends, there will be three important
+questions that surface. First, just because something is correlated,
+does that mean it can replace the collection of other types of data?
+Second, how correlated does a trend need to be for social scientists to
+justifiably rely on it to indicate some outcome? And finally, how can we
+construct analyses like this to be robust to changes in the terms used
+across time and location?
+
+The purpose of this paper is more methodological than theoretical, and I
+see this paper having an impact on the social sciences and computational
+social science as researchers pursue more projects using this source of
+big data. Google Trends are relatively underutilized in the field
+compared to in the health sciences and business. Once I assess how this
+data can be used, I would like to be able to join
+@bailCulturalEnvironmentMeasuring2014 in encouraging social scientists
+to pursue more research with big data while taking into account the
+potential pitfalls with any source of big data
+[@mcfarlandBigDataDanger2015].
 
@@
 
-# References {-}
+# References {.unnumbered}
 
-<div id="refs"></div>
+::: {#refs}
+:::
 

### 2022-02-22 paper1-cleaning.Rmd
add in county-level ACS data

@@
 pacman::p_load(tidyverse, glue, here, vroom, gtrendsR,
-               lubridate, zoo)
+               lubridate, zoo, readxl, tidycensus)
 
@@
 
+# county_data
+
+```{r census_api_to_delete}
+# load ACS demographic data
+tidycensus::census_api_key("a78281136605c66d53cf0abd929a5f2101e92a28", overwrite = TRUE, install = TRUE)
+readRenviron("~/.Renviron")
+
+# v19 <- load_variables(2019, "acs5", cache = TRUE)
+# v19_p <- load_variables(2019, "acs5/profile", cache = TRUE)
+# v19_s <- load_variables(2019, "acs5/subject", cache = TRUE)
+
+acs_2010_2016 <- c(Bachelor_higher_25pl = "DP02_0065P",
+              employment_rate = "DP03_0009P",
+              commute_time = 'DP03_0025',
+              median_family_income = 'DP03_0086',
+              perc_poverty = 'DP03_0119P',
+              total_population =	"B01003_001",
+              perc_65_over = "DP05_0021P",
+
+              `TotalLabor Force` ='B23025_003',
+              Employed ='B23025_004',
+              Unemployed ='B23025_005',
+
+              pop25_under = B19037_002,
+              pop18_over = B16003_008,
+              bachelor_n = B16010_041,
+              )
+
+acs_2017_2019 <- c(Bachelor_higher_25pl = "DP02_0065P",
+              employment_rate = "DP03_0009P",
+              commute_time = 'DP03_0025',
+              median_family_income = 'DP03_0086',
+              perc_poverty = 'DP03_0119P',
+              total_population =	"B01003_001",
+              perc_65_over = "DP05_0024P")
+
+##############
+get_acs_5yr <- function(year){
+  vars <- ifelse(year >= 2017, acs_2017_2019, acs_2010_2016)
+  result <- get_acs(geography = "county", 
+                    variables = vars,
+                    survey = "acs5",
+                    year = year)
+
+  result <- result %>% 
+    mutate(state = str_split_fixed(NAME, ", ", 2)[,2],
+           county = str_split_fixed(NAME, ", ", 2)[,1]) %>% 
+    select(-moe, -NAME, fips = GEOID) %>% 
+    pivot_wider(id_cols = c("fips", "state", "county"), 
+                names_from = "variable",
+                values_from = "estimate") %>% 
+    mutate(year = year)
+
+  return(result)
+}
+
+acs_data <- tibble(
+  "fips" = character(),
+  "state" = character(),
+  "county" = character(),
+  "Bachelor_higher_25pl" = numeric(),
+  "wifiathome" = numeric(),
+  "employment_rate" = numeric(),
+  "commute_time" = numeric(),
+  "median_family_income" = numeric(),
+  "perc_poverty" = numeric(),
+  "total_population" = numeric(),
+  "perc_65_over" = numeric(),
+  "year" = numeric()
+)
+
+acs_data <- get_acs_5yr(2010) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2011) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2012) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2013) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2014) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2015) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2016) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2017) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2018) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data <- get_acs_5yr(2019) %>% 
+        bind_rows(acs_data)
+Sys.sleep(10)
+
+acs_data %>% write_rds(here("data", "county-data","acs_from_api.rds"))
+```
+
+```{r social_explorer}
+acs <- read_csv(here("data", "county-data","acs_2010.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,  
+         over_65 = SE_A01001B_010  / SE_A01001B_001,        
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2010) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,         
+         unemployment_rate,         
+         over_65,           
+         poverty_rate, 
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001)
+
+acs <- read_csv(here("data", "county-data","acs_2011.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,  
+         over_65 = SE_A01001B_010  / SE_A01001B_001,        
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2011) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,        
+         unemployment_rate,       
+         over_65,     
+         poverty_rate, 
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2012.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001, 
+         over_65 = SE_A01001B_010  / SE_A01001B_001,    
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2012) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,         
+         unemployment_rate,          
+         over_65,           
+         poverty_rate, 
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2013.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,    
+         over_65 = SE_A01001B_010  / SE_A01001B_001,        
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2013) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,          
+         over_65,         
+         poverty_rate, 
+         unemployment_rate,
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2014.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,        
+         over_65 = SE_A01001B_010  / SE_A01001B_001,     
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2014) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,          
+         over_65,        
+         poverty_rate, 
+         unemployment_rate,
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2015.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,        
+         over_65 = SE_A01001B_010  / SE_A01001B_001,  
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2015) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,          
+         over_65,          
+         poverty_rate, 
+         unemployment_rate,
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2016.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,         
+         over_65 = SE_A01001B_010  / SE_A01001B_001,     
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2016) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,         
+         over_65,         
+         poverty_rate, 
+         unemployment_rate,
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2017.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,      
+         over_65 = SE_A01001B_010  / SE_A01001B_001,     
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2017) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,         
+         over_65,          
+         poverty_rate, 
+         unemployment_rate,
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2018.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,    
+         over_65 = SE_A01001B_010  / SE_A01001B_001,    
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2018) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002,          
+         over_65,          
+         poverty_rate, 
+         unemployment_rate,
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001) %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2019.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,
+         over_65 = SE_A01001B_010  / SE_A01001B_001,
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2019) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002, 
+         unemployment_rate,
+         over_65, 
+         poverty_rate, 
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001)  %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2019.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,
+         over_65 = SE_A01001B_010  / SE_A01001B_001,
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2020) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002, 
+         unemployment_rate,
+         over_65, 
+         poverty_rate, 
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001)  %>% 
+  bind_rows(acs)
+
+acs <- read_csv(here("data", "county-data","acs_2019.csv"))  %>% 
+  rowwise() %>% 
+  mutate(unemployment_rate = SE_A17005_003 / SE_A17005_001,
+         over_65 = SE_A01001B_010  / SE_A01001B_001,
+         poverty_rate = SE_A13002_002 / SE_A13002_001,
+         year = 2021) %>% 
+  select(fips = Geo_FIPS, Geo_QName, year,
+         total_pop = SE_A00001_001, 
+         pop_density = SE_A00002_002, 
+         unemployment_rate,
+         over_65, 
+         poverty_rate, 
+         median_income = SE_A14006_001,
+         commute = SE_A09003_001)  %>% 
+  bind_rows(acs)
+```
+
+```{r}
+internet <- read_excel(here("data", "county-data","broadband_long2000-2018rev.xlsx")) %>% 
+  mutate( fips =  str_pad(cfips, 5, pad = "0")) %>% 
+  filter(year >= 2010) %>% 
+  select(fips, year, broadband)
+
+internet <- internet %>% 
+  bind_rows(mutate(filter(internet, year == 2018), year = 2029)) %>% 
+  bind_rows(mutate(filter(internet, year == 2018), year = 2020)) %>% 
+  bind_rows(mutate(filter(internet, year == 2018), year = 2021))
+
+county <- acs %>% 
+  left_join(internet, by = c('fips', 'year'))
+```
+
 # attitudinal
@@
 
+vacc_hes <- vacc_hes %>% 
+  mutate(year = 2021) %>% 
+  left_join(county, by = c('fips', 'year')) %>% 
+  select(-year)
+
 write_rds(vacc_hes, here('data', 'cleaned_data', 'vacc_hes.rds'))
@@
   facet_wrap(~ name)
+
+mask <- mask %>% 
+  mutate(year = 2020) %>% 
+  left_join(county, by = c('fips', 'year')) %>% 
+  select(-year)
 
@@
 
+covid <- covid %>% 
+  mutate(year = year(date)) %>% 
+  left_join(county, by = c('fips', 'year')) %>% 
+  select(-year)
+
 write_rds(covid, here('data', 'cleaned_data', 'covid.rds'))
@@
 ```{r suicide}
-# suicide_measures_both <- read_delim(here('data','suicide',
-#                                     'Multiple Cause of Death, 1999-2020.txt')) %>% 
-#   janitor::clean_names() %>% 
-#   filter(is.na(notes)) %>% 
-#   select(fips = county_code, county, year = year_code, deaths_both = deaths, population)
-# 
-# suicide_measures_mcd <- read_delim(here('data','suicide',
-#                                     'Multiple Cause of Death, 1999-2020 only multiple cause.txt')) %>% 
-#   janitor::clean_names() %>% 
-#   filter(is.na(notes)) %>% 
-#   select(fips = county_code, county, year = year_code, deaths_mcd = deaths)
-# 
-# breaks <-  c(10,20,40,60,100,200,400,700,1300)
-# suicide_measures <- suicide_measures_both %>% 
-#   left_join(suicide_measures_mcd, by = c('fips', 'county', 'year')) %>% 
-#   mutate(deaths_mcd = na_if(deaths_mcd,'Missing'),
-#          deaths_both = na_if(deaths_both,'Missing'),
-#          deaths_mcd_supp = ifelse(deaths_mcd == 'Suppressed', '(0:9]', NA), 
-#          deaths_both_supp = ifelse(deaths_both == 'Suppressed', '(0:9]', NA), 
-#          deaths_mcd = na_if(deaths_mcd,'Suppressed'),
-#          deaths_both = na_if(deaths_both,'Suppressed'),
-#          deaths_mcd_cut = as.character(cut(as.numeric(deaths_mcd), breaks = breaks)),
-#          deaths_both_cut = as.character(cut(as.numeric(deaths_both), breaks = breaks)),
-#          deaths_mcd_cut = ifelse(!is.na(deaths_mcd_supp),
-#                                  deaths_mcd_supp,
-#                                  deaths_mcd_cut), 
-#          deaths_both_cut = ifelse(!is.na(deaths_both_supp),
-#                                   deaths_both_supp,
-#                                   deaths_both_cut)) %>% 
-#         select(fips, county, year, deaths_both_cut) %>% 
-#   mutate(deaths = factor(deaths_both_cut, ordered = T),
-#          deaths = fct_relevel(deaths, c("(0:9]",
-#                                         "(10,20]",
-#                                         "(20,40]", 
-#                                         "(40,60]",
-#                                         "(60,100]",    
-#                                         "(100,200]",
-#                                         "(200,400]",
-#                                         "(400,700]",   
-#                                         "(700,1.3e+03]")))
-# suicide_measures %>% 
-#   count(year, deaths) %>%
-#   ggplot(aes(x = deaths, y = n)) +
-#   geom_bar(stat = 'identity') +
-#   facet_wrap(~year)
 
@@
 
-write_rds(suicide, here('data', 'cleaned_data', 'suicide.rds'))
-
 suicide %>% 
@@
   theme_minimal()
+
+suicide <- suicide %>% 
+  left_join(county, by = c('fips', 'year'))
+
+write_rds(suicide, here('data', 'cleaned_data', 'suicide.rds'))
 
@@
 
+pres_2016 <- pres_2016 %>% 
+  mutate(year = 2016) %>% 
+  left_join(county, by = c('fips', 'year')) %>% 
+  select(-year)
+
 write_rds(pres_2016, here('data', 'cleaned_data', 'pres_2016.rds'))
+
+pres_2020 <- pres_2020 %>% 
+  mutate(year = 2020) %>% 
+  left_join(county, by = c('fips', 'year')) %>% 
+  select(-year)
+
 write_rds(pres_2020, here('data', 'cleaned_data', 'pres_2020.rds'))

### 2022-02-22 paper1.Rmd
add in county-level ACS data

@@
 pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
-               modelsummary, showtext, thematic, kableExtra, scales,
-               rmcorr)
+               modelsummary, showtext, thematic, kableExtra, scales)
 
@@
 theme_set(theme_diss())
+
+stars <- function(p.value){
+  unclass(symnum(p.value, 
+                 corr = FALSE, 
+                 na = FALSE, 
+                 cutpoints = c(0, 0.001, 0.01, 0.05, 1), 
+                 symbols = c("***", "**", "*", " ")))
+}
 
@@
 
+### Other
+
+ACS 1 year estimates
+a00001 total population
+a00002 population density
+a17005 unemployment rate 16+
+a14006 median income
+a09003 average commute time
+poverty percent
+01001B 65 plus
+
+broadband percent 
+[@internet_use]
+
 ## Analysis
@@
 To address longitudinal correlations, I employ Repeated Measures Correlation
-[@bland1995] using the `rmcorr` package in R [@bakdash2017]. Repeated Measures
-Correlation is useful for determining the within-individual association for
-paired measures across time and individuals.
+using the `rmcorr` package in R [@bland1995; @bakdash2017]. Repeated Measures
+Correlation is useful for determining the within-county association for paired
+measures across time and counties.
 
-I test both the raw trends, as well a combination of trends created
-through factor analysis as a method of dimensionality reduction.
-
-As an additional test of correlation, I employ multiple linear
+As an additional test of the relationships, I employ multiple linear
 regression to identify the strength of relationships across locales: I
-include city-data like county population size, internet usage rates, and
-Z to attempt to disentangle why some individual cases may be better predicted by
-Google Trends while others may not.
+include city-data like county population size, in-home internet rates, and
+median income to attempt to disentangle possible confounders of the relationship 
+between Google search Trends and verified indicators. Identifying these possible
+confounded relationships will help to explain why some articles find relationships
+between the trends and outcomes while others did not.
 
@@
 
+### vacc_hes 
+```{r vacc_hes_analysis}
+
+vacc_hes %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
+
+vacc_hes_reg <- lm(vacc_hesitant  ~ covid_conspiracy +covid_19_vaccine +coronavirus +covid_19, data = vacc_hes)
+```
+
+vacc_hes correlations
+rsquared
+
+### mask
+
 ## Medical
+### covid
 
 ```{r}
-covid_corr <- rmcorr::rmcorr(fips, measure1 = covid_rate, measure2 = covid_19, dataset = covid)
+
+covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
+covid_corrs[1,1] <- "Covid Rate, Pearson's R Correlation"
+write_rds(covid_corrs, here('data', 'from_hpc', 'covid_corrs.rds'))
+
+covid_corrs %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
 
@@
 ```
+### suicide
 
 ```{r}
-suicide_corr <- rmcorr::rmcorr(fips, measure1 = death_rate, measure2 = suicide, dataset = suicide)
+
+suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))
+suicide_corrs[1,1] <- "Death by Suicide Rate, Pearson's R Correlation"
+suicide_corrs[2,1] <- "Death by Suicide Rate, rmcorr"
+
+write_rds(suicide_corrs, here('data', 'from_hpc', 'suicide_corrs.rds'))
+
+suicide_corrs %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
 
@@
 
+```{r factor-analysis}
+library(psych)
+library(nFactors)
+library(corrplot)
+
+dat <- suicide %>% ungroup() %>% 
+  select(death_rate, suicide, depression, suicide_hotline) %>% 
+  drop_na()
+
+round(cor(dat, use="complete.obs"),2)
+corrplot(cor(dat, use="complete.obs"), order = "hclust", tl.col='black', tl.cex=.75)
+
+EFAresult1 = factanal(~ ., data=dat, factors = 1, rotation = "varimax", 
+                      na.action = na.exclude) #note the formula specification allows NA 
+EFAresult1
+# First, we can look at the sums of squared (SS) loadings; these are the
+# eigenvalues, or the variance in all variables which is accounted for by that
+# factor (i.e., the eigenvalue/# of variables = proportion variance). If a
+# factor has a “high” SS loading (i.e., eigenvalue), then it is helping to
+# explain the variances in the variables. In the factanal() output, the factors
+# are ordered by their eigenvalues, with higher eigenvalues first.
+#
+# A general rule-of-thumb called the Kaiser Rule, is that a factor is
+# important/useful if its eigenvalue is greater than 1 (i.e., the average),
+# Here, factors 1-6 appear to be important. There are other ways to choose the
+# number of factors, we will look at later.
+#
+# To illustrate how the eigenvalue is calculated.
+
+```
+
 ## Political
+### pres_2016
+
+### pres_2020
 

### 2022-02-22 rmcorrs.r

@@ -1,0 +1,31 @@
+#rmcorr script
+library(tidyverse)
+library(glue)
+library(rmcorr)
+
+covid <- read_rds('data/covid.rds')
+# suicide <- read_rds(here('data', 'cleaned_data', 'suicide.rds'))
+
+vars <- c('covid_19', 'smell_loss', 'taste_loss')
+
+for (i in vars){
+  corr_result <-  rmcorr::rmcorr(fips, measure1 = covid_rate, measure2 = covid_19, dataset = covid)
+  covid_mcor[i] <- corr_result
+  write_rds(corr_result, glue('data/covid_mcor_{i}.rds'))
+}
+
+
+covid_corrs <- tribble(
+  ~'measure', ~'covid_19', ~'smell_loss', ~'taste_loss', 
+  'covid_rate, raw corr',
+  cor(covid_dat$covid_rate, covid_dat$covid_19),
+  cor(covid_dat$covid_rate, covid_dat$smell_loss),
+  cor(covid_dat$covid_rate, covid_dat$taste_loss),
+  
+  'covid_rate, rmcorr',
+  glue("{round(covid_mcor$covid_19$r,3)}{stars(covid_mcor$covid_19$p)}"),
+  glue("{round(covid_mcor$smell_loss$r,3)}{stars(covid_mcor$smell_loss$p)}"),
+  glue("{round(covid_mcor$taste_loss$r,3)}{stars(covid_mcor$taste_loss$p)}")
+)
+
+write_rds(covid_corrs, here('data/covid_corrs.rds'))

### 2022-02-22 paper1.Rmd
analysis prepped

--- 2022-02-19 paper1.Rmd
@@
                       warning = FALSE,
-                      # cache = TRUE,
+                      cache = TRUE,
                       fig.width = 7,
@@
 pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
-               modelsummary, showtext, thematic, kableExtra, scales,
-               rmcorr)
+               modelsummary, showtext, thematic, kableExtra, scales, nlme)
 
-my_palette = c('#56b4e9','#999999','#E69F00','#009E73','#CC79A7','#0072B2','#D55E00','#E69F00')
 my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')
 
-## Automatically use showtext to render text
-font_add_google("Lora", "lora")
-showtext_auto()
-
-theme_diss <- function(base_size = 14) {
-  theme_minimal(base_size = base_size) %+replace%
-    theme(
-      # Figure assembly
-      plot.title = element_text(family="lora",
-                                size = rel(1), 
-                                margin = margin(0,0,5,0), 
-                                hjust = 0),
-      plot.title.position = "plot",
-      plot.subtitle = element_text(family="lora",
-                                   size = rel(0.85)),
-      plot.caption = element_text(family="lora",
-                                  size = rel(0.70),
-                                  hjust = 1),
-      # Graphical Zones
-      panel.grid.minor = element_blank(),
-      panel.border = element_blank(),
-      # Axes
-      axis.title = element_text(family="lora", 
-                                size = rel(0.85)),
-      axis.text = element_text(family="lora", 
-                               size = rel(0.70)),
-      axis.line = element_line(color = "black", 
-                               arrow = arrow(length = unit(0.3, "lines"), 
-                                             type = "closed")),
-      # Legend
-      legend.title = element_text(family="lora",
-                                  size = rel(0.85)),
-      legend.text = element_text(family="lora", 
-                                 size = rel(0.70)),
-      legend.key = element_rect(fill = "transparent", 
-                                colour = NA),
-      legend.key.size = unit(1.5, "lines"),
-      legend.background = element_rect(fill = "transparent", 
-                                       colour = NA),
-      # Facetting 
-      strip.background = element_rect(fill = "#17252D",
-                                      color = "#17252D"),
-      strip.text = element_text(family="lora",
-                                size = rel(0.85), 
-                                color = "white", 
-                                margin = margin(5,0,5,0))
-    )
+stars <- function(p.value){
+  unclass(symnum(p.value, 
+                 corr = FALSE, 
+                 na = FALSE, 
+                 cutpoints = c(0, 0.001, 0.01, 0.05, 1), 
+                 symbols = c("***", "**", "*", " ")))
 }
-
-theme_set(theme_diss())
 
@@
 vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
-mask <- read_rds(here('data', 'cleaned_data', 'mask.rds'))
+mask <- read_rds(here('data', 'cleaned_data', 'mask.rds')) %>%  ungroup()
 covid <- read_rds(here('data', 'cleaned_data', 'covid.rds'))
@@
 pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))
+
 ```
@@
 
+<!-- TODO: VARIABLE SCALE -->
+
 Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
@@
 consists of `r nrow(mask)` observations, one for each U.S. County.
+
+<!-- TODO: VARIABLE SCALE -->
 
@@
 Case Rate is measured as number of cases per 100,000 population. Observations
-vary from a minimum of 0 to a maximum of `r max(covid$covid_rate))` for each 
+vary from a minimum of 0 to a maximum of `r max(covid$covid_rate)` for each 
 Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
@@
 using `zoo::na.approx()` [@zoo].
+
+<!-- TODO: VARIABLE SCALE -->
 
@@
 
+<!-- TODO: VARIABLE SCALE -->
+
 In addition, I use data on political opinions from the the American National
@@
 restricted data provided by ICPSR, the Inter-university Consortium for Political
-and Social Research, that contains the geo-ids of the `r 5,441` survey respondents.
-The study interviewed respondents in a pre-election survey that was conducted
-between August 18, 2020 and the day of the US Presidential election day,
-November 3, 2020.
+and Social Research, that contains the geo-ids of the `r scales::label_comma()(5441)`
+survey respondents. The study interviewed respondents in a pre-election survey
+that was conducted between August 18, 2020 and the day of the US Presidential
+election day, November 3, 2020.
+
+<!-- TODO: VARIABLE SCALE -->
+
+### Other
+
+In addition to specific outcomes of interest, I also gathered various county
+controls to investigate possible variable confounding. The first Seven of these
+variables come from the 2010-2019 5-year American Community Surveys [@acs2019;
+@acs2018; @acs2017; @acs2016; @acs2015; ; @acs2014; @acs2013; @acs2012;
+@acs2011; @acs2010]. These data include total population, population density,
+unemployment rate for those 16 and over, median county income, average commute
+time, percent of households living under the poverty line, and percent above 65
+years old. In addition, some models employ the U.S. Current Population Survey &
+American Community Survey Geographic Estimates of Internet Use, 1997-2018
+[@internet_use] to estimate households with broadband internet subscriptions.
+This final variable is an attempt to capture the latent propensity to use the
+internet for information search.
+
+<!-- ACS 5 year estimates -->
+<!-- a00001 total population -->
+<!-- a00002 population density -->
+<!-- a17005 unemployment rate 16+ -->
+<!-- a14006 median income -->
+<!-- a09003 average commute time -->
+<!-- poverty percent -->
+<!-- 01001B 65 plus -->
 
@@
 To address longitudinal correlations, I employ Repeated Measures Correlation
-[@bland1995] using the `rmcorr` package in R [@bakdash2017]. Repeated Measures
-Correlation is useful for determining the within-individual association for
-paired measures across time and individuals.
+using the `rmcorr` package in R [@bland1995; @bakdash2017]. Repeated Measures
+Correlation is useful for determining the within-county association for paired
+measures across time and counties.
 
-I test both the raw trends, as well a combination of trends created
-through factor analysis as a method of dimensionality reduction.
-
-As an additional test of correlation, I employ multiple linear
-regression to identify the strength of relationships across locales: I
-include city-data like county population size, internet usage rates, and
-Z to attempt to disentangle why some individual cases may be better predicted by
-Google Trends while others may not.
-
-visualizations made with [@wickham11; @wickham_etal]
+As an additional test of the relationships, I employ multiple linear regression
+to identify the strength of relationships across locales: I include city-data
+like county population size, broadband rates, and median income to attempt to
+disentangle possible confounders of the relationship between Google search
+Trends and verified indicators. Identifying these possible confounded
+relationships will help to explain why some articles find relationships between
+the trends and outcomes while others did not. For linear regression models, I
+normalize independent variables, i.e.variables have been centered and scaled to
+have a mean of 0 and standard deviation 1.
 
@@
 
-## Medical
+```{r vacc_hes_analysis1}
+tribble(
+  ~'measure',~'covid_conspiracy', ~'covid_19_vaccine', ~'coronavirus', ~'covid_19', 
+  "vacc_hes, Pearson's R Correlation",
+  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),
+  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),
+  cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),
+  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs")
+)  %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
+```
 
-```{r}
-covid_corr <- rmcorr::rmcorr(fips, measure1 = covid_rate, measure2 = covid_19, dataset = covid)
+```{r vacc_hes_analysis2}
+vacc_hes <- vacc_hes %>% 
+  select(-c(DMA_google, Geo_QName)) %>% 
+  mutate(across(covid_conspiracy:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
 
-covid_reg <- lm(covid_rate ~ covid_19 + smell_loss + taste_loss, data = covid)
+vacc_hes_1  <- lm(vacc_hesitant  ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + broadband,
+                  data = vacc_hes)
+vacc_hes_2 <- lm(vacc_hesitant  ~  covid_19_vaccine +     
+                   coronavirus +covid_19,
+                 data = vacc_hes)
+vacc_hes_2b <- lm(vacc_hesitant  ~ covid_conspiracy + covid_19_vaccine +
+                    coronavirus +covid_19,
+                  data = vacc_hes)
+vacc_hes_3  <- lm(vacc_hesitant  ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + broadband + 
+                    covid_19_vaccine +
+                    coronavirus +covid_19,
+                   data = vacc_hes)
+
+modelsummary(list(vacc_hes_1, vacc_hes_2, vacc_hes_2b,vacc_hes_3), 
+             # title = "Linear Regression Results for Vaccine Hesitancy",
+             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
+             estimate = "{estimate}{stars}",
+             gof_omit = 'AIC|BIC|ICC|RMSE'
+             ) %>%
+  kable_styling(latex_options = c("hold_position", 'condensed'),
+                font_size = 8)
 
@@
 
-```{r}
-suicide_corr <- rmcorr::rmcorr(fips, measure1 = death_rate, measure2 = suicide, dataset = suicide)
+pearson correlations
+rsquared
+coefficients
+conclusion
 
-suicide_reg <- lm(death_rate ~ suicide + depression + suicide_hotline, data = suicide)
-summary(suicide_reg)
-
-library(nlme)
-
-suicide <- suicide %>% 
-  drop_na()
-suicide_lme <- lme(fixed = death_rate ~ suicide + depression + suicide_hotline,
-             random = ~ 1 | fips,
-             data = suicide)
-summary(suicide_lme)
+```{r mask_analysis1}
+tribble(
+  ~'measure',~'face_mask', ~'mask', ~'cloth_face_mask',  
+  "Mask Rare, Pearson's R Correlation",
+  cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),
+  cor(mask$mask_rare, mask$mask, use = "complete.obs"),
+  cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs")
+)  %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
 ```
 
+```{r mask_analysis2}
+mask <- mask %>% 
+  select(-c(DMA_google, Geo_QName)) %>% 
+  mutate(across(face_mask:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+
+mask_1  <- lm(mask_rare  ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + broadband,
+                  data = mask)
+mask_2 <- lm(mask_rare  ~  face_mask + mask + cloth_face_mask,
+                 data = mask)
+mask_3  <- lm(mask_rare  ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + broadband + 
+                    face_mask + mask + cloth_face_mask,
+                   data = mask)
+
+modelsummary(list(mask_1, mask_2, mask_3), 
+             # title = "Linear Regression Results for Rare Mask Usage",
+             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
+             estimate = "{estimate}{stars}",
+             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
+  kable_styling(latex_options = c("hold_position", 'condensed'),
+                font_size = 8)
+
+```
+pearson correlations
+rsquared
+coefficients
+conclusion
+
+## Medical
+
+```{r covid_analysis1}
+covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
+# covid_corrs[1,1] <- "Covid Rate, Pearson's R Correlation"
+# write_rds(covid_corrs, here('data', 'from_hpc', 'covid_corrs.rds'))
+
+covid_corrs %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
+```
+
+```{r covid_analysis2}
+covid <- covid %>% 
+  select(-c(dma_google, Geo_QName, county, state)) %>% 
+  mutate(across(covid_19:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
+  left_join(covid %>%
+              group_by(fips) %>%
+              summarize(covid_rate_fips_mean = mean(covid_rate, na.rm = TRUE)),
+            by = "fips") %>% 
+  drop_na(covid_rate)
+
+covid_1  <- lme(covid_rate  ~ 
+                  total_pop + pop_density + unemployment_rate + 
+                  over_65 + poverty_rate + median_income + broadband +
+                  covid_rate_fips_mean + date,
+                random = ~ 1 | fips, na.action=na.omit,data = covid)
+covid_2 <- lme(covid_rate  ~  
+                 covid_19 + smell_loss + taste_loss + covid_rate_fips_mean  + 
+                 date,
+               random = ~ 1 | fips, na.action=na.omit, data = covid)
+covid_3  <- lme(covid_rate  ~ 
+                  total_pop + pop_density + unemployment_rate + 
+                  over_65 + poverty_rate + median_income + broadband + 
+                  covid_19 + smell_loss + taste_loss + covid_rate_fips_mean  +
+                  date,
+                random = ~ 1 | fips, na.action=na.omit, data = covid)
+
+modelsummary(list(covid_1, covid_2, covid_3), 
+             # title = "Hierarchical Model for Covid Case Rates",
+             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Random intercept per county'),
+             estimate = "{estimate}{stars}",
+             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
+  kable_styling(latex_options = c("hold_position", 'condensed'),
+                font_size = 8)
+
+# TODO Drop SD intercept and observations,
+
+```
+pearson correlations
+rmcorr
+rsquared
+coefficients
+conclusion
+
+```{r suicide_analysis1}
+suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))
+
+# suicide_corrs[1,1] <- "Death by Suicide Rate, Pearson's R Correlation"
+# suicide_corrs[2,1] <- "Death by Suicide Rate, rmcorr"
+# 
+# write_rds(suicide_corrs, here('data', 'from_hpc', 'suicide_corrs.rds'))
+
+suicide_corrs %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
+```
+
+```{r suicide_analysis2}
+suicide <- suicide %>% 
+  select(-c(dma_google, Geo_QName, county, population, deaths)) %>% 
+  mutate(across(suicide:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
+  left_join(suicide %>%
+              group_by(fips) %>%
+              summarize(death_rate_fips_mean = mean(death_rate , na.rm = TRUE)),
+            by = "fips") %>% 
+  drop_na(death_rate )
+
+suicide_1  <- lme(death_rate   ~ 
+                  total_pop + pop_density + unemployment_rate + 
+                  over_65 + poverty_rate + median_income + broadband +
+                  death_rate_fips_mean + year,
+                random = ~ 1 | fips, na.action=na.omit,data = suicide)
+suicide_2 <- lme(death_rate   ~  
+                 suicide + depression + suicide_hotline + death_rate_fips_mean  + 
+                 year,
+               random = ~ 1 | fips, na.action=na.omit, data = suicide)
+suicide_3  <- lme(death_rate   ~ 
+                  total_pop + pop_density + unemployment_rate + 
+                  over_65 + poverty_rate + median_income + broadband + 
+                  suicide + depression + suicide_hotline + death_rate_fips_mean  +
+                  year,
+                random = ~ 1 | fips, na.action=na.omit, data = suicide)
+
+modelsummary(list(suicide_1, suicide_2, suicide_3), 
+             # title = "Hierarchical Model for Suicide Rates",
+             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Random intercept per county'),
+             estimate = "{estimate}{stars}",
+             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
+  kable_styling(latex_options = c("hold_position", 'condensed'),
+                font_size = 8)
+
+# TODO Drop SD intercept and observations,
+# TODO why is the r2 so high? death_rate_fips_mean?
+```
+pearson correlations
+rmcorr
+rsquared
+coefficients
+conclusion
+
 ## Political
+
+```{r pres_2016_analysis1}
+tribble(
+  ~'measure',~'Searches for Hilary Clinton', ~ 'Searches for Donald Trump',
+  "Votes for Clinton, Pearson's R Correlation",
+  cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
+  cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),
+
+  "Votes for Trump, Pearson's R Correlation",
+  cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
+  cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),
+)  %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
+```
+
+```{r pres_2016_analysis2}
+pres_2016 <- pres_2016 %>% 
+  select(-c(Geo_QName, dma)) %>% 
+  mutate(across(c(`Hilary Clinton`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+
+vacc_hes_1a  <- lm(clinton_p   ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income,
+                  data = pres_2016)
+vacc_hes_2a <- lm(clinton_p   ~  `Donald Trump` + `Hilary Clinton`,
+                 data = pres_2016)
+
+vacc_hes_3a  <- lm(clinton_p   ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + 
+                     `Donald Trump` + `Hilary Clinton`,
+                   data = pres_2016)
+
+vacc_hes_1b  <- lm(trump_p    ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income,
+                  data = pres_2016)
+vacc_hes_2b <- lm(trump_p    ~  `Donald Trump` + `Hilary Clinton`,
+                 data = pres_2016)
+
+vacc_hes_3b  <- lm(trump_p    ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + 
+                     `Donald Trump` + `Hilary Clinton`,
+                   data = pres_2016)
+
+modelsummary(list(vacc_hes_1a, vacc_hes_2a,vacc_hes_3a 
+                  # ,vacc_hes_1b, vacc_hes_2b,vacc_hes_3b
+                  ), 
+             # title = "Linear Regression Results for 2016 Presidential Election Results (Hilary Clinton Shown)",
+             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Results predicting Donald J. Trump percentage largely equivalent and available upon request.'),
+             estimate = "{estimate}{stars}",
+             gof_omit = 'AIC|BIC|ICC|RMSE'
+             ) %>%
+  kable_styling(latex_options = c("hold_position", 'condensed'),
+                font_size = 8)
+
+```
+pearson correlations
+rsquared
+coefficients
+conclusion
+
+```{r pres_2020_analysis1}
+tribble(
+  ~'measure',~'Searches for Joe Biden', ~ 'Searches for Donald Trump',
+  "Votes for Biden, Pearson's R Correlation",
+  cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),
+  cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),
+
+  "Votes for Trump, Pearson's R Correlation",
+  cor(pres_2020$trump_p, pres_2020$`Joe Biden`, use = "complete.obs"),
+  cor(pres_2020$trump_p, pres_2020$`Donald Trump`, use = "complete.obs"),
+)  %>% 
+  kbl(digits=4) %>%
+  #overall styling
+  kable_styling(latex_options = c( "hold_position"), full_width = T)
+```
+
+```{r pres_2020_analysis2}
+pres_2020 <- pres_2020 %>% 
+  select(-c(Geo_QName, dma)) %>% 
+  mutate(across(c(`Joe Biden`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+
+vacc_hes_1a  <- lm(biden_p   ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income,
+                  data = pres_2020)
+vacc_hes_2a <- lm(biden_p   ~  `Donald Trump` + `Joe Biden`,
+                 data = pres_2020)
+
+vacc_hes_3a  <- lm(biden_p   ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + 
+                     `Donald Trump` + `Joe Biden`,
+                   data = pres_2020)
+
+vacc_hes_1b  <- lm(trump_p    ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income,
+                  data = pres_2020)
+vacc_hes_2b <- lm(trump_p    ~  `Donald Trump` + `Joe Biden`,
+                 data = pres_2020)
+
+vacc_hes_3b  <- lm(trump_p    ~ 
+                    total_pop + pop_density + unemployment_rate + 
+                    over_65 + poverty_rate + median_income + 
+                     `Donald Trump` + `Joe Biden`,
+                   data = pres_2020)
+
+modelsummary(list(vacc_hes_1a, vacc_hes_2a,vacc_hes_3a 
+                  # ,vacc_hes_1b, vacc_hes_2b,vacc_hes_3b
+                  ), 
+             # title = "Linear Regression Results for 2020 Presidential Election Results (Joe Biden Shown)",
+             notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
+                      'Results predicting Donald J. Trump percentage largely equivalent and available upon request.'),
+             estimate = "{estimate}{stars}",
+             gof_omit = 'AIC|BIC|ICC|RMSE'
+             ) %>%
+  kable_styling(latex_options = c("hold_position", 'condensed'),
+                font_size = 8)
+
+```
+pearson correlations
+rsquared
+coefficients
+conclusion
 

### 2022-02-23 paper1.Rmd
Some findings written

@@
     number_sections: true
-  bookdown::word_document2: 
-    toc: true
-    reference_docx: StylesTemplate.docx
+  # bookdown::word_document2: 
+  #   toc: true
+  #   reference_docx: StylesTemplate.docx
 header-includes:
@@
    - \usepackage{dcolumn}
+   - \usepackage{longtable}
    - \usepackage{caption}
-   - \usepackage{longtable}
    - \usepackage{booktabs}
+   - \usepackage{placeins}
    - \doublespacing
-   - \usepackage{placeins}
 csl: american-sociological-association.csl
@@
 indent: true
-always_allow_html: true
 ---
@@
                       fig.align="center"
-                      # dev.args = list(png = list(type = "cairo"))
                       )
@@
 pacman::p_load(tidyverse, glue, extrafont, here, jtools, psych,
-               modelsummary, showtext, thematic, kableExtra, scales, nlme)
+               modelsummary, showtext, thematic, kableExtra, scales, nlme,
+               flextable)
 
 my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')
-
-stars <- function(p.value){
-  unclass(symnum(p.value, 
-                 corr = FALSE, 
-                 na = FALSE, 
-                 cutpoints = c(0, 0.001, 0.01, 0.05, 1), 
-                 symbols = c("***", "**", "*", " ")))
-}
 
@@
 pres_2020 <- read_rds(here('data', 'cleaned_data', 'pres_2020.rds'))
+covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
+suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))
 
@@
 
-<https://journals.sagepub.com/doi/10.1177/0894439316631043> § What
+<https://journals.sagepub.com/doi/10.1177/0894439316631043> What
 constructs might google trends capture and not capture well? Capture
@@
 ```{r data-sources-table}
-#| results='asis',
-#| tab.cap = 'airquality dataset caption here'
+#| results='asis'
 
 data_sources <- tibble::tribble(
-~Validated.Data.Source, ~Type, ~Dates, ~Google.Trends.Used,
-"General Social Survey", "Cross-Sectional", "2010 - 2020", NA,
+~type, ~Validated.Data.Source, ~Type, ~Dates, ~Google.Trends.Used,
+"Behaviors and Attitudes","General Social Survey", "Cross-Sectional", "2010 - 2020", NA,
 
-"Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "covid conspiracy', 'COVID-19 vaccine', 'Coronavirus', 'Covid-19'",
+"Behaviors and Attitudes","Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "covid conspiracy', 'COVID-19 vaccine', 'Coronavirus', 'Covid-19'",
 
-"Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "'Face Mask', 'Mask', 'Cloth Face Mask'",
+"Behaviors and Attitudes","Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "'Face Mask', 'Mask', 'Cloth Face Mask'",
 
- "Covid Rates", "Longitudinal", "Every Monday, 2020 - 2021", "'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss'",
+"Health","Covid Rates", "Longitudinal", "Every Monday, 2020 - 2021", "'Covid-19', 'Coronavirus', 'Taste Loss', 'Smell Loss'",
 
-"County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "'Suicide', 'Depression',' Suicide Hotline'",
+"Health","County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "'Suicide', 'Depression',' Suicide Hotline'",
 
-"American National Election Survey", "Cross-Sectional", "2020", NA,
+'Political',"American National Election Survey", "Cross-Sectional", "2020", NA,
 
-"Presidential Election Results", "Cross Sectional", "2016 & 2020", "'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
- )
+'Political',"Presidential Election Results", "Cross Sectional", "2016 & 2020", "'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
+ ) %>% as_grouped_data(groups = c("type"), columns = NULL)
 
 data_sources %>% 
-  kbl() %>%
-  # group rows
-  pack_rows("Behaviors and Attitudes", 1,3, background = '#bad7db', bold = T) %>% 
-  pack_rows("Health", 4,5, background = '#bad7db', bold = T) %>% 
-  pack_rows('Political', 6,7, background = '#bad7db', bold = T) %>% 
-  # header style
-  row_spec(0, background = my_palette[8], color = 'white', bold = T) %>% 
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
+  as_flextable(hide_grouplabel = TRUE) %>% 
+  set_caption(caption = "New York Air Quality Measurements")  %>% 
+  # theming
+  theme_box() %>% 
+  bg(bg = my_palette[8], part = "header") %>% 
+  color(color = "white", part = "header") %>%
+  set_table_properties(layout = "autofit", width = 1) %>% 
+  # grouped row style
+  fontsize(size = 8) %>% 
+  bold(i = ~ !is.na(type), bold = TRUE) %>% 
+  italic(i = ~ !is.na(type), italic = TRUE) %>% 
+  bg(i = ~ !is.na(type), bg = "#bad7db", part = "body")
 
@@
 vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
-of `r nrow(vacc_hes)` observations, one for each U.S. County.
-
-<!-- TODO: VARIABLE SCALE -->
+of `r nrow(vacc_hes)` observations, one for each U.S. County. The variable
+measures the precent of adults in the county who describe themselves as
+“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
+once one is available to them. The variable ranges from 
+`r percent_format(0.01)(min(vacc_hes$vacc_hesitant))` to 
+`r percent_format(0.01)(max(vacc_hes$vacc_hesitant))`.
 
@@
 to create a county level measure of what percent of the county never, rarely,
-sometimes, frequetly, and always wore a mask when in public. This dataset
-consists of `r nrow(mask)` observations, one for each U.S. County.
-
-<!-- TODO: VARIABLE SCALE -->
+sometimes, frequently, and always wore a mask when in public. This dataset
+consists of `r nrow(mask)` observations, one for each U.S. County. This measure
+represents the percent of adults in the county who never or rarely wear a mask
+(range = `r percent_format(0.01)(min(mask$mask_rare))` to 
+`r percent_format(0.01)(max(mask$mask_rare))`)
 
@@
 
-I first use U.S. Covid-19 rates to validate health and disease related topics. I
+I also use U.S. Covid-19 rates to validate health and disease related topics. I
 retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
@@
 
-<!-- TODO: VARIABLE SCALE -->
-
 I also use county-level suicide rates from the US Centers for Disease Control
 and Prevention [-@suic_data]. Data is grouped by year from 2010-2020. Raw death
-rates are scaled by population size for each year. There are `r nrow(suicide)` 
-total cases, resulting from `r nrow(count(suicide, year))` observations of 
-`r nrow(count(suicide, fips))` counties. Missing data were interpolated 
-using `zoo::na.approx()` [@zoo].
-
-<!-- TODO: VARIABLE SCALE -->
+rates are scaled by population size for each year and can be interpreted as the
+death rate by suicide for every 1000 people. There are `r nrow(suicide)` total
+cases, resulting from `r nrow(count(suicide, year))` observations of `r
+nrow(count(suicide, fips))` counties. Missing data were interpolated using
+`zoo::na.approx()` [@zoo]. Measures range from 
+`r round(min(suicide$death_rate, na.rm=T),3)` to 
+`r round(max(suicide$death_rate, na.rm=T),3)`.
 
@@
 presidential outcomes were avaiable for `r nrow(pres_2016)` counties in 2016 and
-`r nrow(pres_2020)` counties in 2020.
-
-<!-- TODO: VARIABLE SCALE -->
+`r nrow(pres_2020)` counties in 2020. Each variable measures the percent of votes
+for the candidate, with the lowest percent at 
+`r percent_format(0.01)(min(pres_2020$biden_p, na.rm=T))`
+and the highest at `r percent_format(0.01)(max(pres_2020$biden_p, na.rm=T))`.
 
@@
 
+<!-- TODO: WHICH VARIABLES -->
 <!-- TODO: VARIABLE SCALE -->
@@
 variables come from the 2010-2019 5-year American Community Surveys [@acs2019;
-@acs2018; @acs2017; @acs2016; @acs2015; ; @acs2014; @acs2013; @acs2012;
+@acs2018; @acs2017; @acs2016; @acs2015; @acs2014; @acs2013; @acs2012;
 @acs2011; @acs2010]. These data include total population, population density,
@@
 ## Analysis
-For cross-sectional numeric data, I use the Pearson correlation formula (formula
-\@ref(eq:pearsoncorr)) to calculate the strength of the relationship between
-each Google Trend and the respective datasource.
+Google Search Trends data and additional demographic data are merged with each
+individual indicator based on County FIPS Codes and date. After creating these
+different datasets, I use the Pearson correlation formula (formula
+\@ref(eq:pearsoncorr)) for cross-sectional numeric data to calculate the
+strength of the relationship between each Google Trend and the respective
+data source.
 
@@
 Correlation is useful for determining the within-county association for paired
-measures across time and counties.
+measures across time and counties. Results of these correlations can be seen in 
+table \@ref(tab:corr-results).
 
 As an additional test of the relationships, I employ multiple linear regression
-to identify the strength of relationships across locales: I include city-data
-like county population size, broadband rates, and median income to attempt to
-disentangle possible confounders of the relationship between Google search
-Trends and verified indicators. Identifying these possible confounded
-relationships will help to explain why some articles find relationships between
-the trends and outcomes while others did not. For linear regression models, I
-normalize independent variables, i.e.variables have been centered and scaled to
-have a mean of 0 and standard deviation 1.
+(for cross-sectional datasets) and random intercept hierarchical linear models
+[@pinheiro_etal21] (for longitudinal datasets) to identify the strength of
+relationships across locales: I include city-data like county population size,
+broadband rates, and median income to attempt to disentangle possible
+confounders of the relationship between Google search Trends and verified
+indicators. Identifying these possible confounded relationships will help to
+explain why some articles find relationships between the trends and outcomes
+while others did not. For linear regression models, I normalize independent
+variables, i.e.variables have been centered and scaled to have a mean of 0 and
+standard deviation 1.
 
@@
 ## Cultural
+```{r corr-results}
+#|  results='asis'
 
-```{r vacc_hes_analysis1}
-tribble(
-  ~'measure',~'covid_conspiracy', ~'covid_19_vaccine', ~'coronavirus', ~'covid_19', 
-  "vacc_hes, Pearson's R Correlation",
-  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),
-  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),
-  cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),
-  cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs")
+options(knitr.kable.NA = '')
+
+table2 <- tribble(
+  ~'grp', ~'variable', ~'measure',~'trend1', ~'trend2', ~'trend3', ~'trend4', 
+  "Vaccine Hesitancy", NA,  NA, 'covid_conspiracy', 'covid_19_vaccine', 'coronavirus', 'covid_19', 
+  "Vaccine Hesitancy", "Vaccine Hesitancy", "Pearson's R Correlation",
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),4)),
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),4)),
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),4)),
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs"),4)),
+
+  "Mask Attitudes",NA,  NA, 'face_mask', 'mask', 'cloth_face_mask',  NA,
+  "Mask Attitudes","Mask Rare", "Pearson's R Correlation",
+  as.character(round(cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),4)),
+  as.character(round(cor(mask$mask_rare, mask$mask, use = "complete.obs"),4)),
+  as.character(round(cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs"), 4)), NA,
+
+  "Covid Rates",NA,  NA, 'covid_19',  'smell_loss', 'taste_loss', NA, 
+  "Covid Rates","Covid Rate", "Pearson's R Correlation", 
+  as.character(round(cor(covid$covid_rate, covid$covid_19, use = "complete.obs"),4)),
+  as.character(round(cor(covid$covid_rate, covid$smell_loss, use = "complete.obs"),4)),
+  as.character(round(cor(covid$covid_rate, covid$taste_loss, use = "complete.obs"),4)),
+  NA,
+  "Covid Rates","Covid Rate", "rmcorr", 
+  as.character(covid_corrs[[2,2]]), 
+  as.character(covid_corrs[[2,3]]), 
+  as.character(covid_corrs[[2,4]]), NA,
+
+  "Suicide Rates",NA,  NA, 'suicide', 'depression', 'suicide_hotline', NA, 
+  "Suicide Rates","Suicide Rate", "Pearson's R Correlation",
+  as.character(round(cor(suicide$death_rate, suicide$suicide, use = "complete.obs"),4)),
+  as.character(round(cor(suicide$death_rate, suicide$depression, use = "complete.obs"),4)),
+  as.character(round(cor(suicide$death_rate, suicide$suicide_hotline, use = "complete.obs"),4)),
+  NA,
+  "Suicide Rates","Suicide Rate", "rmcorr", 
+  as.character(suicide_corrs[[2,2]]), 
+  as.character(suicide_corrs[[2,3]]), 
+  as.character(suicide_corrs[[2,4]]), NA,
+
+  "2016 Presidential Votes",NA,  NA, 'Hilary Clinton',  'Donald Trump', NA, NA,
+  "2016 Presidential Votes","2016 Votes for Clinton", "Pearson's R Correlation",
+  as.character(round(cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
+  "2016 Presidential Votes","2016 Votes for Trump", "Pearson's R Correlation",
+  as.character(round(cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
+
+  "2016 Presidential Votes",NA,  NA, 'Joe Biden',  'Donald Trump', NA, NA,
+  "2016 Presidential Votes","2020 Votes for Biden", "Pearson's R Correlation",
+  as.character(round(cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
+  "2016 Presidential Votes","2020 Votes for Trump", "Pearson's R Correlation",
+  as.character(round(cor(pres_2020$trump_p, pres_2020$`Joe Biden`, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2020$trump_p, pres_2020$`Donald Trump`, use = "complete.obs"),4)), NA, NA
 )  %>%   
-  kbl(digits=4) %>%
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
+  select(grp, measure, variable, trend1, trend2, trend3, trend4) %>% 
+  as_grouped_data(groups = c("grp"), columns = NULL)
+
+as_flextable(table2, hide_grouplabel = TRUE) %>% 
+  set_caption(caption = "Correlation Results")  %>% 
+  # theming
+  theme_box() %>% 
+  bg(bg = my_palette[8], part = "header") %>% 
+  color(color = "white", part = "header") %>%
+  set_table_properties(layout = "autofit", width = 1) %>% 
+  # grouped row style
+  fontsize(size = 8) %>% 
+  bold(i = ~ !is.na(grp), bold = TRUE) %>% 
+  italic(i = ~ !is.na(grp), italic = TRUE) %>% 
+  bg(i = ~ !is.na(grp), bg = "#bad7db", part = "body")
 ```
 
-```{r vacc_hes_analysis2}
+The first attitudinal indicators is Vaccine Hesitancy for COVID-19 vaccines
+[@vaches_data]. When comparing the measure of vaccine hesitancy to four
+different Google Search Trends, the correlation does not exceed -0.4021
+('Coronavirus' and vaccine hesitancy). Correlation's under |0.40| are considered
+to be weak according to the common rules of thumb. When running these
+correlations in multiple linear regression (see the results in table 
+\@ref(tab:vacc_hes_analysis)), I see an $r^2$ of 0.221 (Model 1)
+and 0.346 (Model 2), indicating that the Google Trends are able to explain about
+22% of the variation in Vaccine Hesitancy alone. Demographic characteristics
+like the percentage of households with broadband internet and the population
+density are able to explain about 35% of the variation (model 3), outperforming
+the first two models. The Trend coefficients themselves, however, are
+significant and remain significant when controlling for demographics. This
+reinforces the finding from the Pearson Correlation that there is a significant
+but weak relationship between the Google Trends and Vaccine Hesitancy.
+
+```{r vacc_hes_analysis}
+#| tab.cap = "Linear Regression Results for Vaccine Hesitancy",
+#|  results='asis'
+
 vacc_hes <- vacc_hes %>% 
@@
 
-modelsummary(list(vacc_hes_1, vacc_hes_2, vacc_hes_2b,vacc_hes_3), 
+modelsummary(list(vacc_hes_2, vacc_hes_2b, vacc_hes_1, vacc_hes_3), 
              # title = "Linear Regression Results for Vaccine Hesitancy",
@@
 
-pearson correlations
-rsquared
-coefficients
-conclusion
+The second attitudinal measure I test is how Google Trends relates to rare mask
+usage. As with vaccine hesitancy, the Pearson correlations are weak, if not 
+negligible. I introduce these trends in multiple linear regression in table 
+\@ref(tab:mask_analysis). Model 1 demonstrates that these three Google Search
+Trends can explain about 9% of the variance in mask usage across U.S. counties,
+reinforcing the conclusion that the relationship is quite weak. The coefficients
+themselves are somewhat significant in Model 1. However, after including the
+demographic varaibles in Models 2 and 3, we see that the relationship between
+the Google Search Trends and mask usage is strengthed in magnitude and in
+significance, likely indicating a repression effect due to background
+relationships between the trends and demograhic variables. While the trends are
+significant and match the magnitude of the demographic variables, the low $r^2$ 
+for the trends still provides evidence that Google Search Trends data cannot 
+replace survey analysis when trying to measure rare mask usage.
 
-```{r mask_analysis1}
-tribble(
-  ~'measure',~'face_mask', ~'mask', ~'cloth_face_mask',  
-  "Mask Rare, Pearson's R Correlation",
-  cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),
-  cor(mask$mask_rare, mask$mask, use = "complete.obs"),
-  cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs")
-)  %>% 
-  kbl(digits=4) %>%
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
-```
+```{r mask_analysis}
+#|  results='asis',
+#| tab.cap = "Linear Regression Results for Rare Mask Usage"
 
-```{r mask_analysis2}
 mask <- mask %>% 
@@
 
-modelsummary(list(mask_1, mask_2, mask_3), 
+modelsummary(list(mask_2, mask_1, mask_3), 
              # title = "Linear Regression Results for Rare Mask Usage",
@@
 ```
-pearson correlations
-rsquared
-coefficients
-conclusion
 
@@
 
-```{r covid_analysis1}
-covid_corrs <- read_rds(here('data', 'from_hpc', 'covid_corrs.rds'))
-# covid_corrs[1,1] <- "Covid Rate, Pearson's R Correlation"
-# write_rds(covid_corrs, here('data', 'from_hpc', 'covid_corrs.rds'))
-
-covid_corrs %>% 
-  kbl(digits=4) %>%
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
-```
-
-```{r covid_analysis2}
+```{r covid_analysis}
 covid <- covid %>% 
@@
 
-modelsummary(list(covid_1, covid_2, covid_3), 
+modelsummary(list(covid_2, covid_1, covid_3), 
              # title = "Hierarchical Model for Covid Case Rates",
@@
 
-```{r suicide_analysis1}
-suicide_corrs <- read_rds(here('data', 'from_hpc', 'suicide_corrs.rds'))
-
-# suicide_corrs[1,1] <- "Death by Suicide Rate, Pearson's R Correlation"
-# suicide_corrs[2,1] <- "Death by Suicide Rate, rmcorr"
-# 
-# write_rds(suicide_corrs, here('data', 'from_hpc', 'suicide_corrs.rds'))
-
-suicide_corrs %>% 
-  kbl(digits=4) %>%
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
-```
-
-```{r suicide_analysis2}
+```{r suicide_analysis}
 suicide <- suicide %>% 
@@
 
-modelsummary(list(suicide_1, suicide_2, suicide_3), 
+modelsummary(list(suicide_2, suicide_1, suicide_3), 
              # title = "Hierarchical Model for Suicide Rates",
@@
 
-```{r pres_2016_analysis1}
-tribble(
-  ~'measure',~'Searches for Hilary Clinton', ~ 'Searches for Donald Trump',
-  "Votes for Clinton, Pearson's R Correlation",
-  cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
-  cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),
-
-  "Votes for Trump, Pearson's R Correlation",
-  cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),
-  cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),
-)  %>% 
-  kbl(digits=4) %>%
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
-```
-
-```{r pres_2016_analysis2}
+```{r pres_2016_analysis}
 pres_2016 <- pres_2016 %>% 
@@
 
-modelsummary(list(vacc_hes_1a, vacc_hes_2a,vacc_hes_3a 
+modelsummary(list(vacc_hes_2a,vacc_hes_1a, vacc_hes_3a 
                   # ,vacc_hes_1b, vacc_hes_2b,vacc_hes_3b
@@
 
-```{r pres_2020_analysis1}
-tribble(
-  ~'measure',~'Searches for Joe Biden', ~ 'Searches for Donald Trump',
-  "Votes for Biden, Pearson's R Correlation",
-  cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),
-  cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),
-
-  "Votes for Trump, Pearson's R Correlation",
-  cor(pres_2020$trump_p, pres_2020$`Joe Biden`, use = "complete.obs"),
-  cor(pres_2020$trump_p, pres_2020$`Donald Trump`, use = "complete.obs"),
-)  %>% 
-  kbl(digits=4) %>%
-  #overall styling
-  kable_styling(latex_options = c( "hold_position"), full_width = T)
-```
-
-```{r pres_2020_analysis2}
+```{r pres_2020_analysis}
 pres_2020 <- pres_2020 %>% 
@@
 
-modelsummary(list(vacc_hes_1a, vacc_hes_2a,vacc_hes_3a 
+modelsummary(list(vacc_hes_2a, vacc_hes_1a, vacc_hes_3a 
                   # ,vacc_hes_1b, vacc_hes_2b,vacc_hes_3b

### 2022-03-01 paper1-cleaning.Rmd
Finish initial findings

@@
 
-vacc_hes_gtrends <- find_cross_sectional_trends(c('covid conspiracy',
-                                                  'COVID-19 vaccine',
-                                                  'Coronavirus',
-                                                  'Covid-19'
-                                                  # URLdecode('%2Fg%2F11j8_9sv06'),
-                                                  # URLdecode('%2Fg%2F11j2cc_qll')
-                                                  ), 
-                            '2021-05-26', 12) %>%   
-  pivot_wider(names_from = keyword, values_from = hits)  %>% 
-  select(-date) %>% 
-  janitor::clean_names()
+# vacc_hes_gtrends <- find_cross_sectional_trends(c('covid conspiracy',
+#                                                   'COVID-19 vaccine',
+#                                                   'Coronavirus',
+#                                                   'Covid-19'
+#                                                   # URLdecode('%2Fg%2F11j8_9sv06'),
+#                                                   # URLdecode('%2Fg%2F11j2cc_qll')
+#                                                   ), 
+#                             '2021-05-26', 12) %>%   
+#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
+#   select(-date) %>% 
+#   janitor::clean_names()
+
+vacc_hes_gtrends <- read_csv(here('data', 'google_trends', 'covid19vaccinemarch3_152021.csv')) %>% 
+  full_join(read_csv(here('data', 'google_trends', 'vaccinemarch3_152021.csv')), by = "DMA") %>% 
+  full_join(read_csv(here('data', 'google_trends', 'Coronavirusdisease2019march3_152021.csv')), by = "DMA") %>% 
+  full_join(read_csv(here('data', 'google_trends', 'Coronavirusvirusmarch3_152021.csv')), by = "DMA")  %>% 
+  janitor::clean_names()  %>% 
+  mutate(dma = str_to_upper(dma),
+           dma = str_replace_all(dma,"-", " - "),
+           dma = str_replace_all(dma,",", ""),
+           dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))
 
@@
   left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
-  full_join(vacc_hes_gtrends, by = c('DMA_google' = 'location'))
+  full_join(vacc_hes_gtrends, by = c('DMA_google' = 'dma'))
 
 vacc_hes %>% 
-  pivot_longer(cols = covid_conspiracy:covid_19) %>% 
+  pivot_longer(cols = covid_19_vaccine:coronavirus_virus) %>% 
   ggplot(aes(y = vacc_hesitant, x = value, color = name)) +
@@
 
-mask_gtrends <- find_cross_sectional_trends(c('Face mask',
-                                              'Mask',
-                                              'Cloth face mask'
-                                              ),
-                                            '2020-07-02', 12)%>%   
-  pivot_wider(names_from = keyword, values_from = hits)  %>% 
-  select(-date) %>% 
-  janitor::clean_names()
+# mask_gtrends <- find_cross_sectional_trends(c('Face mask',
+#                                               'Mask',
+#                                               'Cloth face mask'
+#                                               ),
+#                                             '2020-07-02', 12)%>%   
+#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
+#   select(-date) %>% 
+#   janitor::clean_names()
+
+mask_gtrends <- read_csv(here('data', 'google_trends', 'Coronavirusdisease2019july2_142020.csv')) %>% 
+  full_join(read_csv(here('data', 'google_trends', 'Coronavirusvirusjuly2_142020.csv')), by = "DMA") %>% 
+    full_join(read_csv(here('data', 'google_trends', 'Cloth face mask july2_142020.csv')), by = "DMA")  %>% 
+    full_join(read_csv(here('data', 'google_trends', 'mask july2_142020.csv')), by = "DMA")  %>% 
+    full_join(read_csv(here('data', 'google_trends', 'Civil and political rights july2_142020.csv')), by = "DMA")  %>% 
+    full_join(read_csv(here('data', 'google_trends', 'Anti-mask law july2_142020.csv')), by = "DMA")  %>% 
+  janitor::clean_names()  %>% 
+    mutate(dma = str_to_upper(dma),
+           dma = str_replace_all(dma,"-", " - "),
+           dma = str_replace_all(dma,",", ""),
+           dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))
 
@@
   left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
-  full_join(mask_gtrends, by = c('DMA_google' = 'location'))
+  full_join(mask_gtrends, by = c('DMA_google' = 'dma'))
 
 mask %>% 
-  pivot_longer(cols = face_mask:civil_and_political_rights) %>% 
+  pivot_longer(cols = coronavirus_disease:anti_mask_law) %>% 
   ggplot(aes(y = mask_rare, x = value, color = name)) +
@@
   results <- tibble('location' = character(),
-    'suicide' = numeric(), 
-    'depression' = numeric(),
+    # 'suicide' = numeric(), 
+    # 'depression' = numeric(),
     'suicide hotline' = numeric(),
@@
     print(glue("finding trends for {i}..."))
-    results <- find_cross_sectional_trends(c('suicide', 'depression', 'suicide hotline'),
+    results <- find_cross_sectional_trends(c('suicide hotline'
+      # 'suicide', 'depression', 
+      ),
                                 glue("{i}-01-01"), 365) %>%
@@
 
-suicide_gtrends <- append_years(2010, 2020)
+hotline_gtrends <- append_years(2010, 2020)
+hotline_rescale_point <-  read_csv(here('data', 'google_trends', 'suicidehotline_long_LA.csv')) %>% 
+  mutate(dma = 'LOS ANGELES (CA)',
+         year = as.numeric(str_sub(Month, 1, 4)),
+         month = as.numeric(str_sub(Month, 6, 7)))  %>% 
+  group_by(year, dma) %>%
+  summarize(hits_rescale = mean(`suicide hotline`, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  left_join(hotline_gtrends, by = c('year' = 'year', 'dma' = 'location'))  %>% 
+  mutate(rescale_ratio = hits_rescale / `suicide hotline`)  %>%
+  select(year, rescale_ratio)
 
-suicide <- suicide_measures %>% 
-  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
-  full_join(suicide_gtrends, by = c('DMA_google' = 'location', 'year' = 'year'))  %>% 
+hotline <- hotline_gtrends %>% 
+  group_by(location) %>% 
+  fill( `suicide hotline`) %>%
+  ungroup() %>% 
+  left_join(hotline_rescale_point, by = "year") %>% 
+  mutate(`suicide hotline` = `suicide hotline` * rescale_ratio) %>% 
+  rename(suicide_hotline = `suicide hotline`) %>% 
+  select(-rescale_ratio)
+
+suicide <- mutate(read_csv(here('data', 'google_trends', 'suicide2010.csv')), year = 2010) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2011.csv')), year = 2011)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2012.csv')), year = 2012)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2013.csv')), year = 2013)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2014.csv')), year = 2014)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2015.csv')), year = 2015)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2016.csv')), year = 2016)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2017.csv')), year = 2017)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2018.csv')), year = 2018)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2019.csv')), year = 2019)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'suicide2020.csv')), year = 2020)) %>% 
   janitor::clean_names()
 
+suicide_rescale_point <-  read_csv(here('data', 'google_trends', 'suicide_long_LA.csv')) %>% 
+  mutate(dma = 'Los Angeles CA',
+        year = as.numeric(str_sub(Month, 1, 4)),
+        month = as.numeric(str_sub(Month, 6, 7)))  %>% 
+  group_by(year, dma) %>%
+  summarize(hits_rescale = mean(Suicide, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  left_join(suicide, by = c('year', 'dma'))  %>% 
+  mutate(rescale_ratio = hits_rescale / suicide)  %>%
+  select(year, rescale_ratio)
+
 suicide <- suicide %>% 
+    group_by(dma) %>% 
+    fill(suicide) %>%
+    ungroup() %>% 
+    left_join(suicide_rescale_point, by = "year") %>% 
+    mutate(suicide = suicide * rescale_ratio) %>% 
+  select(-rescale_ratio) %>% 
+  mutate(dma = str_to_upper(dma),
+         dma = str_replace_all(dma,"-", " - "),
+         dma = str_replace_all(dma,",", ""),
+         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))
+
+depression <- mutate(read_csv(here('data', 'google_trends', 'depression2010.csv')), year = 2010) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2011.csv')), year = 2011)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2012.csv')), year = 2012)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2013.csv')), year = 2013)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2014.csv')), year = 2014)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2015.csv')), year = 2015)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2016.csv')), year = 2016)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2017.csv')), year = 2017)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2018.csv')), year = 2018)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2019.csv')), year = 2019)) %>% 
+  bind_rows(mutate(read_csv(here('data', 'google_trends', 'depression2020.csv')), year = 2020)) %>% 
+  janitor::clean_names()
+
+depression_rescale_point <-  read_csv(here('data', 'google_trends', 'depression_long_LA.csv')) %>% 
+  mutate(dma = 'Los Angeles CA',
+        year = as.numeric(str_sub(Month, 1, 4)),
+        month = as.numeric(str_sub(Month, 6, 7)))  %>% 
+  group_by(year, dma) %>%
+  summarize(hits_rescale = mean(Depression, na.rm = TRUE)) %>% 
+  ungroup() %>% 
+  left_join(depression, by = c('year', 'dma'))  %>% 
+  mutate(rescale_ratio = hits_rescale / depression)  %>%
+  select(year, rescale_ratio)
+
+depression <- depression %>% 
+    group_by(dma) %>% 
+    fill(depression) %>%
+    ungroup() %>% 
+    left_join(depression_rescale_point, by = "year") %>% 
+    mutate(depression = depression * rescale_ratio) %>% 
+  select(-rescale_ratio)  %>% 
+  mutate(dma = str_to_upper(dma),
+         dma = str_replace_all(dma,"-", " - "),
+         dma = str_replace_all(dma,",", ""),
+         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"))
+
+suicide_data <- suicide_measures %>% 
+  left_join(select(dma, FIPS, DMA_google), by = c('fips' = 'FIPS')) %>% 
+  full_join(suicide, by = c('DMA_google' = 'dma', 'year' = 'year')) %>% 
+  full_join(depression, by = c('DMA_google' = 'dma', 'year' = 'year')) %>% 
+  full_join(hotline, by = c('DMA_google' = 'location', 'year' = 'year')) %>% 
   group_by(fips) %>%
-  mutate(deaths           = na.approx(deaths, na.rm = FALSE),
+  mutate(death_rate       = na.approx(death_rate, na.rm = FALSE),
          population       = na.approx(population, na.rm = FALSE),
@@
 
-suicide <- suicide %>% 
+suicide_data <- suicide_data %>% 
   left_join(county, by = c('fips', 'year'))
 
-write_rds(suicide, here('data', 'cleaned_data', 'suicide.rds'))
+write_rds(suicide_data, here('data', 'cleaned_data', 'suicide.rds'))
 
@@
 
-pres_2020_gtrend <- find_cross_sectional_trends(c('Joe Biden', 'Donald Trump'), '2020-01-01', 307) %>% 
-  pivot_wider(names_from = keyword, values_from = hits)  %>% 
-  select(-date)
+# pres_2020_gtrend <- find_cross_sectional_trends(c('Joe Biden', 'Donald Trump'), '2020-01-01', 307) %>% 
+#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
+#   select(-date)
+pres_2020_gtrend <- read_csv(here('data', 'google_trends', 'presidents_2020.csv')) %>% 
+  janitor::clean_names() %>% 
+  mutate(dma = str_to_upper(dma),
+         dma = str_replace_all(dma,"-", " - "),
+         dma = str_replace_all(dma,",", ""),
+         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"),
+         donald_trump_trend = as.numeric(str_remove(donald_trump, '%')), 
+         joe_biden_trend = as.numeric(str_remove(joe_biden, '%')))
 
-pres_2016_gtrend <- find_cross_sectional_trends(c('Hilary Clinton', 'Donald Trump'), '2016-01-01', 307) %>% 
-  pivot_wider(names_from = keyword, values_from = hits)  %>% 
-  select(-date)
+# pres_2016_gtrend <- find_cross_sectional_trends(c('Hilary Clinton', 'Donald Trump'), '2016-01-01', 307) %>%
+#   pivot_wider(names_from = keyword, values_from = hits)  %>% 
+#   select(-date)
+pres_2016_gtrend <- read_csv(here('data', 'google_trends', 'presidents_2016.csv')) %>% 
+  janitor::clean_names() %>% 
+  mutate(dma = str_to_upper(dma),
+         dma = str_replace_all(dma,"-", " - "),
+         dma = str_replace_all(dma,",", ""),
+         dma = str_replace_all(dma,"\\s(\\w{2})\\b", " \\(\\1\\)"),
+         donald_trump_trend = as.numeric(str_remove(donald_trump, '%')), 
+         hillary_clinton_trend = as.numeric(str_remove(hillary_clinton, '%')))
 
@@
   inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>%
-  left_join(pres_2016_gtrend, by = c('DMA_google' = 'location')) %>%
+  left_join(pres_2016_gtrend, by = c('DMA_google' = 'dma')) %>%
   select(dma = DMA_google,
          fips = county_fips, 
-         clinton_p, `Hilary Clinton`, trump_p, `Donald Trump`)
+         clinton_p, hillary_clinton_trend, trump_p, donald_trump_trend)
 
-pres_2016 %>% ggplot(aes(x = trump_p, y = `Donald Trump`)) + geom_jitter() + geom_smooth()
-pres_2016 %>% ggplot(aes(x = clinton_p, y = `Hilary Clinton`)) + geom_jitter()
+pres_2016 %>% ggplot(aes(x = trump_p, y = donald_trump_trend)) + geom_jitter() + geom_smooth()
+pres_2016 %>% ggplot(aes(x = clinton_p, y = hillary_clinton_trend)) + geom_jitter()+ geom_smooth()
 
@@
   inner_join(select(dma, FIPS, DMA_google), by = c('county_fips' = 'FIPS')) %>% 
-  left_join(pres_2020_gtrend, by = c('DMA_google' = 'location')) %>% 
+  left_join(pres_2020_gtrend, by = c('DMA_google' = 'dma')) %>% 
   select(dma = DMA_google,
          fips = county_fips, 
-         biden_p, `Joe Biden`, trump_p, `Donald Trump`)
+         biden_p, joe_biden_trend, trump_p, donald_trump_trend)
 
-pres_2020 %>% ggplot(aes(x = biden_p, y = Joe Biden`)) + geom_jitter() + geom_smooth()
-pres_2020 %>% ggplot(aes(x = trump_p, y = `Donald Trump`)) + geom_jitter() + geom_smooth()
+pres_2020 %>% ggplot(aes(x = biden_p, y =joe_biden_trend)) + geom_jitter() + geom_smooth()
+pres_2020 %>% ggplot(aes(x = trump_p, y = donald_trump_trend)) + geom_jitter() + geom_smooth()
 

### 2022-03-01 paper1.Rmd
Finish initial findings

@@
 ---
-title: "Article 1:	Construct Validity and Correspondence of Google Trends"
+title: "Article 1: Digital Trace Data as Indicators of Social Data Validating Google Trends for  use in Scientific Research"
 author: "Kelsey Gonzalez"
@@
   bookdown::pdf_document2: 
+    keep_tex: true
     latex_engine: xelatex
@@
    - \usepackage{placeins}
+   - \usepackage{hhline}
    - \doublespacing
@@
 ```{r data}
+#| cache = FALSE
+
 vacc_hes <- read_rds(here('data', 'cleaned_data', 'vacc_hes.rds'))
@@
 
+Digital Trace Data as Indicators of Social Data: Validating Google Trends for
+ use in Scientific Research
+
 **Keywords**:
@@
 can ignore foundational issues of measurement and construct validity and
-reliability and dependencies among data" \[@lazerParableGoogleFlu2014,
-p. 1203\]. Building on this prior research outlining these various
+reliability and dependencies among data" [@lazerParableGoogleFlu2014,
+p. 1203]. Building on this prior research outlining these various
 issues with big data [@boydCriticalQuestionsBig2012;
@@
 
-"Behaviors and Attitudes","Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "covid conspiracy', 'COVID-19 vaccine', 'Coronavirus', 'Covid-19'",
+"Behaviors and Attitudes","Vaccine Hesitancy for COVID-19", "Cross-Sectional", "March 3 – 15, 2021", "Search Topics: 'Covid-19 vaccine', 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Vaccine'",
 
-"Behaviors and Attitudes","Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "'Face Mask', 'Mask', 'Cloth Face Mask'",
+"Behaviors and Attitudes","Mask-Wearing Survey Data", "Cross-Sectional", "July 2 - 14, 2020", "Search Topics: 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Cloth Face Mask', 'Mask', 'Civil and Political Rights'",
 
@@
 
-"Health","County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "'Suicide', 'Depression',' Suicide Hotline'",
+"Health","County Suicide Rates", "Longitudinal", "Yearly 2010-2020", "Search Topics: 'Suicide', 'Depression', Search Term:' Suicide Hotline'",
 
@@
 
-'Political',"Presidential Election Results", "Cross Sectional", "2016 & 2020", "'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
+'Political',"Presidential Election Results", "Cross Sectional", "2016 & 2020", "Search Topics: 'Hilary Clinton', 'Donald Trump', 'Joe Biden'"
  ) %>% as_grouped_data(groups = c("type"), columns = NULL)
@@
 Raw data is on a scale from 0 to 100, with 100 being the maximum search
-popularity out of all DMAs. Google Search Trend are now only available
-cross-sectionally (a single time period across a geography) or as time-series (a
-single geo-location across time). To remedy this and build a longitudinal
-dataset of each search topic for the longitudinal datasets, I follow the method
-proposed in @park_etal (p. 5). This method involves building a dataset of
-unscaled cross-sectional values, selecting a DMA to use to establish the
-rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
-values for the one DMA. To find the rescaling ratio for each week in the
-time-series, you divide the time-series value for each week by the
-cross-sectional value for each week, resulting in a rescaling vector to be used
-for all weeks in the dataset across geographies. To rescale each longitudinal
-value, multiply the respective week's rescaling ratio by the cross-sectional
-value. Rescaled longitudinal data was compared against time-series data for
-multiple test counties and was equivalent. For a more in-depth explanation of
-this procedure, see @park_etal (p. 5). Missing datapoints in longitudinal
-datasets were filled in with interpolated values using `zoo::na.approx()`
-[@zoo].
+popularity out of all DMAs. When available, I use Google search topics to
+measure trends as opposed to search terms. Search topics are a more robust
+measurement than a single search term: topics are aggregations of the rates of
+multiple, highly correlated search terms together into a cohesive topic. For
+example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
+search terms, 'Beyoncé Knowles' encompasses all of these into a single search
+topic. Google Search Trend are only available cross-sectionally (a single time
+period across a geography) or as time-series (a single geo-location across
+time). To remedy this and build a longitudinal dataset of each search topic for
+the longitudinal datasets, I follow the method proposed in @park_etal (p. 5).
+This method involves building a dataset of unscaled cross-sectional values,
+selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
+CA'), and then finding the time-series values for the one DMA. To find the
+rescaling ratio for each week in the time-series, you divide the time-series
+value for each week by the cross-sectional value for each week, resulting in a
+rescaling vector to be used for all weeks in the dataset across geographies. To
+rescale each longitudinal value, multiply the respective week's rescaling ratio
+by the cross-sectional value. Rescaled longitudinal data was compared against
+time-series data for multiple test counties and was equivalent. For a more
+in-depth explanation of this procedure, see @park_etal (p. 5). Missing
+datapoints in longitudinal datasets were filled in with interpolated values
+using `zoo::na.approx()` [@zoo].
 
@@
 
-## Cultural
+## Validating Google Trends as metrics of attitudinal indicators
+
 ```{r corr-results}
@@
 table2 <- tribble(
-  ~'grp', ~'variable', ~'measure',~'trend1', ~'trend2', ~'trend3', ~'trend4', 
-  "Vaccine Hesitancy", NA,  NA, 'covid_conspiracy', 'covid_19_vaccine', 'coronavirus', 'covid_19', 
+  ~'grp', ~'variable', ~'measure',~'trend1', ~'trend2', ~'trend3', ~'trend4', ~'trend5', 
+  "Vaccine Hesitancy", NA,  NA, 'Covid-19 vaccine', 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Vaccine', NA,
   "Vaccine Hesitancy", "Vaccine Hesitancy", "Pearson's R Correlation",
-  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_conspiracy, use = "complete.obs"),4)),
   as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19_vaccine, use = "complete.obs"),4)),
-  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus, use = "complete.obs"),4)),
-  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$covid_19, use = "complete.obs"),4)),
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus_disease, use = "complete.obs"),4)),
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$coronavirus_virus, use = "complete.obs"),4)),
+  as.character(round(cor(vacc_hes$vacc_hesitant, vacc_hes$vaccine, use = "complete.obs"),4)), NA,
 
-  "Mask Attitudes",NA,  NA, 'face_mask', 'mask', 'cloth_face_mask',  NA,
+  "Mask Attitudes",NA,  NA, 'Coronavirus (Disease)', 'Coronavirus (Virus)', 'Cloth Face Mask', 'Mask', 'Civil and Political Rights',
   "Mask Attitudes","Mask Rare", "Pearson's R Correlation",
-  as.character(round(cor(mask$mask_rare, mask$face_mask, use = "complete.obs"),4)),
-  as.character(round(cor(mask$mask_rare, mask$mask, use = "complete.obs"),4)),
-  as.character(round(cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs"), 4)), NA,
+  as.character(round(cor(mask$mask_rare, mask$coronavirus_disease, use = "complete.obs"),4)),
+  as.character(round(cor(mask$mask_rare, mask$coronavirus_virus, use = "complete.obs"),4)),
+  as.character(round(cor(mask$mask_rare, mask$cloth_face_mask, use = "complete.obs"), 4)), 
+  as.character(round(cor(mask$mask_rare, mask$mask, use = "complete.obs"), 4)), 
+  as.character(round(cor(mask$mask_rare, mask$civil_and_political_rights, use = "complete.obs"), 4)),
 
-  "Covid Rates",NA,  NA, 'covid_19',  'smell_loss', 'taste_loss', NA, 
+  "Covid Rates",NA,  NA, 'covid_19',  'smell_loss', 'taste_loss', NA, NA, 
   "Covid Rates","Covid Rate", "Pearson's R Correlation", 
@@
   as.character(round(cor(covid$covid_rate, covid$taste_loss, use = "complete.obs"),4)),
-  NA,
-  "Covid Rates","Covid Rate", "rmcorr", 
+  NA,NA, 
+  "Covid Rates","Covid Rate", "repeated measures correlation coefficient", 
   as.character(covid_corrs[[2,2]]), 
   as.character(covid_corrs[[2,3]]), 
-  as.character(covid_corrs[[2,4]]), NA,
+  as.character(covid_corrs[[2,4]]), NA,NA,
 
-  "Suicide Rates",NA,  NA, 'suicide', 'depression', 'suicide_hotline', NA, 
+  "Suicide Rates",NA,  NA, 'suicide', 'depression', 'suicide_hotline', NA,NA,  
   "Suicide Rates","Suicide Rate", "Pearson's R Correlation",
@@
   as.character(round(cor(suicide$death_rate, suicide$suicide_hotline, use = "complete.obs"),4)),
-  NA,
-  "Suicide Rates","Suicide Rate", "rmcorr", 
+  NA,NA, 
+  "Suicide Rates","Suicide Rate", "repeated measures correlation coefficient", 
   as.character(suicide_corrs[[2,2]]), 
   as.character(suicide_corrs[[2,3]]), 
-  as.character(suicide_corrs[[2,4]]), NA,
+  as.character(suicide_corrs[[2,4]]), NA,NA,
 
-  "2016 Presidential Votes",NA,  NA, 'Hilary Clinton',  'Donald Trump', NA, NA,
+  "2016 Presidential Votes",NA,  NA, 'Hilary Clinton',  'Donald Trump', NA, NA,NA, 
   "2016 Presidential Votes","2016 Votes for Clinton", "Pearson's R Correlation",
-  as.character(round(cor(pres_2016$clinton_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),4)),
-  as.character(round(cor(pres_2016$clinton_p, pres_2016$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
+  as.character(round(cor(pres_2016$clinton_p, pres_2016$hillary_clinton_trend, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2016$clinton_p, pres_2016$donald_trump_trend, use = "complete.obs"),4)), NA, NA,NA, 
   "2016 Presidential Votes","2016 Votes for Trump", "Pearson's R Correlation",
-  as.character(round(cor(pres_2016$trump_p, pres_2016$`Hilary Clinton`, use = "complete.obs"),4)),
-  as.character(round(cor(pres_2016$trump_p, pres_2016$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
+  as.character(round(cor(pres_2016$trump_p, pres_2016$hillary_clinton_trend, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2016$trump_p, pres_2016$donald_trump_trend, use = "complete.obs"),4)), NA, NA,NA,
 
-  "2016 Presidential Votes",NA,  NA, 'Joe Biden',  'Donald Trump', NA, NA,
-  "2016 Presidential Votes","2020 Votes for Biden", "Pearson's R Correlation",
-  as.character(round(cor(pres_2020$biden_p, pres_2020$`Joe Biden`, use = "complete.obs"),4)),
-  as.character(round(cor(pres_2020$biden_p, pres_2020$`Donald Trump`, use = "complete.obs"),4)), NA, NA,
-  "2016 Presidential Votes","2020 Votes for Trump", "Pearson's R Correlation",
-  as.character(round(cor(pres_2020$trump_p, pres_2020$`Joe Biden`, use = "complete.obs"),4)),
-  as.character(round(cor(pres_2020$trump_p, pres_2020$`Donald Trump`, use = "complete.obs"),4)), NA, NA
+  "2020 Presidential Votes",NA,  NA, 'Joe Biden',  'Donald Trump', NA, NA,NA, 
+  "2020 Presidential Votes","2020 Votes for Biden", "Pearson's R Correlation",
+  as.character(round(cor(pres_2020$biden_p, pres_2020$joe_biden_trend, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2020$biden_p, pres_2020$donald_trump_trend, use = "complete.obs"),4)), NA, NA,NA, 
+  "2020 Presidential Votes","2020 Votes for Trump", "Pearson's R Correlation",
+  as.character(round(cor(pres_2020$trump_p, pres_2020$joe_biden_trend, use = "complete.obs"),4)),
+  as.character(round(cor(pres_2020$trump_p, pres_2020$donald_trump_trend, use = "complete.obs"),4)), NA, NA, NA 
 )  %>%   
-  select(grp, measure, variable, trend1, trend2, trend3, trend4) %>% 
+  select(grp, measure, variable, trend1, trend2, trend3, trend4, trend5) %>% 
   as_grouped_data(groups = c("grp"), columns = NULL)
@@
 [@vaches_data]. When comparing the measure of vaccine hesitancy to four
-different Google Search Trends, the correlation does not exceed -0.4021
-('Coronavirus' and vaccine hesitancy). Correlation's under |0.40| are considered
-to be weak according to the common rules of thumb. When running these
+different Google Search Trends, the correlation does not exceed -0.4657
+('Coronavirus (Disease)' and vaccine hesitancy). Correlation's under |0.40| are
+considered to be weak according to the common rules of thumb. When running these
 correlations in multiple linear regression (see the results in table
-\@ref(tab:vacc_hes_analysis)), I see an $r^2$ of 0.221 (Model 1)
-and 0.346 (Model 2), indicating that the Google Trends are able to explain about
-22% of the variation in Vaccine Hesitancy alone. Demographic characteristics
-like the percentage of households with broadband internet and the population
-density are able to explain about 35% of the variation (model 3), outperforming
-the first two models. The Trend coefficients themselves, however, are
-significant and remain significant when controlling for demographics. This
-reinforces the finding from the Pearson Correlation that there is a significant
-but weak relationship between the Google Trends and Vaccine Hesitancy.
+\@ref(tab:vacc_hes_analysis)), I see an $r^2$ of 0.233 (Model 1) and 0.411
+(Model 2), indicating that the Google Trends are able to explain about 23% of
+the variation in Vaccine Hesitancy alone. Demographic characteristics like the
+percentage of households with broadband internet and the population density are
+able to explain about 35% of the variation (model 2), outperforming the first
+models. The Trend coefficients themselves, however, are significant and remain
+significant when controlling for demographics. This reinforces the finding from
+the Pearson Correlation that there is a significant but weak relationship
+between the Google Trends and Vaccine Hesitancy.
 
@@
   select(-c(DMA_google, Geo_QName)) %>% 
-  mutate(across(covid_conspiracy:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+  mutate(across(covid_19_vaccine:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
 
@@
                   data = vacc_hes)
-vacc_hes_2 <- lm(vacc_hesitant  ~  covid_19_vaccine +     
-                   coronavirus +covid_19,
-                 data = vacc_hes)
-vacc_hes_2b <- lm(vacc_hesitant  ~ covid_conspiracy + covid_19_vaccine +
-                    coronavirus +covid_19,
+vacc_hes_2 <- lm(vacc_hesitant  ~  covid_19_vaccine + vaccine + 
+                   coronavirus_disease + coronavirus_virus,
                  data = vacc_hes)
@@
                     over_65 + poverty_rate + median_income + broadband + 
-                    covid_19_vaccine +
-                    coronavirus +covid_19,
+                    covid_19_vaccine + vaccine + 
+                   coronavirus_disease + coronavirus_virus,
                    data = vacc_hes)
 
-modelsummary(list(vacc_hes_2, vacc_hes_2b, vacc_hes_1, vacc_hes_3), 
+modelsummary(list(vacc_hes_2, vacc_hes_1, vacc_hes_3), 
              # title = "Linear Regression Results for Vaccine Hesitancy",
@@
 The second attitudinal measure I test is how Google Trends relates to rare mask
-usage. As with vaccine hesitancy, the Pearson correlations are weak, if not 
-negligible. I introduce these trends in multiple linear regression in table 
-\@ref(tab:mask_analysis). Model 1 demonstrates that these three Google Search
-Trends can explain about 9% of the variance in mask usage across U.S. counties,
-reinforcing the conclusion that the relationship is quite weak. The coefficients
-themselves are somewhat significant in Model 1. However, after including the
-demographic varaibles in Models 2 and 3, we see that the relationship between
-the Google Search Trends and mask usage is strengthed in magnitude and in
-significance, likely indicating a repression effect due to background
-relationships between the trends and demograhic variables. While the trends are
-significant and match the magnitude of the demographic variables, the low $r^2$ 
-for the trends still provides evidence that Google Search Trends data cannot 
-replace survey analysis when trying to measure rare mask usage.
+usage. As with vaccine hesitancy, the Pearson correlations are negligible.
+Correlation's under |0.20| are considered to be negigible according to the
+common rules of thumb. I introduce these trends in multiple linear regression in
+table \@ref(tab:mask_analysis). Model 1 demonstrates that these five Google
+Search Trends can explain about 7% of the variance in mask usage across U.S.
+counties, reinforcing the conclusion that the relationship is quite weak. The
+coefficients themselves are somewhat significant in Model 1. However, after
+including the demographic variables in Models 2 and 3, we see that the
+relationship between the Google Search Trends and mask usage is strengthened in
+magnitude and in significance, likely indicating a suppression effect due to
+underlying relationships between the trends and demographic variables. While the
+trends are significant and match the demographic variables in magnitude, the
+low $r^2$ of 0.203 for the trends still provides evidence that Google Search
+Trends data cannot replace survey analysis when trying to measure rare mask
+usage.
 
@@
   select(-c(DMA_google, Geo_QName)) %>% 
-  mutate(across(face_mask:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+  mutate(across(coronavirus_disease:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
 
@@
               data = mask)
-mask_2 <- lm(mask_rare  ~  face_mask + mask + cloth_face_mask,
+
+mask_2 <- lm(mask_rare  ~ coronavirus_disease +
+               coronavirus_virus + cloth_face_mask + 
+               mask + civil_and_political_rights,
              data = mask)
+
 mask_3  <- lm(mask_rare  ~ 
@@
                 over_65 + poverty_rate + median_income + broadband + 
-                    face_mask + mask + cloth_face_mask,
+                coronavirus_disease +
+                coronavirus_virus + cloth_face_mask + 
+                mask + civil_and_political_rights,
               data = mask)
@@
 
-## Medical
+## Validating Google Trends as metrics of health outcomes
+
+In addition to attitudinal measures, I attempt to validate Google Trends for
+uses in the measurements of health indicators. The first indicator I test is
+Covid-19 case rates from 2020 through 2021. The Pearson correlation results
+indicate negligible to weak relationships between the search terms and the
+actual case rates across time and place. The repeated measures correlation
+coefficient, a more reliable and less biased measure for longitudinal
+correlations, reveals similarly weak results with a maximum correlation of 0.32
+between 'smell loss' and rates of Covid-19. To further test the relationship, I
+include the three trends in random intercept hierarchical linear models. Model 1
+of table \@ref(tab:covid_analysis) indicates that the trends themselves are able
+to explain about 20% of the variation in Covid-19 rates ($r^2$ = 0.201). Few
+of the demographic variables have an effect on Covid-19 rates in models 2 or 3,
+though it seems there is some suppression for median income, unemployment rates,
+and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
+Google Trends are slightly related to Covid-19 rates, but that this relationship
+is weak and we should not attempt to use Google Trends as an indicator of actual
+health outcomes.
 
@@
 covid <- covid %>% 
+  ungroup() %>% 
   select(-c(dma_google, Geo_QName, county, state)) %>% 
@@
              estimate = "{estimate}{stars}",
-             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
+             gof_omit = 'AIC|BIC|ICC|RMSE|SD') %>%
   kable_styling(latex_options = c("hold_position", 'condensed'),
@@
 ```
-pearson correlations
-rmcorr
-rsquared
-coefficients
-conclusion
+
+Another indicator of health outcomes I test to validate Google Trends as
+possible health indicators are county suicide rates. As with previous cases,
+there is only negligible correlation between actual suicide rates and Google
+Search Trends, not exceeding 0.0845. In the more accurate repeated measures
+correlation coefficient we see a maximum of 0.142 correlation, remaining
+negligible. I introduce these trends into a random intercept model to control
+for inter-group variation over time in table \@ref(tab:suicide_analysis). While
+table \@ref(tab:suicide_analysis) model 1 reveals a significant relationship
+between suicide hotline trends and suicide rates, the effect is small and the
+entire model only has an $r^2$ of 0.058. Adding in demographic features in model
+2 improves the $r^2$ quite a lot. In model 3, the inclusion of Google Trends
+actually decreases the overall amount of suicide rate variance explained
+compared to model 2. These analyses lead me to conclude that Google Search
+Trends should not be used as indicators of suicide rates or intentions.
 
@@
 suicide <- suicide %>% 
-  select(-c(dma_google, Geo_QName, county, population, deaths)) %>% 
-  mutate(across(suicide:broadband  , ~ scale(.x, center=TRUE, scale=TRUE)[,1])) %>% 
+  select(-c(DMA_google, Geo_QName, county, population, deaths)) %>%
+  ungroup() %>% 
+  mutate(across(death_rate:broadband, ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+
+suicide <- suicide %>% 
   left_join(suicide %>%
@@
                   total_pop + pop_density + unemployment_rate + 
-                  over_65 + poverty_rate + median_income + broadband +
-                  death_rate_fips_mean + year,
+                  over_65 + poverty_rate + median_income +
+                  # death_rate_fips_mean +
+                    year,
                 random = ~ 1 | fips, na.action=na.omit,data = suicide)
 suicide_2 <- lme(death_rate   ~  
-                 suicide + depression + suicide_hotline + death_rate_fips_mean  + 
+                 suicide + depression + suicide_hotline + 
+                   # death_rate_fips_mean  +
                  year,
@@
                   total_pop + pop_density + unemployment_rate + 
-                  over_65 + poverty_rate + median_income + broadband + 
-                  suicide + depression + suicide_hotline + death_rate_fips_mean  +
+                  over_65 + poverty_rate + median_income +
+                  suicide + depression + suicide_hotline +
+                    # death_rate_fips_mean  +
                   year,
@@
   kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 8)
+                font_size = 10)
 
@@
 ```
-pearson correlations
-rmcorr
-rsquared
-coefficients
-conclusion
 
-## Political
+## Validating Google Trends as metrics of political support
+
+Previous research has showed some relationship between Google Search Trends and
+political election results. I test here the relationships between search trends
+and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
+correlations for Both Hilary Clinton and Donald Trump do not exceed a |0.17|
+correlation with the actual percentage of votes for either candidate. In 2020,
+results are even less related, with searches for neither Joe Biden nor Donald
+Trump holding any real correlation with the 2020 results.
+
+In table \@ref(tab:pres_2016_analysis), I outline the results for the model
+predicting the county percentage of votes for Hillary Clinton. Model 1
+demonstrates how well Google Trends are able to predict the votes; while the
+trend for 'Hillary Clinton' is significantly associated with votes, the model's
+$r^2$ ($r^2$ = 0.027) shows that it does little to help explain the model
+variance. On the other hand, adding in demographic features improves the model
+fit quite well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in
+model 3. In table \@ref(tab:pres_2020_analysis) shows this same analysis for the
+2020 election and predicts the percentage of votes for Joe Biden. While this
+model is largely similar to those in table \@ref(tab:pres_2016_analysis), this
+model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
+conclusion, I find that Google Trends are an unreliable and invalid indicator of
+political support.
 
@@
   select(-c(Geo_QName, dma)) %>% 
-  mutate(across(c(`Hilary Clinton`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+  mutate(across(c(hillary_clinton_trend,donald_trump_trend:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
 
@@
                   data = pres_2016)
-vacc_hes_2a <- lm(clinton_p   ~  `Donald Trump` + `Hilary Clinton`,
+vacc_hes_2a <- lm(clinton_p   ~  
+                    # donald_trump_trend + 
+                    hillary_clinton_trend,
                  data = pres_2016)
@@
                     over_65 + poverty_rate + median_income + 
-                     `Donald Trump` + `Hilary Clinton`,
+                     # donald_trump_trend + 
+                     hillary_clinton_trend,
                    data = pres_2016)
@@
                   data = pres_2016)
-vacc_hes_2b <- lm(trump_p    ~  `Donald Trump` + `Hilary Clinton`,
+vacc_hes_2b <- lm(trump_p    ~  donald_trump_trend + hillary_clinton_trend,
                  data = pres_2016)
@@
                     over_65 + poverty_rate + median_income + 
-                     `Donald Trump` + `Hilary Clinton`,
+                     donald_trump_trend + hillary_clinton_trend,
                    data = pres_2016)
@@
              estimate = "{estimate}{stars}",
-             gof_omit = 'AIC|BIC|ICC|RMSE'
+             gof_omit = 'AIC|BIC|ICC|RMSE|F'
              ) %>%
   kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 8)
+                font_size = 10)
 
 ```
-pearson correlations
-rsquared
-coefficients
-conclusion
 
@@
   select(-c(Geo_QName, dma)) %>% 
-  mutate(across(c(`Joe Biden`,`Donald Trump`:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
+  mutate(across(c(joe_biden_trend,donald_trump_trend:broadband)  , ~ scale(.x, center=TRUE, scale=TRUE)[,1]))
 
@@
                   data = pres_2020)
-vacc_hes_2a <- lm(biden_p   ~  `Donald Trump` + `Joe Biden`,
+vacc_hes_2a <- lm(biden_p   ~  
+                    # donald_trump_trend +
+                    joe_biden_trend,
                  data = pres_2020)
@@
                     over_65 + poverty_rate + median_income + 
-                     `Donald Trump` + `Joe Biden`,
+                     # donald_trump_trend + 
+                     joe_biden_trend,
                    data = pres_2020)
@@
                   data = pres_2020)
-vacc_hes_2b <- lm(trump_p    ~  `Donald Trump` + `Joe Biden`,
+vacc_hes_2b <- lm(trump_p    ~  donald_trump_trend ,
+                  # +                 joe_biden_trend,
                  data = pres_2020)
@@
                     over_65 + poverty_rate + median_income + 
-                     `Donald Trump` + `Joe Biden`,
+                     donald_trump_trend ,
+                   # + joe_biden_trend,
                    data = pres_2020)
@@
              estimate = "{estimate}{stars}",
-             gof_omit = 'AIC|BIC|ICC|RMSE'
+             gof_omit = 'AIC|BIC|ICC|RMSE|F'
              ) %>%
   kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 8)
+                font_size = 10)
 
 ```
-pearson correlations
-rsquared
-coefficients
-conclusion
 
 # Discussion
+
+The external validity of these voting
 
@@
 \newpage
-
-# References {.unnumbered}
-
-::: {#refs}
-:::
-
-\newpage
-
-# Appendix

### 2022-03-01 googletrends.R

@@ -1,133 +1,0 @@
-pacman::p_load(tidyverse, gtrendsR, lubridate, here, glue, zoo)
-
-find_mondays <- function(year) {
-  mondays <- seq(ymd(glue("{year}-01-01")),ymd(glue("{year}-12-31")),by="1 day")
-  mondays <- mondays[wday(mondays,label = TRUE) == "Mon" & mondays < today() - 7]
-  return(mondays)
-}
-find_initial_trends <- function(keyword, period_list){
-  period_list <- as.character(period_list)
-  
-  trends <- tibble(location = character(),hits = numeric(),keyword = character(),date = character())
-  
-  for (period in period_list){ 
-    ppl7<- as.character(ymd(period) + 7)
-    trends <- gtrends(
-      keyword = keyword,
-      geo = "US",
-      time = paste(period, ppl7),
-      gprop = "web",
-      category = 0,
-      hl = "en-US")$interest_by_dma %>%
-      tibble() %>%
-      mutate(date = period,
-             hits = as.numeric(hits)) %>% 
-      select(-c(geo, gprop)) %>%
-      bind_rows(trends)
-  }
-  
-  return(trends)
-}
-find_scale_point <- function(keyword, year){
-  if (year(today()) == year) {
-    span <- glue("{year}-01-01 {as.character(today() - 7)}")
-    } else {
-      span <- glue("{year}-01-01 {year}-12-31")
-    }
-  
-  if (nchar(span) != 21) stop('incorrect span')
-  
-  print(glue("keyword = {keyword}"))
-  print(glue("span = {span}"))
-  
-  rescale <- gtrends(
-    keyword = keyword,
-    geo = "US-CA-803",
-    time = span,
-    gprop = "web",
-    category = 0,
-    hl = "en-US", 
-    onlyInterest = TRUE, 
-    low_search_volume = FALSE)$interest_over_time %>% 
-    tibble()  %>% 
-    mutate(date = ymd(date(date))+1,
-           hits = ifelse(hits < 1, NA, hits)) %>%
-    fill(hits)%>% 
-    select(-c(gprop, keyword, geo, time, category)) %>% 
-    rename(hits_rescale = hits)
-  
-  if (rescale %>% drop_na() %>% nrow() == 0) stop('no rows of data')
-  return(rescale)
-}
-rescale_trends <- function(trends, rescale){
[…]

### 2022-06-18 paper1.Rmd
Final Dissertation Chapter 1 Version Update

@@
 output:
-  bookdown::pdf_document2: 
+  pdf_document: 
     keep_tex: true
     latex_engine: xelatex
-    number_sections: true
-  # bookdown::word_document2: 
-  #   toc: true
-  #   reference_docx: StylesTemplate.docx
 header-includes:
@@
 
+my_palette = c('#56b4e9','#999999','#E69F00','#009E73','#CC79A7','#0072B2','#D55E00','#E69F00')
 my_palette  <- c(MetBrewer::met.brewer(name = 'Cross', type = 'discrete'), '#555F61')
+
+## Automatically use showtext to render text
+font_add_google("Lora", "lora")
+showtext_auto()
+
+theme_diss <- function(base_size = 14) {
+  theme_minimal(base_size = base_size) %+replace%
+    theme(
+      # Figure assembly
+      plot.title = element_text(family="lora",
+                                size = rel(1), 
+                                margin = margin(0,0,5,0), 
+                                hjust = 0),
+      plot.title.position = "plot",
+      plot.subtitle = element_text(family="lora",
+                                   size = rel(0.85)),
+      plot.caption = element_text(family="lora",
+                                  size = rel(0.70),
+                                  hjust = 1),
+      # Graphical Zones
+      panel.grid.minor = element_blank(),
+      panel.border = element_blank(),
+      # Axes
+      axis.title = element_text(family="lora", 
+                                size = rel(0.85)),
+      axis.text = element_text(family="lora", 
+                               size = rel(0.70)),
+      axis.line = element_line(color = "black", 
+                               arrow = arrow(length = unit(0.3, "lines"), 
+                                             type = "closed")),
+      # Legend
+      legend.title = element_text(family="lora",
+                                  size = rel(0.85)),
+      legend.text = element_text(family="lora", 
+                                 size = rel(0.70)),
+      legend.key = element_rect(fill = "transparent", 
+                                colour = NA),
+      legend.key.size = unit(1.5, "lines"),
+      legend.background = element_rect(fill = "transparent", 
+                                       colour = NA),
+      # Facetting 
+      strip.background = element_rect(fill = "#17252D",
+                                      color = "#17252D"),
+      strip.text = element_text(family="lora",
+                                size = rel(0.85), 
+                                color = "white", 
+                                margin = margin(5,0,5,0))
+    )
+}
+
+theme_set(theme_diss())
 
@@
 
-# Abstract
-
-Possible titles Digital Trace Data as Social Indicators: Indicators of
-Attention Rather Than Support
-
-Digital Trace Data as Indicators of Social Data: Validating Google Trends for
- use in Scientific Research
-
-**Keywords**:
-
-# Intro
-
-New big data sources have led to vast possibilities for social science
-research because they are bigger, cheaper, and already available
-[@kingEnsuringDataRichFuture2011; @lazerComputationalSocialScience2009;
-@salganikBitBitSocial2017]. Before overenthusiastically embracing these
-sources into our workflows, social scientists must clearly establish
-parameters under which these data sources could be operationalized
-[@bailCulturalEnvironmentMeasuring2014; @lazerParableGoogleFlu2014]. As
-prior research outlined, the "quantity of data does not mean that one
-can ignore foundational issues of measurement and construct validity and
-reliability and dependencies among data" [@lazerParableGoogleFlu2014,
-p. 1203]. Building on this prior research outlining these various
-issues with big data [@boydCriticalQuestionsBig2012;
-@lazerIssuesConstructValidity2015], this paper tests the construct
-validity of Google Search Trends as an indicator of three different
-cases, namely cultural attitudes, disease prevalence and voting
-behavior. These three cases will be tested using cultural indicators
-from the NORC General Social Survey, United States county-level suicide
-rates from National Center for Health Statistics, US cases rates of
-Covid-19 from The New York Times, historical US Presidential Election
-results, and the American National Election Survey. Data will be
-analyzed against corresponding operationalized Google Trends
-longitudinal data using Pearson's r for pairwise correlations, testing
-for the strength of relationships between the Google Trend indicator and
-the respective comparison indicator. This paper will contribute to the
-creation of methodological norms and standards of how to use Google
-Trends as a big data source for societal research and serve as a
-critical inquiry into the adoption of big data without a critical eye
-for the ecological validity of the sources.
-
-With the expansion of big data, some research has shown extremely
-innovative methods that lead to groundbreaking results that are shown to
-be reliable. As an example, @blumenstockPredictingPovertyWealth2015 use
-county-level cell-phone records to construct the distribution of poverty
-and wealth in Rwanda, a country where national surveys and censes are
-rare and costly. However, @blumenstockPredictingPovertyWealth2015 go to
-great lengths to demonstrate that their operationalization of the cell
-phone data creates a reliable and valid construct; few social science
-papers utilizing big data dig into the construct validity of their
-metrics to this extent and even fewer publications focus on
-methodological guidelines of how to use sources of big data
-[@asseoTrackingCOVID19Using2020; @stilesAssessingCriterionValidity2018].
-However, research has shown the small adjustments to an algorithm or
-metric may void any research insight we are able to pull from such data
-[@lazerParableGoogleFlu2014]. Because of this, I propose a
-methodological validation study of the Google Search Trends source of
-big data to investigate how it is advisable to utilize this data in
-social scientific research.
-
-I will use three categorizations of ways I propose Google Trends could
-be operationalized for social scientific usage. First, I'll test Google
-Trends as an operationalization of cultural attitudes with the General
-Social Survey. After @bailCulturalEnvironmentMeasuring2014's call for
-cultural sociologists to utilize the ever-expanding world of big data,
-Google trends as a data source began appearing in sociological and
-social science research. From research on mass shootings and firearms
-[@brownsteinInternetSearchPatterns2020;
-@semenzaInformationseekingWakeTragedy2020], protest and anti-Muslim
-sentiment [@bailUsingInternetSearch2018;
-@barrieSearchingRacismGeorge2020; @grossThereFergusonEffect2017], to
-analyzing country-level changes in social perception [@reyes_etal18],
-Google search trends are a new and innovative indicator of cultural
-interest. Extending into social networks and culture,
-@bailPrestigeProximityPrejudice2019 even used Google trends to measure
-how culture spreads around the globe.
-
-Google Search Trends have also been used continuously in estimations of
-disease prevalence and population health in journals like the Journal of
-Medical Internet Research. While much of this research has focused on
-the Covid-19 pandemic [@jimenez_etal20;
-@jimenezCOVID19SymptomGoogle2020;
-@limEstimatingInformationSeekingBehaviour2020;
-@mavraganiCOVID19PredictabilityUnited2020;
-@nguyenGoogleTrendsAnalysis2020; @todorovaInternetBasedData2021] , other
-research has investigated Google Trends as an indicator of wellbeing
-[@brodeurCOVID19LockdownsWellbeing2021;
-@carpiTwitterSubjectiveWellBeing2020; @duCOVID19IncreasesOnline2020],
-suicidality [@burnettTimeTrendsPublic2020], vaccination uptake
-[@dalumhansenEnsembleLearnedVaccination2016], obesity
-[@sarigulNowcastingObesityUsing2014], and even insomnia
-[@zittingGoogleTrendsReveal2020], to cover a few examples. For a partial
-review of other utilizations, see @nutiUseGoogleTrends2014. According to
-@jaidkaInformationseekingVsSharing2021, the majority of studies profess
-a correlation of \> .70, "demonstrating the vast potential of Google
-Search as a proxy for monitoring population health" (p. 3) based on
-assumptions that individuals search because of self-diagnosis and to
-identify possible courses of treatment
-[@dechoudhurySeekingSharingHealth2014].
-
-<!-- Following reports say that Google searches can predict covid  -->
-
-<!-- 14. Brunori, P. & Resce, G. Searching for the peak Google Trends and the Covid-19 outbreak in Italy. SERIES working papers N. 04/2020 -->
-
-<!-- Lampos, V. et al. Tracking COVID-19 using online search. Preprint at https://arxiv.org/abs/2003.08086 (2020). -->
-
-<!-- 16. Walker, A., Hopkins, C. & Surda, P. The use of google trends to investigate the loss of smell related searches during COVID‐19 -->
-
-<!-- outbreak. Int. Forum Allergy Rh. 10, 839–847 (2020). -->
-
-<!-- 17. Stephens-Davidowitz, S. Google Searches Can Help Us Find Emerging Covid-19 Outbreaks. The New York Times https://www. -->
-
-<!-- nytimes.com/2020/04/05/opinion/coronavirus-google-searches.html (2020). -->
-
-<!-- 18.
-Frank, T.
-Goldman says fewer ‘loss of smell’ Google queries suggest better COVID outlook.
-Consumer News and Business Channel.
-CNBC https://www.cnbc.com/2020/04/15/goldman-says-fewer-loss-of-smell-google-searches-is-a-positive-sign-for-pande -->
-
-<!-- mic.html (2020) -->
-
-Various sources have also used Google Trends as a way to forecast
-political elections and political attitudes
-[@wolfTrendingRightDirection2018]. For instance,
-@swearingenGoogleInsightsSenate2014 investigate how U.S. Senate
-Elections relate to attention measured by search traffic.
-@prado-romanGoogleTrendsPredictor2020 compare how Google Search trends
-are able to predict presidential election results in both the United
-States and Canada. Finally, the OECD Development Centre is investigating
-how Google data can help elucidate governments' approval in Latin
-America [@montoyaUsingGoogleData2020].
-
-Research Question - How can we operationalize Google Search Trends as a
-valid indicator for uses in social science research?
-
-<https://journals.sagepub.com/doi/10.1177/0894439316631043> What
-constructs might google trends capture and not capture well? Capture
-attention but not attitudes
-
-Also Asseo - "we assumed that media coverage may potentially decouple
-the search popularity from the number of cases, since searches would
-result not only from self-symptoms, but also from interest elicited by
-media coverage."
-
 # Research Methodology
-To investigate the construct and criterion validity of the use of Google Trends
-in these three areas, I gathered geo-located social science data across multiple
-sources to address the three areas of inquiry for this paper.  Table
-\@ref(tab:data-sources-table) outlines which data sources are used for this
-project and which trends are matched to each source.
 
@@
 ## Measures
-### Google Trends
-This paper focuses on a validation of Google search trends [@googletrends].
-Google trends portray the search frequency for specific search terms across
-designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
-counties to 210 media markets based on similar population clusters [@dma_key].
-Raw data is on a scale from 0 to 100, with 100 being the maximum search
-popularity out of all DMAs. When available, I use Google search topics to
-measure trends as opposed to search terms. Search topics are a more robust
-measurement than a single search term: topics are aggregations of the rates of
-multiple, highly correlated search terms together into a cohesive topic. For
-example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
-search terms, 'Beyoncé Knowles' encompasses all of these into a single search
-topic. Google Search Trend are only available cross-sectionally (a single time
-period across a geography) or as time-series (a single geo-location across
-time). To remedy this and build a longitudinal dataset of each search topic for
-the longitudinal datasets, I follow the method proposed in @park_etal (p. 5).
-This method involves building a dataset of unscaled cross-sectional values,
-selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
-CA'), and then finding the time-series values for the one DMA. To find the
-rescaling ratio for each week in the time-series, you divide the time-series
-value for each week by the cross-sectional value for each week, resulting in a
-rescaling vector to be used for all weeks in the dataset across geographies. To
-rescale each longitudinal value, multiply the respective week's rescaling ratio
-by the cross-sectional value. Rescaled longitudinal data was compared against
-time-series data for multiple test counties and was equivalent. For a more
-in-depth explanation of this procedure, see @park_etal (p. 5). Missing
-datapoints in longitudinal datasets were filled in with interpolated values
-using `zoo::na.approx()` [@zoo].
 
-### attitudinal
+```{r}
+desc_stats_table <- 
+  vacc_hes  %>% 
+  bind_rows(mask) %>% 
+  bind_rows(covid) %>% 
+  bind_rows(suicide) %>% 
+  bind_rows(pres_2016 ) %>% 
+  bind_rows(pres_2020 )
 
-<!-- [@gss_data] (let's see if I get access first) -->
+datasummary(formula = 
+          (`Rate of Vaccine Hesitancy` = vacc_hesitant) +             
+          (`Rate of Rare Mask Usage` = mask_rare) +   
+          (`Rate of Covid` = covid_rate) +                 
+          (`Rate of Deaths by Suicide` = death_rate) +                
+          (`Percent of votes for Joe Biden` = biden_p) +                   
+          (`Percent of votes for Donald Trump` = trump_p) +                    
+          (`Percent of votes for Hillary Clinton` = clinton_p) + 
+          (`Search for Covid-19` = covid_19) +                  
+          (`Search for Covid-19 Vaccine` = covid_19_vaccine) +
+          (`Search for Vaccine` = vaccine) +
+          (`Search for coronavirus virus` = coronavirus_virus) +
+          (`Search for coronavirus disease` = coronavirus_disease) +
+          (`Search for Civil and political rights` = civil_and_political_rights) +
+          (`Search for cloth face mask` = cloth_face_mask) +
+          (`Search for Mask` = mask) +
+          (`Search for Taste Loss` = taste_loss) +                 
+          (`Search for Smell Loss` = smell_loss) + 
+          (`Search for Suicide` = suicide) +                    
+          (`Search for Depression` = depression) +                
+          (`Search for Suicide Hotline` = suicide_hotline) +  
+          (`Search for Hillary Clinton` = hillary_clinton_trend) +     
+          (`Search for Donald Trump` = donald_trump_trend) +        
+          (`Search for Joe Biden` = joe_biden_trend) +         
+          (`Total Population` = total_pop) +  
+          (`Population Density` = pop_density) +                
+          (`Unemployment Rate` = unemployment_rate) +         
+          (`% over 65` = over_65) +                   
+          (`% below poverty line` = poverty_rate) +               
+          (`Median income` = median_income) +             
+          (`% with broadband` = broadband)  ~ 
+    (Min  + Max + Mean + SD) ,
+  data = desc_stats_table,
+  fmt = '%.2f',
+  title = 'Descriptive Statistics for Dichotomous and Numeric Variables',
+  output = "latex")
 
-One measure of attitudinal indicators is the Vaccine Hesitancy for COVID-19
-[@vaches_data]. The CDC uses the U.S. Census Bureau’s Household Pulse Survey
-(HPS) and the 2019 American Community Survey (ACS) 1-year Public Use Microdata
-Sample (PUMS) to measure U.S. residents’ intentions to receive the COVID-19
-vaccine if available during May 26, 2021 – June 7, 2021. This dataset consists
-of `r nrow(vacc_hes)` observations, one for each U.S. County. The variable
-measures the precent of adults in the county who describe themselves as
-“unsure”, “probably not”, or “definitely not” going to get a COVID-19 vaccine
-once one is available to them. The variable ranges from 
-`r percent_format(0.01)(min(vacc_hes$vacc_hesitant))` to 
+```
+
+#### vacc_hes
+
+`r nrow(vacc_hes)`
+
+from `r percent_format(0.01)(min(vacc_hes$vacc_hesitant))` to 
 `r percent_format(0.01)(max(vacc_hes$vacc_hesitant))`.
 
-Another attitudinal indicator I use is the Mask-Wearing Survey Data conducted by
-Dynata for the New York Times from July 2 through 14, 2020 [@mask_data]. 250,000
-survey respondents were asked, "How often do you wear a mask in public when you
-expect to be within six feet of another person?". The NYT weighted each response
-to create a county level measure of what percent of the county never, rarely,
-sometimes, frequently, and always wore a mask when in public. This dataset
-consists of `r nrow(mask)` observations, one for each U.S. County. This measure
-represents the percent of adults in the county who never or rarely wear a mask
+#### mask
 (range = `r percent_format(0.01)(min(mask$mask_rare))` to  
@@
 ### health
-
-I also use U.S. Covid-19 rates to validate health and disease related topics. I
-retrieve U.S. county-level Covid-19 rates from by @covid_data, who compile this
-data based on reports from state and local health agencies. It is widely
-acknowledged that there are biases in this data due to inconsistencies and
-availability in testing as well as different community propensity to test
-[@gu22; @cdc20a] However, it is the best measure we have of actual case rates.
-Case Rate is measured as number of cases per 100,000 population. Observations
-vary from a minimum of 0 to a maximum of `r max(covid$covid_rate)` for each 
+#### covid
+0 to a maximum of `r max(covid$covid_rate)` for each 
 Monday from `r glue("{format( min(covid$date), '%B %d, %Y')} through {format(max(covid$date), '%B %d, %Y')}")`.
 There are `r nrow(covid)` cases across `r nrow(count(covid, fips))` 
-counties and `r nrow(count(covid, date))` dates. Missing data were interpolated 
-using `zoo::na.approx()` [@zoo].
+counties and `r nrow(count(covid, date))` dates.
 
-I also use county-level suicide rates from the US Centers for Disease Control
-and Prevention [-@suic_data]. Data is grouped by year from 2010-2020. Raw death
-rates are scaled by population size for each year and can be interpreted as the
-death rate by suicide for every 1000 people. There are `r nrow(suicide)` total
-cases, resulting from `r nrow(count(suicide, year))` observations of `r
-nrow(count(suicide, fips))` counties. Missing data were interpolated using
-`zoo::na.approx()` [@zoo]. Measures range from 
-`r round(min(suicide$death_rate, na.rm=T),3)` to 
+#### suicide
+ There are `r nrow(suicide)` total
+cases, resulting from `r nrow(count(suicide, year))` observations of 
+`r nrow(count(suicide, fips))` counties. Missing data were interpolated using.
+
+Measures range from `r round(min(suicide$death_rate, na.rm=T),3)` to 
 `r round(max(suicide$death_rate, na.rm=T),3)`.
@@
 ### political
-Finally, I test Google Trends as an operationalization of political
-attitudes by first looking at actual voting outcomes in historical US
-Presidential Election results. This data comes from @pres_data, who scraped the
-results from Townhall.com, Fox News, Politico, and the New York Times. Data on 
-presidential outcomes were avaiable for `r nrow(pres_2016)` counties in 2016 and
-`r nrow(pres_2020)` counties in 2020. Each variable measures the percent of votes
-for the candidate, with the lowest percent at 
+ avaiable for `r nrow(pres_2016)` counties in 2016   
+ and `r nrow(pres_2020)` counties in 2020.
+
+with the lowest percent at 
 `r percent_format(0.01)(min(pres_2020$biden_p, na.rm=T))`
 and the highest at `r percent_format(0.01)(max(pres_2020$biden_p, na.rm=T))`.
-
-In addition, I use data on political opinions from the the American National
-Election Survey 2020 Time-Series Study [@anes_data]. This data is paired with
-restricted data provided by ICPSR, the Inter-university Consortium for Political
-and Social Research, that contains the geo-ids of the `r scales::label_comma()(5441)`
-survey respondents. The study interviewed respondents in a pre-election survey
-that was conducted between August 18, 2020 and the day of the US Presidential
-election day, November 3, 2020.
-
-<!-- TODO: WHICH VARIABLES -->
-<!-- TODO: VARIABLE SCALE -->
-
-### Other
-
-In addition to specific outcomes of interest, I also gathered various county
-controls to investigate possible variable confounding. The first Seven of these
-variables come from the 2010-2019 5-year American Community Surveys [@acs2019;
-@acs2018; @acs2017; @acs2016; @acs2015; @acs2014; @acs2013; @acs2012;
-@acs2011; @acs2010]. These data include total population, population density,
-unemployment rate for those 16 and over, median county income, average commute
-time, percent of households living under the poverty line, and percent above 65
-years old. In addition, some models employ the U.S. Current Population Survey &
-American Community Survey Geographic Estimates of Internet Use, 1997-2018
-[@internet_use] to estimate households with broadband internet subscriptions.
-This final variable is an attempt to capture the latent propensity to use the
-internet for information search.
-
-<!-- ACS 5 year estimates -->
-<!-- a00001 total population -->
-<!-- a00002 population density -->
-<!-- a17005 unemployment rate 16+ -->
-<!-- a14006 median income -->
-<!-- a09003 average commute time -->
-<!-- poverty percent -->
-<!-- 01001B 65 plus -->
-
-## Analysis
-Google Search Trends data and additional demographic data are merged with each
-individual indicator based on County FIPS Codes and date. After creating these
-different datasets, I use the Pearson correlation formula (formula
-\@ref(eq:pearsoncorr)) for cross-sectional numeric data to calculate the
-strength of the relationship between each Google Trend and the respective
-data source.
-
-\begin{equation}
- r =
-  \frac{ \sum_{i=1}^{n}(x_i-\bar{x})(y_i-\bar{y}) }{
-        \sqrt{\sum_{i=1}^{n}(x_i-\bar{x})^2}\sqrt{\sum_{i=1}^{n}(y_i-\bar{y})^2}} (\#eq:pearsoncorr)
-\end{equation}
-
-To address longitudinal correlations, I employ Repeated Measures Correlation
-using the `rmcorr` package in R [@bland1995; @bakdash2017]. Repeated Measures
-Correlation is useful for determining the within-county association for paired
-measures across time and counties. Results of these correlations can be seen in 
-table \@ref(tab:corr-results).
-
-As an additional test of the relationships, I employ multiple linear regression
-(for cross-sectional datasets) and random intercept hierarchical linear models
-[@pinheiro_etal21] (for longitudinal datasets) to identify the strength of
-relationships across locales: I include city-data like county population size,
-broadband rates, and median income to attempt to disentangle possible
-confounders of the relationship between Google search Trends and verified
-indicators. Identifying these possible confounded relationships will help to
-explain why some articles find relationships between the trends and outcomes
-while others did not. For linear regression models, I normalize independent
-variables, i.e.variables have been centered and scaled to have a mean of 0 and
-standard deviation 1.
-
-# Results
-
-## Validating Google Trends as metrics of attitudinal indicators
 
@@
 
-The first attitudinal indicators is Vaccine Hesitancy for COVID-19 vaccines
-[@vaches_data]. When comparing the measure of vaccine hesitancy to four
-different Google Search Trends, the correlation does not exceed -0.4657
-('Coronavirus (Disease)' and vaccine hesitancy). Correlation's under |0.40| are
-considered to be weak according to the common rules of thumb. When running these
-correlations in multiple linear regression (see the results in table
-\@ref(tab:vacc_hes_analysis)), I see an $r^2$ of 0.233 (Model 1) and 0.411
-(Model 2), indicating that the Google Trends are able to explain about 23% of
-the variation in Vaccine Hesitancy alone. Demographic characteristics like the
-percentage of households with broadband internet and the population density are
-able to explain about 35% of the variation (model 2), outperforming the first
-models. The Trend coefficients themselves, however, are significant and remain
-significant when controlling for demographics. This reinforces the finding from
-the Pearson Correlation that there is a significant but weak relationship
-between the Google Trends and Vaccine Hesitancy.
+```{r vacc_hes_plot}
+
+vacc_hes %>% 
+  select(vacc_hesitant, covid_19_vaccine,
+         vaccine, coronavirus_disease,
+         coronavirus_virus, fips) %>% 
+  pivot_longer(cols = -c(vacc_hesitant, fips)) %>% 
+  ggplot(aes(x=value, y = vacc_hesitant)) + 
+  geom_point(aes(group = name, color = name ), show.legend = FALSE, alpha = 0.6) +
+  geom_smooth( aes(group = name),method = 'lm', fill = my_palette[10], color = my_palette[10]) +
+  labs(x = '', 
+       y = "Percent of adults who are vaccine hesitant")+ 
+  scale_y_continuous(labels = scales::label_percent()) +
+  scale_color_manual(values = my_palette[c(3,6,8,4)]) + 
+  facet_wrap(~name)
+```
 
 ```{r vacc_hes_analysis}
-#| tab.cap = "Linear Regression Results for Vaccine Hesitancy",
 #|  results='asis'
@@
 modelsummary(list(vacc_hes_2, vacc_hes_1, vacc_hes_3), 
-             # title = "Linear Regression Results for Vaccine Hesitancy",
+             title = "Linear Regression Results for Vaccine Hesitancy",
              notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
@@
              gof_omit = 'AIC|BIC|ICC|RMSE'
-             ) %>%
-  kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 8)
+             )
 
@@
 
-The second attitudinal measure I test is how Google Trends relates to rare mask
-usage. As with vaccine hesitancy, the Pearson correlations are negligible.
-Correlation's under |0.20| are considered to be negigible according to the
-common rules of thumb. I introduce these trends in multiple linear regression in
-table \@ref(tab:mask_analysis). Model 1 demonstrates that these five Google
-Search Trends can explain about 7% of the variance in mask usage across U.S.
-counties, reinforcing the conclusion that the relationship is quite weak. The
-coefficients themselves are somewhat significant in Model 1. However, after
-including the demographic variables in Models 2 and 3, we see that the
-relationship between the Google Search Trends and mask usage is strengthened in
-magnitude and in significance, likely indicating a suppression effect due to
-underlying relationships between the trends and demographic variables. While the
-trends are significant and match the demographic variables in magnitude, the
-low $r^2$ of 0.203 for the trends still provides evidence that Google Search
-Trends data cannot replace survey analysis when trying to measure rare mask
-usage.
+```{r mask_plot}
+mask %>% 
+  select(mask_rare,  coronavirus_disease,
+               coronavirus_virus, cloth_face_mask, 
+               mask, fips) %>% 
+  pivot_longer(cols = -c(mask_rare, fips)) %>% 
+  ggplot(aes(x=value, y = mask_rare, )) + 
+  geom_point(aes(group = name, color = name ), show.legend = FALSE, alpha = 0.6) +
+  geom_smooth( aes(group = name), method = 'lm', fill = my_palette[10], color = my_palette[10]) +
+  labs(x = '', 
+       y = "Percent of adults who rarely use masks")+ 
+  scale_y_continuous(labels = scales::label_percent()) +
+  scale_color_manual(values = my_palette[c(3,6,8,4)]) + 
+  facet_wrap(~name)
+```
 
 ```{r mask_analysis}
-#|  results='asis',
-#| tab.cap = "Linear Regression Results for Rare Mask Usage"
+#|  results='asis'
 
@@
                coronavirus_virus + cloth_face_mask + 
-               mask + civil_and_political_rights,
+               mask,
              data = mask)
@@
                 coronavirus_virus + cloth_face_mask + 
-                mask + civil_and_political_rights,
+                mask,
               data = mask)
@@
 modelsummary(list(mask_2, mask_1, mask_3), 
-             # title = "Linear Regression Results for Rare Mask Usage",
+             title = "Linear Regression Results for Rare Mask Usage",
              notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).'),
              estimate = "{estimate}{stars}",
-             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
-  kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 8)
+             gof_omit = 'AIC|BIC|ICC|RMSE')
 
@@
 
-## Validating Google Trends as metrics of health outcomes
-
-In addition to attitudinal measures, I attempt to validate Google Trends for
-uses in the measurements of health indicators. The first indicator I test is
-Covid-19 case rates from 2020 through 2021. The Pearson correlation results
-indicate negligible to weak relationships between the search terms and the
-actual case rates across time and place. The repeated measures correlation
-coefficient, a more reliable and less biased measure for longitudinal
-correlations, reveals similarly weak results with a maximum correlation of 0.32
-between 'smell loss' and rates of Covid-19. To further test the relationship, I
-include the three trends in random intercept hierarchical linear models. Model 1
-of table \@ref(tab:covid_analysis) indicates that the trends themselves are able
-to explain about 20% of the variation in Covid-19 rates ($r^2$ = 0.201). Few
-of the demographic variables have an effect on Covid-19 rates in models 2 or 3,
-though it seems there is some suppression for median income, unemployment rates,
-and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
-Google Trends are slightly related to Covid-19 rates, but that this relationship
-is weak and we should not attempt to use Google Trends as an indicator of actual
-health outcomes.
+```{r covid_plot}
+covid   %>% 
+    filter(date %in% lubridate::ymd(c('2020-09-14'))) %>% 
+  select(covid_rate, covid_19, smell_loss, taste_loss, fips) %>% 
+  pivot_longer(cols = -c(covid_rate, fips)) %>% 
+  ggplot(aes(x=covid_rate, y = value, group = fips, color = name)) + 
+  geom_point(aes(group = name, color = name ), show.legend = FALSE, alpha = 0.6) +
+  geom_smooth( aes(group = name), method = 'lm', fill = my_palette[10], color = my_palette[10]) +
+  labs(x = '', 
+       y = "COVID-19 case rate on 09-14-2020")+ 
+  scale_color_manual(values = my_palette[c(3,6,8,4)]) + 
+  facet_wrap(~name)
+```
 
 ```{r covid_analysis}
+#|  results='asis'
+
 covid <- covid %>% 
@@
 modelsummary(list(covid_2, covid_1, covid_3), 
-             # title = "Hierarchical Model for Covid Case Rates",
+             title = "Hierarchical Model for Covid Case Rates",
              notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
@@
              estimate = "{estimate}{stars}",
-             gof_omit = 'AIC|BIC|ICC|RMSE|SD') %>%
-  kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 8)
+             gof_omit = 'AIC|BIC|ICC|RMSE|SD')
 
@@
 
-Another indicator of health outcomes I test to validate Google Trends as
-possible health indicators are county suicide rates. As with previous cases,
-there is only negligible correlation between actual suicide rates and Google
-Search Trends, not exceeding 0.0845. In the more accurate repeated measures
-correlation coefficient we see a maximum of 0.142 correlation, remaining
-negligible. I introduce these trends into a random intercept model to control
-for inter-group variation over time in table \@ref(tab:suicide_analysis). While
-table \@ref(tab:suicide_analysis) model 1 reveals a significant relationship
-between suicide hotline trends and suicide rates, the effect is small and the
-entire model only has an $r^2$ of 0.058. Adding in demographic features in model
-2 improves the $r^2$ quite a lot. In model 3, the inclusion of Google Trends
-actually decreases the overall amount of suicide rate variance explained
-compared to model 2. These analyses lead me to conclude that Google Search
-Trends should not be used as indicators of suicide rates or intentions.
+```{r suicide_plot}
+suicide   %>% 
+    filter(year == 2019) %>% 
+  select(death_rate, suicide, depression, suicide_hotline, fips) %>% 
+  pivot_longer(cols = -c(death_rate, fips)) %>% 
+  ggplot(aes(x=death_rate, y = value, group = fips, color = name)) + 
+  geom_point(aes(group = name, color = name ), show.legend = FALSE, alpha = 0.6) +
+  geom_smooth( aes(group = name), method = 'lm', fill = my_palette[10], color = my_palette[10]) +
+  labs(x = '', 
+       y = "Death rate by suicide for 2019")+ 
+  scale_color_manual(values = my_palette[c(3,6,8,4)]) + 
+  facet_wrap(~name)
+```
 
 ```{r suicide_analysis}
+#|  results='asis'
+
 suicide <- suicide %>% 
@@
 modelsummary(list(suicide_2, suicide_1, suicide_3), 
-             # title = "Hierarchical Model for Suicide Rates",
+             title = "Hierarchical Model for Suicide Rates",
              notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
@@
              estimate = "{estimate}{stars}",
-             gof_omit = 'AIC|BIC|ICC|RMSE') %>%
-  kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 10)
+             gof_omit = 'AIC|BIC|ICC|RMSE')
 
 # TODO Drop SD intercept and observations,
-# TODO why is the r2 so high? death_rate_fips_mean?
 ```
 
-## Validating Google Trends as metrics of political support
+```{r pres_plot}
+pres_2016_plot <- pres_2016 %>% 
+  select(clinton_p, 
+         # trump_p,
+         donald_trump_trend, hillary_clinton_trend,
+         fips) %>% 
+  pivot_longer(cols = -c(clinton_p, fips), names_to = "trend", values_to = "trend_value") %>% 
+  # pivot_longer(cols = -c(trend, trend_value, fips), names_to = "pres", values_to = "pres_percent") %>%
 
-Previous research has showed some relationship between Google Search Trends and
-political election results. I test here the relationships between search trends
-and U.S. Presidential Election results in 2016 and 2020. In 2016, Pearson
-correlations for Both Hilary Clinton and Donald Trump do not exceed a |0.17|
-correlation with the actual percentage of votes for either candidate. In 2020,
-results are even less related, with searches for neither Joe Biden nor Donald
-Trump holding any real correlation with the 2020 results.
+  ggplot(aes(x=trend_value, y = clinton_p, color = trend )) + 
+  geom_jitter(show.legend = FALSE, alpha = 0.6) +
+  geom_smooth(method = 'lm', fill = my_palette[10], color = my_palette[10]) +
+  labs(x = '', 
+       y = "% of votes for Hilary Clinton, 2016")+ 
+  scale_y_continuous(labels = scales::label_percent()) +
+  scale_color_manual(values = my_palette[c(3,6,8,4)]) +
+  facet_wrap(~ trend, scales = 'free_x')
+  # facet_grid(rows = vars(pres), cols = vars(trend), scales = 'free_x')
 
-In table \@ref(tab:pres_2016_analysis), I outline the results for the model
-predicting the county percentage of votes for Hillary Clinton. Model 1
-demonstrates how well Google Trends are able to predict the votes; while the
-trend for 'Hillary Clinton' is significantly associated with votes, the model's
-$r^2$ ($r^2$ = 0.027) shows that it does little to help explain the model
-variance. On the other hand, adding in demographic features improves the model
-fit quite well, bringing the $r^2$ up to 0.313 in model 2 and $r^2$ 0.327 in
-model 3. In table \@ref(tab:pres_2020_analysis) shows this same analysis for the
-2020 election and predicts the percentage of votes for Joe Biden. While this
-model is largely similar to those in table \@ref(tab:pres_2016_analysis), this
-model 1 demonstrates how unrelated Google Trends can be from actual outcomes. In
-conclusion, I find that Google Trends are an unreliable and invalid indicator of
-political support.
+pres_2020_plot <- pres_2020 %>% 
+  select(biden_p, 
+         donald_trump_trend, joe_biden_trend,
+         fips) %>% 
+  pivot_longer(cols = -c(biden_p, fips), names_to = "trend", values_to = "trend_value") %>%
+
+  ggplot(aes(x=trend_value, y = biden_p, color = trend )) + 
+  geom_jitter(show.legend = FALSE, alpha = 0.6) +
+  geom_smooth(method = 'lm', fill = my_palette[10], color = my_palette[10]) +
+  labs(x = '', 
+       y = "% of votes for Joe Biden, 2020")+ 
+  scale_y_continuous(labels = scales::label_percent()) +
+  scale_color_manual(values = my_palette[c(8,4)]) +
+  facet_wrap(~ trend, scales = 'free_x')
+  # facet_grid(rows = vars(pres), cols = vars(trend), scales = 'free_x')
+
+library(patchwork)
+pres_2016_plot /pres_2020_plot
+
+```
 
 ```{r pres_2016_analysis}
+
+#|  results='asis'
+
 pres_2016 <- pres_2016 %>% 
@@
                   ), 
-             # title = "Linear Regression Results for 2016 Presidential Election Results (Hilary Clinton Shown)",
+             title = "Linear Regression Results for 2016 Presidential Election Results (Hilary Clinton Shown)",
              notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
@@
              gof_omit = 'AIC|BIC|ICC|RMSE|F'
-             ) %>%
-  kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 10)
+             )
 
@@
 ```{r pres_2020_analysis}
+#|  results='asis'
+
 pres_2020 <- pres_2020 %>% 
@@
                   ), 
-             # title = "Linear Regression Results for 2020 Presidential Election Results (Joe Biden Shown)",
+             title = "Linear Regression Results for 2020 Presidential Election Results (Joe Biden Shown)",
              notes= c('* p < .05. ** p < .01. *** p < .001 (two-tailed test).',
@@
              gof_omit = 'AIC|BIC|ICC|RMSE|F'
-             ) %>%
-  kable_styling(latex_options = c("hold_position", 'condensed'),
-                font_size = 10)
+             )
 
 ```
-
-# Discussion
-
-The external validity of these voting
-
-While I expect these tests to show high correlation between observed
-indicators and Google search trends, there will be three important
-questions that surface. First, just because something is correlated,
-does that mean it can replace the collection of other types of data?
-Second, how correlated does a trend need to be for social scientists to
-justifiably rely on it to indicate some outcome? And finally, how can we
-construct analyses like this to be robust to changes in the terms used
-across time and location?
-
-The purpose of this paper is more methodological than theoretical, and I
-see this paper having an impact on the social sciences and computational
-social science as researchers pursue more projects using this source of
-big data. Google Trends are relatively underutilized in the field
-compared to in the health sciences and business. Once I assess how this
-data can be used, I would like to be able to join
-@bailCulturalEnvironmentMeasuring2014 in encouraging social scientists
-to pursue more research with big data while taking into account the
-potential pitfalls with any source of big data
-[@mcfarlandBigDataDanger2015].
-
-# Conclusion
-
-\newpage

### 2022-06-18 paper1.tex
Final Dissertation Chapter 1 Version Update

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Article 1: Digital Trace Data as Indicators of Social Data Validating Google Trends for use in Scientific Research},
  pdfauthor={Kelsey Gonzalez},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{siunitx}
\usepackage{setspace}
\usepackage{dcolumn}
\usepackage{longtable}
\usepackage{caption}
\usepackage{booktabs}
\usepackage{placeins}
\usepackage{hhline}
\doublespacing
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Article 1: Digital Trace Data as Indicators of Social Data
Validating Google Trends for use in Scientific Research}
\author{Kelsey Gonzalez}
\date{21 March, 2022}

\begin{document}
\maketitle

\hypertarget{research-methodology}{%
\section{Research Methodology}\label{research-methodology}}

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{cccc}

\caption{New York Air Quality Measurements
}(\#tab:data-sources-table)\\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Validated.Data.Source}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Type}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Dates}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Google.Trends.Used}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Validated.Data.Source}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Type}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Dates}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{Google.Trends.Used}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}\endhead

\multicolumn{4}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Behaviors\ and\ Attitudes}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{General\ Social\ Survey}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Cross-Sectional}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2010\ -\ 2020}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Vaccine\ Hesitancy\ for\ COVID-19}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Cross-Sectional}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{March\ 3\ –\ 15,\ 2021}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Search\ Topics:\ 'Covid-19\ vaccine',\ 'Coronavirus\ (Disease)',\ 'Coronavirus\ (Virus)',\ 'Vaccine'}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Mask-Wearing\ Survey\ Data}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Cross-Sectional}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{July\ 2\ -\ 14,\ 2020}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Search\ Topics:\ 'Coronavirus\ (Disease)',\ 'Coronavirus\ (Virus)',\ 'Cloth\ Face\ Mask',\ 'Mask',\ 'Civil\ and\ Political\ Rights'}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{4}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Health}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Covid\ Rates}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Longitudinal}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Every\ Monday,\ 2020\ -\ 2021}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{'Covid-19',\ 'Coronavirus',\ 'Taste\ Loss',\ 'Smell\ Loss'}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{County\ Suicide\ Rates}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Longitudinal}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Yearly\ 2010-2020}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Search\ Topics:\ 'Suicide',\ 'Depression',\ Search\ Term:'\ Suicide\ Hotline'}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{4}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Political}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{American\ National\ Election\ Survey}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Cross-Sectional}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2020}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Presidential\ Election\ Results}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Cross\ Sectional}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2016\ \&\ 2020}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Search\ Topics:\ 'Hilary\ Clinton',\ 'Donald\ Trump',\ 'Joe\ Biden'}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\end{longtable}

\hypertarget{measures}{%
\subsection{Measures}\label{measures}}

\hypertarget{vacc_hes}{%
\paragraph{vacc\_hes}\label{vacc_hes}}

3148

from 4.99\% to 32.33\%.

\hypertarget{mask}{%
\paragraph{mask}\label{mask}}

(range = 0.10\% to\\
55.80\%)

\hypertarget{health}{%
\subsubsection{health}\label{health}}

\hypertarget{covid}{%
\paragraph{covid}\label{covid}}

0 to a maximum of 1460.46 for each Monday from January 27, 2020 through
December 27, 2021. There are 285986 cases across 3136 counties and 101
dates.

\hypertarget{suicide}{%
\paragraph{suicide}\label{suicide}}

There are 34683 total cases, resulting from 34617 observations of 3147
counties. Missing data were interpolated using.

Measures range from 0.034 to 53.254.

\hypertarget{political}{%
\subsubsection{political}\label{political}}

avaiable for 3147 counties in 2016\\
and 3118 counties in 2020.

with the lowest percent at 3.09\% and the highest at 92.15\%.

\providecommand{\docline}[3]{\noalign{\global\setlength{\arrayrulewidth}{#1}}\arrayrulecolor[HTML]{#2}\cline{#3}}

\setlength{\tabcolsep}{2pt}

\renewcommand*{\arraystretch}{1.5}

\begin{longtable}[c]{ccccccc}

\caption{Correlation Results
}(\#tab:corr-results)\\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{measure}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{variable}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend1}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend2}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend3}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend4}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend5}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\endfirsthead

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{measure}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{variable}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend1}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend2}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend3}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend4}}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{004F63}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{11}{11}\selectfont{\textcolor[HTML]{FFFFFF}{\global\setmainfont{Arial}{\textbf{trend5}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}\endhead

\multicolumn{7}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Vaccine\ Hesitancy}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Covid-19\ vaccine}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Coronavirus\ (Disease)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Coronavirus\ (Virus)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Vaccine}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Vaccine\ Hesitancy}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.3866}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.4657}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.3561}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.3994}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{7}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Mask\ Attitudes}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Coronavirus\ (Disease)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Coronavirus\ (Virus)}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Cloth\ Face\ Mask}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Mask}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Civil\ and\ Political\ Rights}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Mask\ Rare}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.1398}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.1343}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.146}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.1339}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.1175}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{7}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Covid\ Rates}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{covid\_19}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{smell\_loss}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{taste\_loss}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Covid\ Rate}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.1012}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.2835}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.2851}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{repeated\ measures\ correlation\ coefficient}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Covid\ Rate}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.099***}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.322***}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.313***}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{7}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{Suicide\ Rates}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{suicide}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{depression}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{suicide\_hotline}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Suicide\ Rate}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.0845}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.0273}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.0618}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{repeated\ measures\ correlation\ coefficient}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Suicide\ Rate}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.055***}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.142***}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.131***}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{7}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{2016\ Presidential\ Votes}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Hilary\ Clinton}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Donald\ Trump}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2016\ Votes\ for\ Clinton}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.1663}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.1663}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2016\ Votes\ for\ Trump}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.1682}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.1682}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{7}{!{\color[HTML]{666666}\vrule width 1pt}>{\cellcolor[HTML]{BAD7DB}}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{\textbf{\textit{2020\ Presidential\ Votes}}}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Joe\ Biden}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Donald\ Trump}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2020\ Votes\ for\ Biden}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.0286}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.0286}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{Pearson's\ R\ Correlation}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{2020\ Votes\ for\ Trump}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{0.0356}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{-0.0356}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} & \multicolumn{1}{!{\color[HTML]{666666}\vrule width 1pt}>{}l!{\color[HTML]{666666}\vrule width 1pt}}{\fontsize{8}{8}\selectfont{\textcolor[HTML]{000000}{\global\setmainfont{Arial}{}}}} \\

\hhline{>{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}->{\arrayrulecolor[HTML]{666666}\global\arrayrulewidth=1pt}-}

\end{longtable}

\begin{center}\includegraphics[width=0.8\linewidth]{paper1_files/figure-latex/vacc_hes_plot-1} \end{center}

\begin{table}

\caption{\label{tab:vacc_hes_analysis}Linear Regression Results for Vaccine Hesitancy}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & \num{0.191}*** & \num{0.191}*** & \num{0.191}***\\
 & (\num{0.001}) & (\num{0.001}) & (\num{0.001})\\
covid\_19\_vaccine & \num{-0.006}+ &  & \num{-0.011}**\\
 & (\num{0.004}) &  & (\num{0.003})\\
vaccine & \num{0.021}*** &  & \num{0.023}***\\
 & (\num{0.005}) &  & (\num{0.005})\\
coronavirus\_disease & \num{-0.037}*** &  & \num{-0.027}***\\
 & (\num{0.003}) &  & (\num{0.003})\\
coronavirus\_virus & \num{-0.003}* &  & \num{0.000}\\
 & (\num{0.001}) &  & (\num{0.001})\\
total\_pop &  & \num{-0.005}*** & \num{-0.004}***\\
 &  & (\num{0.001}) & \vphantom{5} (\num{0.001})\\
pop\_density &  & \num{-0.004}*** & \num{-0.003}***\\
 &  & (\num{0.001}) & \vphantom{4} (\num{0.001})\\
unemployment\_rate &  & \num{-0.002}* & \num{0.000}\\
 &  & (\num{0.001}) & \vphantom{3} (\num{0.001})\\
over\_65 &  & \num{-0.013}*** & \num{-0.010}***\\
 &  & (\num{0.001}) & \vphantom{2} (\num{0.001})\\
poverty\_rate &  & \num{0.005}** & \num{0.004}**\\
 &  & (\num{0.002}) & (\num{0.001})\\
median\_income &  & \num{-0.021}*** & \num{-0.016}***\\
 &  & (\num{0.001}) & \vphantom{1} (\num{0.001})\\
broadband &  & \num{-0.008}*** & \num{-0.005}***\\
 &  & (\num{0.001}) & (\num{0.001})\\
\midrule
Num.Obs. & \num{3148} & \num{3133} & \num{3133}\\
R2 & \num{0.233} & \num{0.350} & \num{0.411}\\
R2 Adj. & \num{0.232} & \num{0.349} & \num{0.409}\\
Log.Lik. & \num{5163.343} & \num{5405.127} & \num{5557.567}\\
F & \num{238.587} & \num{240.876} & \num{197.733}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{center}\includegraphics[width=0.8\linewidth]{paper1_files/figure-latex/mask_plot-1} \end{center}

\begin{table}

\caption{\label{tab:mask_analysis}Linear Regression Results for Rare Mask Usage}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & \num{0.162}*** & \num{0.163}*** & \num{0.162}***\\
 & (\num{0.002}) & (\num{0.002}) & (\num{0.002})\\
coronavirus\_disease & \num{-0.011}*** &  & \num{-0.012}***\\
 & (\num{0.003}) &  & \vphantom{3} (\num{0.003})\\
coronavirus\_virus & \num{-0.007}* &  & \num{0.003}\\
 & (\num{0.003}) &  & \vphantom{2} (\num{0.003})\\
cloth\_face\_mask & \num{-0.003} &  & \num{-0.008}*\\
 & (\num{0.003}) &  & \vphantom{1} (\num{0.003})\\
mask & \num{0.019}*** &  & \num{0.016}***\\
 & (\num{0.003}) &  & (\num{0.003})\\
total\_pop &  & \num{-0.012}*** & \num{-0.011}***\\
 &  & (\num{0.002}) & \vphantom{3} (\num{0.002})\\
pop\_density &  & \num{-0.003}+ & \num{-0.003}*\\
 &  & (\num{0.002}) & \vphantom{2} (\num{0.002})\\
unemployment\_rate &  & \num{-0.028}*** & \num{-0.027}***\\
 &  & (\num{0.002}) & \vphantom{1} (\num{0.002})\\
over\_65 &  & \num{-0.006}** & \num{-0.005}*\\
 &  & (\num{0.002}) & (\num{0.002})\\
poverty\_rate &  & \num{-0.010}** & \num{-0.010}**\\
 &  & (\num{0.003}) & \vphantom{2} (\num{0.003})\\
median\_income &  & \num{-0.036}*** & \num{-0.033}***\\
 &  & (\num{0.003}) & \vphantom{1} (\num{0.003})\\
broadband &  & \num{-0.006}* & \num{-0.006}*\\
 &  & (\num{0.003}) & (\num{0.003})\\
\midrule
Num.Obs. & \num{3136} & \num{3133} & \num{3121}\\
R2 & \num{0.049} & \num{0.176} & \num{0.189}\\
R2 Adj. & \num{0.047} & \num{0.174} & \num{0.186}\\
Log.Lik. & \num{2970.506} & \num{3184.261} & \num{3202.189}\\
F & \num{40.072} & \num{95.547} & \num{65.970}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{center}\includegraphics[width=0.8\linewidth]{paper1_files/figure-latex/covid_plot-1} \end{center}

Random effect variances not available. Returned R2 does not account for
random effects. Random effect variances not available. Returned R2 does
not account for random effects.

\begin{table}

\caption{\label{tab:covid_analysis}Hierarchical Model for Covid Case Rates}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & \num{-532.306}*** & \num{-712.023}*** & \num{-534.608}***\\
 & (\num{8.271}) & (\num{6.009}) & (\num{8.268})\\
covid\_19 & \num{1.031}*** &  & \num{1.024}***\\
 & (\num{0.082}) &  & \vphantom{1} (\num{0.082})\\
smell\_loss & \num{7.373}*** &  & \num{7.374}***\\
 & (\num{0.082}) &  & (\num{0.082})\\
taste\_loss & \num{6.344}*** &  & \num{6.347}***\\
 & (\num{0.078}) &  & (\num{0.078})\\
covid\_rate\_fips\_mean & \num{0.813}*** & \num{0.982}*** & \num{0.879}***\\
 & (\num{0.019}) & (\num{0.010}) & (\num{0.020})\\
date & \num{0.029}*** & \num{0.038}*** & \num{0.029}***\\
 & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
SD (Intercept) & \num{5.196} & \num{0.002} & \num{4.984}\\
SD (Observations) & \num{29.478} & \num{31.736} & \num{29.441}\\
total\_pop &  & \num{0.064} & \num{0.409}**\\
 &  & (\num{0.066}) & (\num{0.140})\\
pop\_density &  & \num{0.010} & \num{0.463}***\\
 &  & (\num{0.067}) & (\num{0.123})\\
unemployment\_rate &  & \num{0.049} & \num{0.725}***\\
 &  & (\num{0.080}) & (\num{0.155})\\
over\_65 &  & \num{-0.116} & \num{-0.055}\\
 &  & (\num{0.074}) & (\num{0.139})\\
poverty\_rate &  & \num{0.054} & \num{0.351}\\
 &  & (\num{0.118}) & (\num{0.221})\\
median\_income &  & \num{0.031} & \num{0.907}***\\
 &  & (\num{0.114}) & (\num{0.214})\\
broadband &  & \num{0.073} & \num{0.437}*\\
 &  & (\num{0.097}) & (\num{0.182})\\
\midrule
Num.Obs. & \num{248346} & \num{284666} & \num{247655}\\
R2 Marg. & \num{0.201} & \num{0.081} & \num{0.200}\\
R2 Cond. &  & \num{0.081} & \\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Random intercept per county}\\
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{center}\includegraphics[width=0.8\linewidth]{paper1_files/figure-latex/suicide_plot-1} \end{center}

Random effect variances not available. Returned R2 does not account for
random effects. Random effect variances not available. Returned R2 does
not account for random effects. Random effect variances not available.
Returned R2 does not account for random effects.

\begin{table}

\caption{\label{tab:suicide_analysis}Hierarchical Model for Suicide Rates}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & \num{-7.364}*** & \num{-10.046}*** & \num{-9.683}***\\
 & (\num{0.359}) & (\num{0.342}) & (\num{0.454})\\
suicide & \num{-0.001} &  & \num{-0.001}\\
 & (\num{0.001}) &  & \vphantom{2} (\num{0.001})\\
depression & \num{-0.001}+ &  & \num{-0.001}\\
 & (\num{0.001}) &  & \vphantom{1} (\num{0.001})\\
suicide\_hotline & \num{0.002}*** &  & \num{0.002}***\\
 & (\num{0.001}) &  & (\num{0.001})\\
year & \num{0.004}*** & \num{0.005}*** & \num{0.005}***\\
 & (\num{0.000}) & (\num{0.000}) & (\num{0.000})\\
SD (Intercept) & \num{1.460} & \num{1.587} & \num{1.459}\\
SD (Observations) & \num{0.050} & \num{0.051} & \num{0.050}\\
total\_pop &  & \num{-0.032}*** & \num{-0.027}**\\
 &  & (\num{0.010}) & (\num{0.009})\\
pop\_density &  & \num{-0.037}** & \num{-0.033}**\\
 &  & (\num{0.011}) & (\num{0.011})\\
unemployment\_rate &  & \num{-0.001} & \num{-0.001}\\
 &  & (\num{0.001}) & \vphantom{1} (\num{0.001})\\
over\_65 &  & \num{-0.010}*** & \num{-0.014}***\\
 &  & (\num{0.002}) & \vphantom{1} (\num{0.002})\\
poverty\_rate &  & \num{-0.005}*** & \num{-0.003}**\\
 &  & (\num{0.001}) & (\num{0.001})\\
median\_income &  & \num{-0.014}*** & \num{-0.015}***\\
 &  & (\num{0.002}) & (\num{0.002})\\
\midrule
Num.Obs. & \num{30008} & \num{33582} & \num{30001}\\
R2 Marg. & \num{0.058} & \num{0.582} & \num{0.564}\\
R2 Cond. &  &  & \\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Random intercept per county}\\
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{center}\includegraphics[width=0.8\linewidth]{paper1_files/figure-latex/pres_plot-1} \end{center}

\begin{table}

\caption{\label{tab:pres_2016_analysis}Linear Regression Results for 2016 Presidential Election Results (Hilary Clinton Shown)}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & \num{0.318}*** & \num{0.318}*** & \num{0.318}***\\
 & (\num{0.003}) & (\num{0.002}) & (\num{0.002})\\
hillary\_clinton\_trend & \num{-0.025}*** &  & \num{-0.019}***\\
 & (\num{0.003}) &  & (\num{0.002})\\
total\_pop &  & \num{0.028}*** & \num{0.028}***\\
 &  & (\num{0.002}) & \vphantom{1} (\num{0.002})\\
pop\_density &  & \num{0.022}*** & \num{0.022}***\\
 &  & (\num{0.002}) & (\num{0.002})\\
unemployment\_rate &  & \num{0.047}*** & \num{0.045}***\\
 &  & (\num{0.003}) & \vphantom{1} (\num{0.003})\\
over\_65 &  & \num{-0.012}*** & \num{-0.014}***\\
 &  & (\num{0.003}) & (\num{0.003})\\
poverty\_rate &  & \num{0.034}*** & \num{0.034}***\\
 &  & (\num{0.004}) & \vphantom{1} (\num{0.004})\\
median\_income &  & \num{0.054}*** & \num{0.052}***\\
 &  & (\num{0.004}) & (\num{0.004})\\
\midrule
Num.Obs. & \num{3147} & \num{3145} & \num{3145}\\
R2 & \num{0.028} & \num{0.314} & \num{0.329}\\
R2 Adj. & \num{0.027} & \num{0.313} & \num{0.327}\\
Log.Lik. & \num{1483.493} & \num{2037.065} & \num{2071.025}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Results predicting Donald J. Trump percentage largely equivalent and available upon request.}\\
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\begin{table}

\caption{\label{tab:pres_2020_analysis}Linear Regression Results for 2020 Presidential Election Results (Joe Biden Shown)}
\centering
\begin{tabular}[t]{lccc}
\toprule
  & Model 1 & Model 2 & Model 3\\
\midrule
(Intercept) & \num{0.333}*** & \num{0.333}*** & \num{0.333}***\\
 & (\num{0.003}) & (\num{0.002}) & (\num{0.002})\\
joe\_biden\_trend & \num{-0.005} &  & \num{-0.014}***\\
 & (\num{0.003}) &  & (\num{0.002})\\
total\_pop &  & \num{0.030}*** & \num{0.029}***\\
 &  & (\num{0.003}) & \vphantom{3} (\num{0.003})\\
pop\_density &  & \num{0.021}*** & \num{0.022}***\\
 &  & (\num{0.003}) & \vphantom{2} (\num{0.003})\\
unemployment\_rate &  & \num{0.044}*** & \num{0.044}***\\
 &  & (\num{0.003}) & \vphantom{1} (\num{0.003})\\
over\_65 &  & \num{-0.007}* & \num{-0.008}**\\
 &  & (\num{0.003}) & (\num{0.003})\\
poverty\_rate &  & \num{0.032}*** & \num{0.033}***\\
 &  & (\num{0.004}) & \vphantom{1} (\num{0.004})\\
median\_income &  & \num{0.069}*** & \num{0.070}***\\
 &  & (\num{0.004}) & (\num{0.004})\\
\midrule
Num.Obs. & \num{3118} & \num{3118} & \num{3118}\\
R2 & \num{0.001} & \num{0.295} & \num{0.303}\\
R2 Adj. & \num{0.000} & \num{0.294} & \num{0.301}\\
Log.Lik. & \num{1291.161} & \num{1835.433} & \num{1852.002}\\
\bottomrule
\multicolumn{4}{l}{\rule{0pt}{1em}Results predicting Donald J. Trump percentage largely equivalent and available upon request.}\\
\multicolumn{4}{l}{\rule{0pt}{1em}* p $<$ .05. ** p $<$ .01. *** p $<$ .001 (two-tailed test).}\\
\end{tabular}
\end{table}

\end{document}
